### 2019-06-27 Rebuttal_Letter.tex
started a git project

% Title:    A LaTeX Template For Responses To a Referees' Reports
% Author:   Petr Zemek <s3rvac@gmail.com>
% Homepage: https://blog.petrzemek.net/2016/07/17/latex-template-for-responses-to-referees-reports/
% License:  CC BY 4.0 (https://creativecommons.org/licenses/by/4.0/)
\documentclass[12pt]{article}

% Allow Unicode input (alternatively, you can use XeLaTeX or LuaLaTeX)
\usepackage[utf8]{inputenc}
\usepackage[inline]{trackchanges}
\usepackage{times}

\usepackage{microtype,xparse,tcolorbox}
\newenvironment{reviewer-comment }{}{}
\tcbuselibrary{skins}
\tcolorboxenvironment{reviewer-comment }{empty,
  left = 1em, top = 1ex, bottom = 1ex,
  borderline west = {2pt} {0pt} {black!20},
}
\ExplSyntaxOn
\NewDocumentEnvironment {response} { +m O{black!20} } {
  \IfValueT {#1} {
    \begin{reviewer-comment~}
      \setlength\parindent{2em}
      \noindent
      \ttfamily #1
    \end{reviewer-comment~}
  }
  \par\noindent\ignorespaces
} { \bigskip\par }

\NewDocumentCommand \Reviewer { m } {
  \section*{Comments~by~Reviewer~#1}
}
\ExplSyntaxOff
\AtBeginDocument{\maketitle\thispagestyle{empty}\noindent}

% You can get probably get rid of these definitions:
\newcommand\meta[1]{$\langle\hbox{#1}\rangle$}
\newcommand\PaperTitle[1]{``\textit{#1}''}

%\title{Statement on the Revision of \meta{Paper \#2019JB017831} \\
%  Based on the Referees' Report}
%\author{Oluwaseun Idowu Fadugba \and Eunseo Choi \and Christine A. Powell}
%\date{\today}
\date{}

\begin{document}

\noindent Dear Dr Yehuda Ben-Zion,
%\add[EC]{[the name of the handling editor]}, 
\\\vspace{1em}

Thank you for giving us the opportunity to revise our manuscript \PaperTitle{Effects of pre-existing structures on the seismicity of the Charlevoix Seismic Zone}. We also thank the reviewers for the critical assessment and constructive comments on the manuscript. In this submission, you will find our detailed answers to all of the reviewers’ comments, a copy of the revised manuscript with all changes highlighted in color, a copy of the revised manuscript with the changes simply incorporated, and the supplementary material that we would like to provide to the readers.

The following are our detailed responses to the comments by the reviewers:

\Reviewer{\#1}

\begin{response}{The manuscript of Fadugba et al. "Effects of pre-existing structures on the seismicity of the Charlevoix Seismic Zone" introduces a modeling study assessing the stress perturbation due to a specific tectonic structure, that is, a rift system overprinted on the impact crater in Charlevoix Seismic Zone, eastern Canada. The effects of possible factors, including fault geometry, frictional strengths along faults, elastic properties of the crater and the different velocity models, are being discussed by comparing the causal stress perturbations to relocated seismic distributions. They study the combined effects of the impact zone and rift faults, confirm the importance of the two tectonic factors in explaining the stress perturbation, and provide a quantified estimation of the elastic contrast within and outside the impact crater. Overall, I find that their research approach is well designed. While the result is clearly presented, my main concern is how to justify conclusions based on model comparisons with single factor control.}
\end{response}

\begin{response}{I recommend the authors to justify the assumption of the independency effect of involved factors on stress perturbations, or that they have consistently monotonous effects.}
    The indepnedency effect, if we understand it correctly, is not assumed but achieved by our experiment design, in which a reference model is compared with a model with only one parameter changed. We also believe our original results were already showing that that the controlled parameters have consistently monotonous effects. However, in this revision, we have run more models so that all the explored parameters have more regular intervals and thus the monotonicity of model responses can be exposed more clearly. For more details about the changes we have made in this regard, please refer to our response right below as well as those to the reviewer's specific comments.
\end{response}

\begin{response}{Also, I would be curious to know the sensitivity of your model to these factors, so that we will have a rough idea of the model resolution. It will also support your choice of parameter intervals, for example, moduli ratio and $\mu$ (Table 1). Thus, I suggest a moderate revision.}

    We have addressed this concern by running new models, making parameter intervals more regular. The combined set of models not only clearly exhibit the sensitivity but also show that it is a monotonous one. We have justified that the choice of model parameters such as $\mu$, moduli ratio, and have included additional figures in the supplementary information (Figs. S3, S4 and S6) 
    %\annote[EC]{(Figs. S1-S4 and S6)}{Not all are relevant to this comment. Refer to only those directly relevant.}.
\end{response}

%\textbf{We addressed the line-by-line comments below.}

\begin{response}{1. Line 113: Add a supplementary figure to support your statement of consistent solutions for domain sizes of 1 km and 2 km.}

We have added Fig. S1 in the supplementary information.

\end{response}

\begin{response}{2. Line 116: Introduce the computational efficiency of your model, like how much cores your model requests, how long it takes. You can add this information into Table 1 if it varies much between different models.}

  We have added the computational efficiency of our model in the model geometry section (Lines 125-130) of the manuscript. We did not add the computational efficiency to Table 1 because it does not change significantly among the models except for the SD65R25 model, which took about twice longer to run for the same model time. We do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper.

  %\add[EC]{, which took about twice longer to run for the same model time.} \annote[EC]{which may be due to the shallower fault dips.}{The shallower fault dips are the difference of SD65R25 from the others but does not directly explain why this model should take much less time. We can go ahead and speculate about possible reasons but it would be just enough to say that we do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper.}
  %\annote[EC]{except for the SD65R25 model}{This model then needs further explanation why it took a significantly longer or short time}. 
  %\note[EC]{Is there a reason why you did not follow the reviewer's suggestion to add this into to Table 1?}
\end{response}

\begin{response}{3. Line 131-133: I do not understand why you set your boundary conditions as the differential stress reaches 706 MPa. Do you set a criterion for shear stress somewhere else? Please make it more clear.}

  %\annote[EC]{We agree with the reviewer}{Agree only when you are sure that doing so would not negatively affect your arguments, assumptions or the overall integrity of your paper. Never confess; only justify.} on the high differential stress at seismogenic depth in our study, due to}
  The differential stress of 706 MPa at 10 km depth is based on Byerlee's law under the assumption of  \add[EC]{$\mu$ equal to XX and} the absence of pore-fluid pressure. The full derivation of this value is now provided in the supplementary information. Shear stress was not considered as a stopping criterion. In addition, we have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 528-538).

\end{response}

\begin{response}{4. Section 2.3: You did not mention the values of bulk modulus and shear modulus applied in your calculation.}

  PyLith, the modeling software used in this study, internally converts P and S wave velocities and density to bulk and shear moduli. \add[EC]{For readers' reference, however, we now list representative values of elastic moduli in Table 1.}\note[EC]{Seun, please take care of this.}
\end{response}

\begin{response}{5. Line 154-156: As I said in the main concern, you need to justify the reduction of 10\% from the velocity model to represent the impact crater area, instead of, for example, 2\%, 5\%, or 20\%.}

  We ran extra models to have a series of models from 0 to 20 \% reduction. No significant changes in the model results were found in these models. The 10\% reduction in the density of corresponding crustal rock is to model a \annote[EC]{realistic}{Without further justification or proper citation of supporting evidence, you cannot say this. Support it or remove it.} damaged crustal rock \annote[EC]{(Lines 174-175).}{The main text should be accordingly revised. The point should be that, in all the presented models, the impact structure has elastic moduli reduced by 10 \% relative to the surrounding crust but the model results were insensitive to other amounts of reduction as see in Fig. S3 in the supplementary information.}
\end{response}

\begin{response}{6. Line 164-165: According to Marone (1995), the assumption of zero cohesion could be valid for the pre-existing fractures sheared at low normal stress. In your models, the fault depth reaches up to 40 km (at least the stress change at 25 km depth is discussed), which is not the case for a low normal stress. It will be helpful to discuss the situation of faults with reasonable cohesive stress values, especially how this influence the fitting of friction coefficient.}

    The faults in our models extend to 40 km but \annote[EC]{slips on them occur only down to about 10 km due to our stopping criterion.}{Correct this if I'm wrong.} Since the non-slipping portion of the faults are irrelevant, the condition of low normal stress is already being satisfied. For reference, however, we have explored non-zero values of cohesion and their impact on the results are shown in Fig. S4 in the supplementary information.
\end{response}

\begin{response}{7. Line 226-231: When evaluate the modeling result, I suggest the authors to quantify the fitting between the simulated stress change and the earthquake hypocenters. It will help convincing the readers of preferred model parameters. For example, I do not see it necessarily to prefer the frictional coefficient equals to 0.3 over 0.4 based on Figure 11.}

   We have added a quantitative assessment
   %\annote[EC]{qualitative assessment}{Why is it still only qualitative? Have you tried one of the ideas I suggested? If none worked, you are supposed to let me know and look at another solution. Unless you have a good reason to ignore the reviewer's suggestion, the editor and the reviewer would be very curious why you didn't follow the suggestion. This is indeed the main reason why I asked if you had run into any trouble while revising the manuscript. Please take care of this and let me know if you need hlep.} \add[OF]{I am sorry it was a typo. I meant quantitative.}
   of the correlation between the change in differential stress and the observed seismicity \add[OF]{by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\%} without accounting for uncertainty in hypocenter relocation (Line 199-202). We added a discussion on the choice of the friction coefficient in Lines 506-509.
    %: 1) the change in differential stress maps changes with fault geometry, and we have established an along-strike variation in the fault dips in this study; and 2) the 3D velocity model is very well defined in the upper 5 km depth which may introduced an uncertainty in the hypocenter relocation.
\end{response}

\begin{response}{8. Line 312: You need to justify the mesh size of 4 km in Section 2.1.}

  \annote[EC]{We have justified}{You cannot simply say like this. Do describe what is the justification here as well.} the mesh size in Section 2.1 (Lines 118-121).
\end{response}

\begin{response}{9. Line 321-323: It is not sufficient to reject the possibility of positive Coulomb stress change along the entire faults based on limited observation period of seismicity distribution, that is, consider the northern segment as aseismic creeping. Alternatively, it is possible that the northern segment of the fault accumulates the stress loading and has longer time interval to rupture as a seismic asperity. To distinguish these two possibilities, I suggest check the distribution of historical earthquakes, or GPS observations of the fault aseismic slip.}

  \annote[EC]{Some earthquakes occurred at the SW region outside the impact structure, as shown in the updated Fig. 1. However, reexamination of historical earthquakes in the Charlevoix area by Stevens (1980) also supports a finite extent of the observed seismicity in the CSZ.}{This response is not addressing the reviewer's concern. }
\end{response}

\textbf{Minor and typographic errors}

\begin{response}{1. Line 35-36: "The impact crater has a radius of 28 km and is 15 km deep." Please add an appropriate reference here.}

  We have added an appropriate reference (Line 39).
\end{response}

\begin{response}{2. Line 428: Please add a reference to support the implication of these rift faults have varied dip angle along depth.}

  We have added an appropriate reference (Line 436).
\end{response}

\textbf{Comments on Figures and Tables:}

\begin{response}{1. Mark the crater and faults as a reference in Figures 6, 8 ,10-12, as what you did for Figures 7 and 9. It helps readers to compare between your results.}

  We have marked the crater as a reference in the figures (i.e., Figs. 6, 8, 10-12). We didn't mark the faults so that it won't mask the features and the hypocenters plotted on the maps. The figures are significantly modified by abrupt changes in the vicinity of the rift faults.
\end{response}

\begin{response}{2. Figure 10(B): Check the last two plots for the change in the orientation of SHmax. It should be the model with no crater reduces the model with no faults (reference model).}

  The figures are similar to those of the SH$_{\max}$ orientation because of the very low SH$_{\max}$ orientation in the corresponding reference model.
\end{response}

\Reviewer{\#2}
\begin{response}{Maurice Lamontagne, Geological Survey of Canada

This study is important to better understand the characteristics of the seismicity of the Charlevoix Seismic Zone. It puts to light that it is the combination of the meteor impact structure and the rift faults that determine the positions of most earthquakes. Although the modelling does not explain the whole hypocenter distribution in Charlevoix, it is one step forward in our understanding of the local seismotectonics. I have added a few comments directly in the attached pdf.}
    We thank the reviewer for the critical assessment, and comments in the attached pdf. We have modified the manuscript accordingly. We have ALSO addressed the comments by providing more explanation in the manuscript with all changes highlighted in color.
\end{response}

\begin{response}{I think that Charlevoix is considered a meteor impact structure more than a crater. Although the difference is sometimes nebulous between the two, I would prefer if the authors referred to the impact structure. Another word that could be used is astrobleme ("star wound"). There are some interesting links that explain the difference.}

  We have changed the words "impact crater" and "crater" to "impact structure" throughout the manuscript.
\end{response}

\begin{response}{An aspect that may have been missed is the fact that the epicentral map, such as Fig. 1, does not show a complete view of the regional seismicity. The SSW portion of the St. Lawrence River (upstream towards Quebec City) is also active (although not as much as the interior of the astrobleme). The dataset shown is the one of Powell and Lamontagne (2017) which was a selection of events based on their locations within the network of seismograph stations, but for this map view, I suggest that a more complete dataset is presented. The data can be downloaded from the earthquakescanada web site.}

  We have plotted the complete dataset in Fig. 1. We represented the relocated hypocenters of Powell and Lamontagne (2017) as circles and the other earthquakes that are not in the relocated catalog as diamonds.
\end{response}

\begin{response}{In a couple of places, authors use the expression 'large magnitude earthquakes'... Except for the 1925 M 6.2 earthquake, we are uncertain about the exact position of the 'large' earthquakes in Charlevoix (four other M6+; 1663; 1791, 1860,1870... although 1870 M 6.5 was probably near Ile-aux-Coudres). It would be better to say that the M4+ earthquakes, appear to occur more often in the NE portion of the CSZ. Stevens (1980) also found that some M4+ earthquakes of the period 1924-1980 also occurred at the SE end.}

  We have edited the manuscript accordingly (see Lines 448-450). We have also included the findings of Steven (1980) in our discussion.
\end{response}

\begin{response}{The authors write that the focal mechanisms of the CSZ were not well defined. I disagree with them. You can check this OF report, which shows that the Quality 'A' mechanisms were well defined by the P first motions. I think that Mazzotti used most of them in his catalog.
https://geoscan.nrcan.gc.ca/starweb/geoscan/servlet.starweb?
path=geoscan/downloade.web&search1=R=209378}

 The focal mechanisms are good, and we suggest that the focal mechanisms can be further constrained using waveform modeling to validate the magnitude of the stress rotation (Lines 561-563).
\end{response}

\begin{response}{The model assumes an absence of pore-fluid pressure along faults. For this reason, the stress difference used by the authors is very high at seismogenic depth. It is my impression that worldwide, direct measurements and modelling of tectonic stresses suggest that the maximum crustal stress difference has an upper limit of about 100-200 MPa... very different from the 706 MPa suggested by the authors.
I think that the authors should discuss the possibility that high pore-fluid pressures exist at depth and their possible consequences. One aspect would be that faults could be reactivated at smaller angles from the maximum compressive stress and that the stress difference would have more realistic values.}

  The differential stress of 706MPa at 10 km depth is due to the assumption of the absence of pore-fluid pressure. The higher stopping criterion in our study is necessary to make faults slip at seismogenic depth under the assumption. We have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 528-538).
\end{response}

\end{document}

### 2019-06-27 Supporting_Information.tex
started a git project

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUtmpl.tex: this template file is for articles formatted with LaTeX2e,
% Modified December 2018
%
% This template includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements.
%
% FOR FIGURES, DO NOT USE \psfrag
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% IMPORTANT NOTE:
%
% SUPPORTING INFORMATION DOCUMENTATION IS NOT COPYEDITED BEFORE PUBLICATION.
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: Set the \documentclass
%
%
% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
%
% Choose the journal abbreviation for the journal you are
% submitting to:

% jgrga JOURNAL OF GEOPHYSICAL RESEARCH (use for all of them)
% gbc   GLOBAL BIOCHEMICAL CYCLES
% grl   GEOPHYSICAL RESEARCH LETTERS
% pal   PALEOCEANOGRAPHY
% ras   RADIO SCIENCE
% rog   REVIEWS OF GEOPHYSICS
% tec   TECTONICS
% wrr   WATER RESOURCES RESEARCH
% gc    GEOCHEMISTRY, GEOPHYSICS, GEOSYSTEMS
% sw    SPACE WEATHER
% ms    JAMES
% ef    EARTH'S FUTURE
%
%
%
% (If you are submitting to a journal other than jgrga,
% substitute the initials of the journal for "jgrga" below.)

\documentclass[draft,jgrga]{agutexSI2019}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  SUPPORTING INFORMATION TEMPLATE
%
%% ------------------------------------------------------------------------ %%
%
%
%Please use this template when formatting and submitting your Supporting Information.

%This template serves as both a “table of contents” for the supporting information for your article and as a summary of files.
%
%
%OVERVIEW
%
%Please note that all supporting information will be peer reviewed with your manuscript. It will not be copyedited if the paper is accepted.
%In general, the purpose of the supporting information is to enable authors to provide and archive auxiliary information such as data tables, method information, figures, video, or computer software, in digital formats so that other scientists can use it.
%The key criteria are that the data:
% 1. supplement the main scientific conclusions of the paper but are not essential to the conclusions (with the exception of
%    including %data so the experiment can be reproducible);
% 2. are likely to be usable or used by other scientists working in the field;
% 3. are described with sufficient precision that other scientists can understand them, and
% 4. are not exe files.
%
%USING THIS TEMPLATE
%
%***All references should be included in the reference list of the main paper so that they can be indexed, linked, and counted as citations.  The reference section does not count toward length limits.
%
%All Supporting text and figures should be included in this document. Insert supporting information content into each appropriate section of the template. To add additional captions, simply copy and paste each sample as needed.

%Tables may be included, but can also be uploaded separately, especially if they are larger than 1 page, or if necessary for retaining table formatting. Data sets, large tables, movie files, and audio files should be uploaded separately. Include their captions in this document and list the file name with the caption. You will be prompted to upload these files on the Upload Files tab during the submission process, using file type “Supporting Information (SI)”

%IMPORTANT NOTE ON FIGURES AND TABLES
% Placeholders for figures and tables appear after the \end{article} command, after references.
% DO NOT USE \psfrag or \subfigure commands.
%
 \usepackage{graphicx}

%  Uncomment the following command to allow illustrations to print
%   when using Draft:
 \setkeys{Gin}{draft=false}
%
% You may need to use one of these options for graphicx depending on the driver program you are using. 
%
% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
% [oztex], [textures]
%
%
%% ------------------------------------------------------------------------ %%
%
%  ENTER PREAMBLE
%
%% ------------------------------------------------------------------------ %%

% Author names in capital letters:
%\authorrunninghead{BALES ET AL.}

% Shorter version of title entered in capital letters:
%\titlerunninghead{SHORT TITLE}

%Corresponding author mailing address and e-mail address:
\authoraddr{Corresponding author: Oluwaseun Idowu Fadugba,
Center for Earthquake Research and Information, The University of Memphis, Memphis, TN 38152. (ifadugba@memphis.edu)}

\begin{document}

%% ------------------------------------------------------------------------ %%
%
%  TITLE
%
%% ------------------------------------------------------------------------ %%

%\includegraphics{agu_pubart-white_reduced.eps}

\title{Supporting Information for ``Effects of pre-existing structures on the seismicity of the Charlevoix Seismic Zone"}
%
% e.g., \title{Supporting Information for "Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
%
%DOI: 10.1002/%insert paper number here%

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

% List authors by first name or initial followed by last name and
% separated by commas. Use \affil{} to number affiliations, and
% \thanks{} for author notes.
% Additional author notes should be indicated with \thanks{} (for
% example, for current addresses).

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}

\authors{Oluwaseun Idowu Fadugba\affil{1}, Eunseo Choi\affil{1}, and Christine A. Powell\affil{1}}

% \affiliation{1}{First Affiliation}
% \affiliation{2}{Second Affiliation}
% \affiliation{3}{Third Affiliation}
% \affiliation{4}{Fourth Affiliation}

\affiliation{1}{Center for Earthquake Research and Information, The University of Memphis, Memphis, TN 38152}
%(repeat as many times as is necessary)

%% ------------------------------------------------------------------------ %%
%
%  BEGIN ARTICLE
%
%% ------------------------------------------------------------------------ %%

% The body of the article must start with a \begin{article} command
%
% \end{article} must follow the references section, before the figures
%  and tables.

\begin{article}

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

\noindent\textbf{Contents of this file}
%%%Remove or add items as needed%%%
\begin{enumerate}
%\item Text S1 to Sx
\item Figure S1
\item Figure S2
\item Figure S3
\item Figure S4
\item Figure S5
\item Figure S6
%\item Tables S1 to Sx
%if Tables are larger than 1 page, upload as separate excel file
\end{enumerate}

%\noindent\textbf{Additional Supporting Information (Files uploaded separately)}
%\begin{enumerate}
%\item Captions for figure S1
%\item Captions for large Tables S1 to Sx (if larger than 1 page, upload as separate excel file)
%\item Captions for Movies S1 to Sx
%\item Captions for Audio S1 to Sx
%\end{enumerate}

%Type or paste your text here. The introduction gives a brief overview of the supporting information. You should include information %about as many of the following as possible (when appropriate):
% 1. a general overview of the kind of data files;
% 2. information about when and how the data were collected or created;
% 3. a general description of processing steps used;
% 4. any known imperfections or anomalies in the data.

%\clearpage
\vspace{10mm} %5mm vertical space

\noindent\textbf{Introduction}

This supplement presents the resolution test in our study, the derivation of the stopping criterion, effect of density ratio, cohesion, and moduli ratio on stress models.

\vspace{10mm} %5mm vertical space

\noindent\textbf{Resolution Test}

We create stress models with element sizes ranging from 1 to 8 km to examine the effect of mesh resolution on $\sigma_{D}$ and $\phi_{\max}$ using the SFR25 domain geometry. We perform the resolution test by comparing the displacement components and differential stress in the entire domain in each model with respect to the model with element size of 1 km. We determine the errors in differential stress, for example, using the equation:
%
\[
 E\sigma_{D}^{4km} = \frac{[\sum_{k=0}^n (\sigma_{D}^{4km} - \sigma_{D}^{1km})_{k}^2]^\frac{1}{2}}
{[\sum_{k=0}^n (\sigma_{D}^{1km})_{k}^2]^\frac{1}{2}},
\]
%
where k represents the index for data points and $ E\sigma_{D}^{4km} $ is the error in $\sigma_{D}$ in model with element size of 4 km relative to 1 km.

\vspace{5mm} %5mm vertical space

\begin{sidewaysfigure}
\setfigurenum{S1}
\includegraphics[width=25pc]{Figures/res_test_CSZ.png}
\caption{Errors in displacement components and differential stress ($\sigma_{D}$) for models with element sizes ranging from 2 to 8 km relative to a model with 1 km element size.}
\label{S1}
\end{sidewaysfigure}

\vspace{10mm} %5mm vertical space

This resolution test shows that the error generally increases with mesh resolution (Fig. \ref{S1}). %For example, the model has an error of about 0.02 and 0.16 in the $\sigma_{D}$ and $\phi_{\max}$ in element size of 2 km relative to 1 km, respectively (Fig. \ref{S2}). The error values increase to 0.06 and 0.26 when the element size is 4 km. 
The errors in displacement components and differential stress in models with element sizes of 2 km is less than 5 \% of the corresponding values in the model with 1 km resolution. The errors are less than 10 \% for models with element sizes below 4 km. In our study, we will use an element size of 2 km for our fault models. However, due to expensive computation time, we will use an element size of 4 km to evaluate model parameters, e.g., coefficient of friction.

\vspace{10mm} %5mm vertical space

\noindent\textbf{Stopping criterion of differential stress at 10 km depth}
\vspace{10mm} %5mm vertical space

\begin{sidewaysfigure}
\setfigurenum{S2}
\includegraphics[width=25pc]{Figures/Calc_diff_stress.png}
\caption{Determining the differential stress for stopping criterion.}
\label{S2}
\end{sidewaysfigure}

\vspace{5mm} %5mm vertical space

From $\Delta$ABC,
\[
 \sin(\alpha) = \frac{\sigma_{1}-\sigma_{3}}{2}/[\frac{250}{3} + \frac{\sigma_{1}+\sigma_{3}}{2}],
\]
%
\[
 \sin(\alpha) = \frac{3(\sigma_{1}-\sigma_{3})}{3(\sigma_{1}+\sigma_{3})+500},
\]
%
\[
 \sigma_{1} = \frac{\sigma_{3}+[\sigma_{3}+\frac{500}{3}]\times \sin(\alpha)}{1-\sin(\alpha)},
\]

Based on Byerlee's law, $\tau$  = 50 MPa + 0.6$\,\sigma_n$, under the assumption of absence of pore-fluid pressure along the rift faults, $\tan(\alpha) = 0.6$, hence, $\sin(\alpha)= 0.5145$. $\sigma_{3}$ corresponds to the lithostatic stress, and assuming it is equal to 250 MPa at 10 km depth, gives $\sigma_{1}$ = 956.4882 MPa. Hence, the differential stress at 10 km depth with no pore-fluid pressure ($\sigma_{D} = \sigma_{1} - \sigma_{3})$ is 706.4882 MPa.

\vspace{10mm} %5mm vertical space

\noindent\textbf{Effects of density ratio in the impact structure}

The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio.  The maps show no significant change with density ratio. We use density ratio of 10\% in this study to model a realistic damaged crustal rock. 
\vspace{10mm} %5mm vertical space

\begin{sidewaysfigure}
\setfigurenum{S3}
\includegraphics[width=25pc]{Figures/effect_of_density.png}
\caption{Effect of impact structure-crust density ratio on the $\Delta\sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ at 10 km depth. Earthquakes within 2 km of each depth slice are represented by black dots in \ref{S3}A. The outline of the impact structure is represented as black circle. Each figure is 70 $\times$ 70 km.}
\label{S3}
\end{sidewaysfigure}

\vspace{10mm} %5mm vertical space

\noindent\textbf{Effect of cohesion}

We compute $\Delta \sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ in a series of models in which the rift faults dip at 70$^{\circ}$ (i.e., SD70R25) but their cohesion ($C$) is varied systematically at a constant coefficient of friction ($\mu$) of 0.3. We assume that the fault parameters are the same for each rift fault and uniform throughout the fault surfaces. Six models with 0, 3, 5, 10, 20 and 30 MPa are constructed (Fig. \ref{S4}).

Magnitudes of $\Delta\sigma_D^{\prime}$ and $\phi_{\max}$ decrease with increasing cohesion. $\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity at all the fault cohesions, especially well when the cohesion is less than 5 MPa (Fig. \ref{S4}A). However, the models could not explain some earthquakes in the SW corner of the crater. The $\Delta\sigma_D^{\prime}$ is not affected by a change in cohesion between 0 and 5 MPa. However, $\phi_{\max}$ approaches the reference no-fault model as the cohesion increases (Fig. \ref{S4}B). As cohesion increases, $\Delta\phi_{\max}$ decreases in value and the rotation is concentrated in the fault region outside the crater (Fig. \ref{S4}C). $\Delta\phi_{\max}$ is up to 10.8$^\circ$ when the cohesion is less than 5 MPa.

Figure \ref{S4} shows that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope. We use a cohesion value of 0 MPa to explain the spatial distribution of observed seismicity in the CSZ.

\vspace{10mm} %5mm vertical space

\begin{sidewaysfigure}
\setfigurenum{S4}
\includegraphics[width=25pc]{Figures/SD70R25C_S2.png}
\caption{Same as \ref{S3} but for the models with different cohesion values.}
\label{S4}
\end{sidewaysfigure}

\vspace{10mm} %5mm vertical space

\noindent\textbf{Effects of no impact structure (SD70R100 model)}

The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model.  $\Delta\sigma_{D}^{\prime}$ shows increased $\sigma_{D}$ relative to SNFR25 throughout the entire length of the rift faults at and below 15 km depth, hence the model predicts earthquakes in those regions.

\vspace{10mm} %5mm vertical space

\begin{sidewaysfigure}
\setfigurenum{S5}
\includegraphics[width=25pc]{Figures/SD70R100_S1.png}
\caption{Percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the SNFR25 at various depths depths from the SD70R100 model. Earthquakes within 2 km of each depth slice are represented by black dots in \ref{S3}A. Each figure is 70 $\times$ 70 km.}
\label{S5}
\end{sidewaysfigure}

\vspace{10mm} %5mm vertical space
%\pagebreak

\noindent\textbf{Effects of impact structure-crust moduli ratio}

We test the response of the model results with different impact structure-crust moduli ratio. The model with a moduli ratio of 1.0 does not have the impact crater. The models show a better spatial correlation with the observed seismicity when the moduli ratio is 0.25.

\vspace{10mm} %5mm vertical space

\begin{sidewaysfigure}
\setfigurenum{S6}
\includegraphics[width=25pc]{Figures/effect_of_moduli_ratio.png}
\caption{Same as \ref{S3} but for the models with different impact structure-crust moduli ratio.}
\label{S6}
\end{sidewaysfigure}

\vspace{10mm} %5mm vertical space

%\pagebreak

%\begin{figure}
%\setfigurenum{S1} %%You can change number for each figure if you want, not required. "S" prepended automatically.
%\noindent\includegraphics[width=\textwidth]{Figures/SD70R100/F1_r10_m3_c0_sup.png}
%\caption{caption}
%\label{epsfiguresample}
%\end{figure}

%Delete all unused file types below. Copy/paste for multiples of each file type as needed.
%\noindent\textbf{Text S1.}

%Type or paste text here. This should be additional explanatory text, such as: extended descriptions of results, full details of models, extended lists of acknowledgements etc.  It should not be additional discussion, analysis, interpretation or critique. It should not be an additional scientific experiment or paper.
%
%Repeat for any additional Supporting Text

%%Enter Data Set, Movie, and Audio captions here
%%EXAMPLE CAPTIONS

%\noindent\textbf{Data Set S1.} %Type or paste caption here.
%upload your dataset(s) to AGU's journal submission site and select "Supporting Information (SI)" as the file type. Following naming %convention: ds01.

%Repeat for any additional Supporting data sets

%\noindent\textbf{Movie S1.} %Type or paste caption here.
%upload your movie(s) to AGU's journal submission site and select, "Supporting Information %(SI)" as the file type. Following naming convention: ms01.

%Repeat any additional Supporting movies

%\noindent\textbf{Audio S1.} %Type or paste caption here.
%upload your audio file(s) to AGU's journal submission site and select "Supporting Information %(SI)" as the file type. Following naming convention: auds01.

%Repeat for any additional Supporting audio files

%%% End of body of article:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Notation section goes here
%
% Notation -- End each entry with a period.
% \begin{notation}
% Term & definition.\\
% Second term & second definition.\\
% \end{notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% ------------------------------------------------------------------------ %%
%%  REFERENCE LIST AND TEXT CITATIONS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
%
% \bibliography{<name of your .bib file>} do not specify file extension
%
% no need to specify bibliographystyle
%
% Note that ALL references in this supporting information file must also be referenced in the primary manuscript
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% if you get an error about newblock being undefined, uncomment this line:
%\newcommand{\newblock}{}
%\bibliography{<name of your .bib file>}

%Reference citation instructions and examples:
%
% Please use ONLY \cite and \citeA for reference citations.
% \cite for parenthetical references
% ...as shown in recent studies (Simpson et al., 2019)
% \citeA for in-text citations
% ...Simpson et al (2019) have shown...
% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
%
%
%...as shown by \citeA{jskilby}.
%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
%...has been shown \cite{jskilbye}.
%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
%
% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
%

%% ------------------------------------------------------------------------ %%
%
%  END ARTICLE
%
%% ------------------------------------------------------------------------ %%
\end{article}
\clearpage

% Copy/paste for multiples of each file type as needed.

% enter figures and tables below here: %%%%%%%
%
%
%
%
% EXAMPLE FIGURES
% ---------------
% If you get an error about an unknown bounding box, try specifying the width and height of the figure with the natwidth and natheight options.
% \begin{figure}
%\setfigurenum{S1} %%You can change number for each figure if you want, not required. "S" prepended automatically.
% \noindent\includegraphics[natwidth=800px,natheight=600px]{samplefigure.eps}
%\caption{caption}
%\label{epsfiguresample}
%\end{figure}
%
%
% Giving latex a width will help it to scale the figure properly. A simple trick is to use \textwidth. Try this if large figures run off the side of the page.
% \begin{figure}
% \noindent\includegraphics[width=\textwidth]{anothersample.png}
%\caption{caption}
%\label{pngfiguresample}
%\end{figure}
%
%
%\begin{figure}
%\noindent\includegraphics[width=\textwidth]{athirdsample.pdf}
%\caption{A pdf test figure}
%\label{pdffiguresample}
%\end{figure}
%
% PDFLatex does not seem to be able to process EPS figures. You may want to try the epstopdf package.
%
%
% ---------------
% EXAMPLE TABLE
%
%\begin{table}
%\settablenum{S1} %%Change number for each table
%\caption{Time of the Transition Between Phase 1 and Phase 2\tablenotemark{a}}
%\centering
%\begin{tabular}{l c}
%\hline
% Run  & Time (min)  \\
%\hline
%  $l1$  & 260   \\
%  $l2$  & 300   \\
%  $l3$  & 340   \\
%  $h1$  & 270   \\
%  $h2$  & 250   \\
%  $h3$  & 380   \\
%  $r1$  & 370   \\
%  $r2$  & 390   \\
%\hline
%\end{tabular}
%\tablenotetext{a}{Footnote text here.}
%\end{table}
% ---------------
%
% EXAMPLE LARGE TABLE (UPLOADED SEPARATELY)
%\begin{table}
%\settablenum{S1} %%Change number for each table
%\caption{Time of the Transition Between Phase 1 and Phase 2\tablenotemark{a}}
%\end{table}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% IF YOU HAVE MULTI-LINE EQUATIONS, PLEASE
% BREAK THE EQUATIONS INTO TWO OR MORE LINES
% OF SINGLE COLUMN WIDTH (20 pc, 8.3 cm)
% using double backslashes (\\).

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

%% ------------------------------------------------------------------------ %%
%
%  SIDEWAYS FIGURE AND TABLE EXAMPLES
%
%% ------------------------------------------------------------------------ %%
%
% For tables and figures, add \usepackage{rotating} to the paper and add the rotating.sty file to the folder.
% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
%
% \begin{sidewaysfigure}
% \includegraphics[width=20pc]{samplefigure.eps}
% \caption{caption here}
% \label{label_here}
% \end{sidewaysfigure}
%
%
%
% \begin{sidewaystable}
% \caption{}
% \begin{tabular}
% Table layout here.
% \end{tabular}
% \end{sidewaystable}
%
%

### 2019-06-27 main_full_manuscript.tex
started a git project

o%% March 2018
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
%
% This file includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements, including customized APA reference formatting.
%
% You may copy this file and give it your
% article name, and enter your text.
%
%
% Step 1: Set the \documentclass
%
% There are two options for article format:
% 
% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
%

%% To submit your paper:
\PassOptionsToPackage{inline}{trackchanges}
\documentclass[draft]{agujournal2018}
\usepackage{apacite}
\usepackage{comment}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
\addeditor{EC}
\addeditor{OF}

%%%%%%%

%% Enter journal name below.
%% Choose from this list of Journals:
%
% JGR: Atmospheres
% JGR: Biogeosciences
% JGR: Earth Surface
% JGR: Oceans
% JGR: Planets
% JGR: Solid Earth
% JGR: Space Physics
% Global Biogeochemical Cycles
% Geophysical Research Letters
% Paleoceanography and Paleoclimatology
% Radio Science
% Reviews of Geophysics
% Tectonics
% Space Weather
% Water Resources Research
% Geochemistry, Geophysics, Geosystems
% Journal of Advances in Modeling Earth Systems (JAMES)
% Earth's Future
% Earth and Space Science
% Geohealth
%
% ie, \journalname{Water Resources Research}
\journalname{JGR: Solid Earth}

\begin{document}

%% ------------------------------------------------------------------------ %%
%  Title
% 
% (A title should be specific, informative, and brief. Use
% abbreviations only if they are defined in the abstract. Titles that
% start with general keywords then specific terms are optimized in
% searches)
%
%% ------------------------------------------------------------------------ %%

% Example: \title{This is a test title}

\title{Effects of pre-existing structures on the seismicity of the Charlevoix Seismic Zone}

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

% Authors are individuals who have significantly contributed to the
% research and preparation of the article. Group authors are allowed, if
% each author in the group is separately identified in an appendix.)

% List authors by first name or initial followed by last name and
% separated by commas. Use \affil{} to number affiliations, and
% \thanks{} for author notes.  
% Additional author notes should be indicated with \thanks{} (for
% example, for current addresses).

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antarctica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}

\authors{Oluwaseun Idowu Fadugba\affil{1}, Eunseo Choi\affil{1}, and Christine A. Powell\affil{1}}

% \affiliation{1}{First Affiliation}
% \affiliation{2}{Second Affiliation}
% \affiliation{3}{Third Affiliation}
% \affiliation{4}{Fourth Affiliation}

\affiliation{1}{Center for Earthquake Research and Information, The University of Memphis, Memphis, TN 38152}
%(repeat as many times as is necessary)

%% Corresponding Author:
% Corresponding author mailing address and e-mail address:

% (include name and email addresses of the corresponding author.  More
% than one corresponding author is allowed in this LaTeX file and for
% publication; but only one corresponding author is allowed in our
% editorial system.)

% Example: \correspondingauthor{First and Last Name}{email@address.edu}

\correspondingauthor{Oluwaseun Idowu Fadugba}{ifadugba@memphis.edu}

%% Keypoints, final entry on title page.

% Example: 
% \begin{keypoints}
% \item	List up to three key points (at least one is required)
% \item	Key Points summarize the main points and conclusions of the article
% \item	Each must be 100 characters or less with no special characters or punctuation 
% \end{keypoints}

%  List up to three key points (at least one is required)
%  Key Points summarize the main points and conclusions of the article
%  Each must be 100 characters or less with no special characters or punctuation

\begin{keypoints}

  \item The CSZ seismicity and stress orientations are the combined effects of the rift faults and the impact \change[OF]{crater}{structure}.

  \item Planar faults we considered can explain the observed seismicity but only 50$\%$ of the stress rotation.

  \item \change[OF]{A crater}{An impact structure} four times less elastically stiff than the surrounding crust can explain the seismicity in the CSZ.

\end{keypoints}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
% A good abstract will begin with a short description of the problem
% being addressed, briefly describe the new data or analyses, then
% briefly states the main conclusion(s) and how they are supported and
% uncertainties. 
%% ------------------------------------------------------------------------ %%

%% \begin{abstract} starts the second page

\begin{abstract}
The Charlevoix Seismic Zone (CSZ) \change[OF]{occurs}{is located} along the early Paleozoic St. Lawrence rift zone in southeastern Quebec at the location of a major Devonian impact \change[OF]{crater}{structure}. The \change[OF]{crater}{impact structure} superimposed major, steeply dipping basement faults trending \add[OF]{approximately} N35$^\circ$E. \change[OF]{Many}{Approximately 250} earthquakes are recorded each year in the CSZ and are concentrated within and beneath the impact \change[OF]{crater}{structure}. \change[OF]{Some large-magnitude}{Most M4+} earthquakes associated with the rift faults occurred outside the \change[OF]{crater}{impact structure}. Apart from the unique distribution of earthquakes in the CSZ, stress inversion of focal mechanisms shows stress rotations within the CSZ, and in the CSZ relative to the stress orientation determined from borehole breakouts. The primary goal of this research is to investigate the combined effects of the pre-existing structures and regional stresses on earthquake activity and stress rotations in the CSZ. We approach this using PyLith, a finite-element code for simulations of crustal deformation. Adopting the results from recent hypocenter relocation and 3D tomography studies, we modify the locations and dips of the rift faults and assess the effect of the new fault geometries on stress distributions. We also discuss the effects of resolved velocity anomalies. We find that the observed stress rotation is due to the combined effect of the rift faults and the \change[OF]{crater impact}{impact structure}. 1D velocity models of the CSZ with an embedded \change[OF]{crater}{impact structure} and a combination of 65$^\circ$-40$^\circ$-40$^\circ$ and constant 70$^\circ$ fault dip models \add[OF]{for the three main rift faults} with a \add[OF]{very low} friction coefficient of 0.3 and cohesion of 0 MPa can explain the observed seismicity and more than 50$\%$ of the stress rotations.
\end{abstract}

\section{Introduction}
The Charlevoix Seismic Zone (CSZ) is the most seismically active region in eastern Canada. The CSZ is within the \change[OF]{Cambro-Ordovician}{Late Precambrian} St. Lawrence rift zone in southeastern Quebec and is overprinted by a Devonian impact \change[OF]{crater}{structure} (Fig. \ref{figone}). The impact \change[OF]{crater}{structure} has a radius of 28 km and is \change[OF]{15}{approximately 12} km deep \add[OF]{$\citep{RONDOT1994}$}. The \change[OF]{crater}{impact structure} has a more damaged interior zone with a surface radius of 18 km (Fig. \ref{figone}). The impact \change[OF]{crater}{structure} is superimposed on three major rift faults trending N35$^\circ$E and dipping to the southeast~\citep{anglin1984,Rondot_1971}. The CSZ \change[OF]{is considered to pose a high risk of seismic hazard}{has a high seismic hazards} due to its history of generating \change[OF]{large}{moderate to large} earthquakes \citep{anglin1984,lamontagne1999}. Over 200 earthquakes are recorded each year in the CSZ (Nuttli magnitude, mN \add[OF]{mostly} $\leq$ 3) \citep{Baird_2010} and the hypocenters have a bimodal distribution with peaks at 10 and 22 km depths \citep{Vlahovic_2003}. The vast majority of earthquakes in the CSZ occur within the volume bounded by the rift faults \citep{Yu_2016} and those with greater magnitudes occur northeast of the \change[OF]{crater}{impact structure}~\citep{Mazzotti_2010} (Fig. \ref{figone}).

\begin{figure}[h]
\centering
\includegraphics[width=18.5pc]{Figures/Map_of_CSZ_2.png} 
\caption{Topography\add[OF]{, bathymetry,} and seismicity of the Charlevoix Seismic Zone (CSZ) as well as the locations of the impact \change[OF]{crater}{structure} (outer cyan circle) and the more damaged inner \change[OF]{crater}{impact structure} (inner cyan circle). Small circles \add[OF]{and diamonds} are the relocated epicenters \citep{Powell_2017} \add[OF]{and the complete dataset for the years 1988-2011, respectively,} and their colors represent the focal depths. The focal mechanisms are for the earthquakes used by \citet{Mazzotti_2010} for the stress inversion. Large circles labeled as NW and SE show orientations of SH$_{\max}$ from the stress inversion of focal mechanism (SH$_S$) and from borehole breakout measurements (SH$_B$) for the earthquake clusters northwest and southeast of the \change[OF]{crater}{impact structure} center. Solid black lines mark the rift faults known in the region: GNF, Gouffre Northwest Fault; SLF, Saint-Laurent fault; CHF, Charlevoix Fault; and SSF, South Shore Fault \citep{Rondot_1971,lamontagne1999}. The inset shows the location of the CSZ in eastern Canada. Earthquake \change[OF]{epicenters}{hypocenters} from the National Resources Canada catalog for the years 1988-2011.}
\label{figone}
\end{figure}

\citet{Vlahovic_2003} conducted a three-dimensional (3D) P-wave velocity study of the CSZ. The tomography model shows several \change[OF]{high-velocity}{higher P velocity} bodies at mid-crustal depths. A significant fraction of the CSZ earthquakes occurs around these \change[OF]{high-velocity}{higher P velocity} bodies and some larger earthquakes occur along the northern edges of the high velocity bodies.

A recent earthquake relocation and tomography study of \citet{Powell_2017} using a larger number of CSZ earthquakes gives a better constraint on the geometries of these high-velocity bodies. In addition to the high-velocity bodies, \citet{Powell_2017} show that the relocated earthquakes are distributed along the rift faults and thus define the geometry of the rift faults. They also conclude that the dip of the northernmost rift fault is 65$^\circ$SE while the two other major faults dip 40$^\circ$SE.

\citet{Mazzotti_2010} determined the orientation of maximum principal horizontal stress (SH$_{\max}$) from a stress inversion of focal mechanisms in ten seismic zones in central and eastern North America including the CSZ. They found a clockwise rotation of SH$_{\max}$ in the CSZ by about 32$^\circ$ relative to the regional SH$_{\max}$ orientation of 54$^\circ$ determined from borehole breakouts \citep{Zoback_1992,Mazzotti_2010}. \citet{Mazzotti_2010} observed a number of relative stress rotations in SH$_{\max}$ determined from different partitions of the earthquakes in the CSZ. The largest stress rotation occurs in the cluster of earthquakes located southeast of the \change[OF]{crater}{impact structure} midpoint relative to the earthquakes in the northwest of the \change[OF]{crater}{impact structure} midpoint. Specifically, SH$_{\max}$ in the cluster of earthquakes located southeast of the \change[OF]{crater}{impact structure} midpoint shows about a 47$^\circ$ clockwise rotation whereas the cluster located to the northwest has a SH$_{\max}$ that is compatible with the regional SH$_{\max}$~\citep{Mazzotti_2010} (Fig. \ref{figone}).

\citet{Baird_2010} explain the distribution of seismicity in the CSZ as products of the interactions between the impact structure and the rift faults. Their numerical models for the rift faults and impact \change[OF]{crater}{structure} subjected to the regional stress show increased differential stresses near the fault planes, which is consistent with the distribution of the earthquakes. Stress solutions from their numerical models show greater differential stress in the northeast of the \change[OF]{crater}{impact structure}, where \change[OF]{more}{most of the larger} earthquakes occur, than in the southwest. However, their models could not fully explain the SH$_{\max}$ rotations in the CSZ relative to the regional SH$_{\max}$. Instead, they addressed the observed stress rotations based on the discrepancy between the SH$_{\max}$ from the stress solutions in the seismogenic zone and the SH$_{\max}$ inverted from the modeled slips on the rift faults.

In this study, we present a new set of numerical models that can assess the impacts \change[OF]{on}{of} stress distribution due to fault geometry, frictional strengths of faults, elastic properties of the \change[OF]{crater}{impact structure} and velocity models for the region. We then try to correlate modeled stress distributions with the recently-relocated hypocenters \citep{Powell_2017} and discuss implications for the non-uniform stress orientation around the \change[OF]{crater}{impact structure} that was previously recognized.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model Setup}
We create numerical models that include three major rift faults and the damaged impact \change[OF]{crater}{structure} (Fig. \ref{figtwo}A). For this purpose, we use PyLith version 2.1.0~\citep{Aagard2015, matthew2015, c2015}, an open-source finite element code for modeling dynamic and quasi-static tectonic deformation. PyLith is suitable for the intended models because it can compute elastic responses of a model involving multiple faults and material heterogeneities subjected to various types of loading.

\subsection{Model geometry}
Our models are composed of three units, crust, \change[OF]{crater}{impact structure} and rift faults, reflecting a simplification of the geology of the region (Fig. \ref{figtwo}A). The crust is a 220 $\times$ 220 $\times$ 40 km box with the \change[OF]{crater}{impact structure} cut out. The impact \change[OF]{crater}{structure} is modeled as a spherical cap with a surface diameter of 60 km and a depth of 15 km.

The three rift faults have a strike of N35$^\circ$E and are embedded in the crust layer except for the top surface edge that is exposed on the surface. The three faults correspond to the Gouffre \add[OF]{NW} River, St. Laurent, and the Charlevoix faults (Fig. \ref{figone}). \citet{Baird_2010} modeled the Gouffre River, St. Laurent, and the South Shore faults. They did not model the Charlevoix fault. The locations of the rift faults relative to the \change[OF]{crater}{impact structure} are based on geologic maps by \citet{lamontagne1999} and \citet{Rondot_1971}. We create two sets of models with different dip angles of the faults based on two proposed geometries of the rift faults. One set has a uniform dip of 70$^\circ$SE for all three faults \citep{anglin1984,Baird_2010} while the other has 65$^\circ$, 40$^\circ$ and 40$^\circ$ for the three planar faults, from north to south, respectively \citep{Powell_2017}.

We conducted resolution tests in which the change in displacement and stress solutions relative to a 1 km-resolution model are monitored as a function of element size \add[OF]{(Fig. S1)}. Displacement was almost constant for 2 km or smaller element sizes. \add[OF]{We use an element size of 4 km for more computational expensive models due to its consistent displacement, but slightly higher stress solutions relative to the 2 km-resolution model.} We also observe edge effects by comparing a 420 $\times$ 420 $\times$ 40 km model with the original 220 $\times$ 220 $\times$ 40 km model, finding that the seismogenic parts around the \change[OF]{crater}{impact structure} show consistent displacement and stress solutions for both domain sizes. Based on this result, we choose the smaller domain for this study and set the element size to be about 2 km. \add[OF]{We use an average computation time of about 16 days for fault models ($\mu$ = 0.3) with 2 km element size using 16 cores on the University of Memphis High Performance Computing cluster, except for the 65$^\circ$-40$^\circ$-40$^\circ$ fault dip model, which took about twice longer to run for the same model time. We do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper. However, we use an element size of 4 km for models with friction coefficient ($\mu$) values of 0.1 and 0.2 due to their expensive computation time.}

\subsection{Initial and boundary conditions}
\label{Initial_and_boundary_conditions}
Initial stresses are assumed to be lithostatic but due to the non-planar geometry of the \change[OF]{crater}{impact structure}, computing initial lithostatic equilibrium stresses is not trivial. We first compute lithostatic stresses based on the density distribution from an adopted velocity model for the CSZ (Table~\ref{tableone}) and use it as an initial stress distribution. We then use this stress solution as the true initial stress conditions. We verify that this two-step approach leads to an initial stress field perfectly balancing the gravitational body force by observing that the initial vertical displacements are uniformly zero.

Velocities are prescribed on the sides perpendicular to the $x$-axis (Fig. \ref{figtwo}A) while the $y$-perpendicular sides and the bottom boundary are free-slip and the top boundary is traction-free. Rather than applying velocities oblique to the sides, we rotate the model domain such that the $x$-axis is oriented to N55$^\circ$E, the regional SH$_{\max}$ direction~\citep{Zoback_1992} (Fig. \ref{figtwo}B). We apply a 1 m/yr compressive velocity in the x-axis direction. The magnitude of boundary velocity does not represent any tectonic loading in the continental interiors but has the sole purpose of increasing the differential stress ($\sigma_D$ = $\sigma_1 - \sigma_3$). Noting that \change[OF]{most earthquakes in the crater occur near 10 km depth}{the distribution of earthquakes within the impact structure has a peak at 10 km} \citep{Baird_2010,Powell_2017}, we increase the boundary displacement until $\sigma_D$ reaches 706 MPa at 10 km depth based on Byerlee's law, $\tau$  = 50 MPa + 0.6$\,\sigma_n$~\citep{Byerlee_1978}. $\sigma_3$ corresponds to the lithostatic stress. Lithostatic (compressive) stress is negative. \add[OF]{We assume the absence of pore-fluid pressure along the rift faults (Fig. S2).}

\begin{figure}[ht]
\centering
\includegraphics[width=25pc]{Figures/model_geometry.png}
\caption{(A) Model domain with the \change[OF]{crater}{impact structure} (gray) and crust (red). The three rift faults (black lines), dimensions, boundary conditions and the total amount of displacement are annotated. The outer 10 km-thick layer of crust (green) is added to contain fault edges within the domain, a requirement by PyLith. (B) The orientation of the model domain (red dotted box) and the associated coordinate axes (red arrows) relative to the geographic reference frame. The red dotted box is not the actual model domain but just a box that shows its "orientation." Cyan circles on the geographic map show the inner and outer \change[OF]{crater}{impact structure} boundaries and black solid lines trace rift faults (see Fig. \ref{figone}).}
\label{figtwo}
\end{figure}

\subsection{Elastic moduli from velocity models}
We assume linear elasticity for both crust and \change[OF]{crater}{impact structure}. To obtain elastic moduli and density distributions, we consider three regional velocity models and one recent model based on local earthquake tomography~\citep{Powell_2017}. The regional models are for the Saguenay region in Quebec~\citep{Somerville1990}, the 1D standardized halfspace velocity model of eastern Canada~\citep{lamontagne1999}, and the 1D velocity model derived from \change[OF]{seismic refraction studies}{a simultaneous inversion of hypocenters and velocities of the CSZ}~\citep{lamontagne1999} (Fig. \ref{figthree}).

\begin{figure}[ht]
\centering
\includegraphics[width=30pc]{Figures/layered_vel_models.png}
\caption{Velocity models used in this study. Red, blue and black lines are velocity models for the Saguenay region \citep{Somerville1990}, \change[OF]{a standardized velocity}{the Geological Survey of Canada (GSC) standard velocity model} of Eastern Canada \citep{lamontagne1999} and the \add[OF]{Canadian Shield (North Shore)} velocity model of CSZ \citep{lamontagne1999}.}
\label{figthree}
\end{figure}

We also consider a non-uniform distribution of density and elastic moduli inferred from the 3D $V_p$ and $V_s$ tomography model by \citet{Powell_2017}, of which $V_p$ and $V_s$ variations for the depth range from 12 to 14 km are shown in Fig. \ref{figfour}. The tomography has a block size of 2 km and velocity features with a dimension of 6 km can be resolved. Since this tomography solution does not cover the entire study area, we assume a halfspace velocity model~\citep{lamontagne1999} outside of the tomography coverage. Smooth transition between the tomography model and the half-space model is achieved by linear interpolation. Densities ($\rho$) are computed according to Gardner's principle~\citep{Gardner_1974}: $\rho=0.31 V_p^{0.25}$, where $V_p$ is the P-wave velocity in m/s and density is given as g/cm$^3$.

For simplicity, we assume that the \change[OF]{crater}{impact structure}'s bulk and shear moduli are a certain fraction of those of the crust~\citep[e.g.,][]{Baird_2010}. Similarly, the density of the \change[OF]{crater}{impact structure} is reduced by 10 \% from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a realistic damaged crustal rock. Lower values of density ratios does not significantly affect the model results (Fig. S3).}

\begin{figure}[ht]
\centering
\includegraphics[width=30pc]{Figures/TOMO_vel_models.png}
\caption{Variation of $V_p$ and $V_s$ at the depths from 12 to 14 km from the 3D seismic tomographic model by \citet{Powell_2017}.}
\label{figfour}
\end{figure}

\subsection{Treatment of rift faults}
We treat the rift faults as cohesive-frictional planes, on which slip vectors are not prescribed but determined by the model. In order to create relative motions across the rift fault planes, PyLith decouples the motion of the two sides of the faults by inserting cohesive cells on the fault surfaces. We assign a coefficient of static friction ($\mu$) and the cohesion ($C$) on the fault. We assume that $\mu$ and $C$ are uniform on the fault planes in each model but investigate the consequences of varying $\mu$ from 0.1 to 0.6 at a constant $C$ of 0 MPa. \add[OF]{We compute a series of models in which the rift faults dip at 70$^{\circ}$ but their cohesion ($C$) is varied systematically at a constant friction coefficient ($\mu$) of 0.3. We use six models with cohesion values of 0, 3, 5, 10, 20 and 30 MPa (Fig. S4). Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.} We choose a cohesion of 0 MPa based on a report that a zero cohesion is sufficient for most pre-existing faults~\citep{Marone_Chris}.

The reference model (SNFR25) has the geometry described above but without the rift faults. This is equivalent to a model with infinitely strong faults. The initial stress state is close to the initially assumed lithostatic stress after the nonplanar correction due to the \change[OF]{crater}{impact structure}. We determine the percentage change in differential stress, $\Delta\sigma_{D}^{\prime}=100\,( \sigma_{D}-\sigma_{D,ref}) / \sigma_{D,ref}$, and the change in the orientation of SH$_{max}$,  $\Delta\phi_{\max}=\phi_{\max}-\phi_{\max,ref}$, where $\phi_{\max}$ denotes the orientation of the maximum principal stress ($\sigma_1$). Since our model domain was rotated clockwise about the center of the \change[OF]{crater}{impact structure} by 35$^\circ$, $\phi_{\max}$ equal to zero should be understood as parallel to the regional stress field. Positive and negative values of $\phi_{\max}$ correspond to anticlockwise and clockwise rotation from the direction of applied loading, respectively. \add[OF]{In order to quantify the fitting between the simulated stress change and the earthquake hypocenters, we determine the percentage of hypocenters that fall within region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5 \%. We did not account for the uncertainty in hypocenter relocation and the effect of any along-strike variation in the fault dips in reality.}

\subsection{Control Parameters}
We create a series of models in which the following parameters are varied: dips of the rift faults, friction coefficients, \change[OF]{crater}{impact structure}-crust elastic moduli ratios, and the velocity models. Two fault geometries for the CSZ are considered. One model has a dip angle of 70$^\circ$SE for all three rift faults \citep{Baird_2010}. The other assumes that the three faults have dip angles of 65$^\circ$SE, 40$^\circ$SE and 40$^\circ$SE from north to south~\citep{Powell_2017}.

\change[OF]{crater}{Impact structure}-crust elastic moduli ratios tested are 0.25, 0.5 and 1.0. When the modulus ratio is 1.0, the \change[OF]{crater}{impact structure} has the same velocity model as the crust. The friction coefficient, $\mu$, is varied from 0.1 to 0.6 at a constant cohesion of 0 MPa in one set of models. We assume that $\mu$ and $C$ are the same for the three rift faults and it is uniform on the fault planes, including the part of the faults within the \change[OF]{crater}{impact structure} region.

Three velocity models are considered in this study: The 1D Saguenay velocity model~\citep{Somerville1990}, the 1D CSZ velocity model~\citep{lamontagne1999} and the 3D V$_p$ and V$_s$ tomography model~\citep{Powell_2017} (Figs. \ref{figthree} and \ref{figfour}). When the tomography model is used, the \change[OF]{crater}{impact structure}-crust moduli ratio becomes irrelevant. All the models presented in this paper are listed in Table~\ref{tableone}.

\begin{table}
\caption{List of numerical models}
\centering
\begin{tabular}{llcccccc}
\hline
Model & Velocity Model & Dip of Rift Faults & Moduli ratio & $\mu$ & $C$ & K$^{*}$ (MPa) & G$^{*}$ (MPa) \\
\hline
SNFR25  & Saguenay Region$^{1}$ & No faults & 0.25 & 0.3 & 0 & 55.7 & 32.7  \\
SD70R25  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7 \\
SD70R25V  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1-0.6 & 0 & 55.7 & 32.7 \\
%SD70R25M1 &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1 & 0 \\
SD65R25  &  & $65^\circ-40^\circ-40^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7\\
SD70R50  &  & $70^\circ-70^\circ-70^\circ$  & 0.5 & 0.3 & 0 & 55.7 & 32.7 \\
SD70R100   &  & $70^\circ-70^\circ-70^\circ$  & 1.0 & 0.3 & 0 & 55.7 & 32.7 \\
LD70R25 & 1-D Model$^{2}$ & $70^\circ-70^\circ-70^\circ$ & 0.25 & 0.3  & 0 & 60.0 & 35.7 \\
TD70 & Tomography$^{3}$ & $70^\circ-70^\circ-70^\circ$ & - & 0.3 & 0 & 58.7 & 35.3 \\
\hline
\multicolumn{8}{1}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}. $^{*}$K, G at 10 km depth.}
\end{tabular}
\label{tableone}
\end{table}

% ###################################################################################################################

\section{Results}

\subsection{Reference Model (SNFR25)} \label{Ref_Model}
The effects of the weaker \change[OF]{crater}{impact structure} are dominant in SNFR25. $\sigma_D$ is smaller by 100s MPa in the \change[OF]{crater}{impact structure} region relative to the surrounding crustal rock as shown by 5 and 10-km depth sections (Fig. \ref{fig:SNFR25_ref}A). The absolute value of $\sigma_D$ is greater (i.e. is more negative) in the direction perpendicular to the applied loading than in the parallel direction. At depths below the \change[OF]{crater}{impact structure} (i.e., depths $\ge$ 15 km), $\sigma_D$ is more negative at the central region by about 300 MPa relative to the average $\sigma_D$ at those depths (Fig. \ref{fig:SNFR25_ref}A). The higher negative value of $\sigma_D$ at 15 km depth decreases to the average value at that depth within 20 km from the center of the model geometry. The effect of the \change[OF]{crater}{impact structure} weakens at 20 km and eventually becomes insignificant at 25 km (Fig. \ref{fig:SNFR25_ref}A).

$\phi_{\max}$, the orientation of SH$_{\max}$, shows a four-lobe pattern of alternating polarities around the \change[OF]{crater}{impact structure} (Fig. \ref{fig:SNFR25_ref}B). $\phi_{\max}$ uniformly approaches 0$^\circ$, the loading direction, away from the \change[OF]{crater}{impact structure} and also with depth (Fig. \ref{fig:SNFR25_ref}B). In the SE corner of the \change[OF]{crater}{impact structure}, $\phi_{\max}$ shows a maximum clockwise (i.e., negative) rotation of about 18.3$^\circ$ from the regional stress direction (5 km panel in Fig. \ref{fig:SNFR25_ref}B). 
$\phi_{\max}$ at 5 km and 10 km depths is close to 0$^\circ$ within the \change[OF]{crater}{impact structure}, being subparallel to the regional stress orientation ~\citep{Zoback_1992}.

\begin{figure}[ht]
\centering
\includegraphics[width=30pc]{Figures/SNFR25.png}
\caption{(A) Differential stress ($\sigma_D$) and (B) SH$_{\max}$ orientation ($\phi_{\max}$) in the reference model (SNFR25) at different depths. The value of lithostatic stress at each depth is at the lower right corner of each depth slice in \ref{fig:SNFR25_ref}A. The arrows in \ref{fig:SNFR25_ref}B represent the loading direction for all models. Note the change in scale in \ref{fig:SNFR25_ref}A for depths greater than 10 km. Each figure is 70 $\times$ 70 km.} 
\label{fig:SNFR25_ref}
\end{figure}

% #############################################################
\subsection{Effects of rift faults and their dip}
\subsubsection{SD70R25}
Magnitudes of $\sigma_{D}$ in SD70R25 are smaller in the \change[OF]{crater}{impact structure} than in the surrounding crust, as in the reference model, but also significantly modified by abrupt changes in the vicinity of the rift faults (Fig. \ref{fig:SD70R25}A). $\sigma_{D}$ at a distance greater than 50 km from the center of the \change[OF]{crater}{impact structure} is similar to that of the reference model at each depth.

\begin{figure}[ht]
\centering
%\includegraphics[width=25pc]{Figures/SD70R25.png}
\includegraphics[width=25pc]{Figures/SD70R25_2.png}
\caption{(A) Differential stress ($\sigma_D$), (B) SH$_{\max}$ orientation ($\phi_{\max}$), (C) Percentage change in differential stress  ($\Delta\sigma_{D}^{\prime}$) and (D) the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) in SD70R25 model relative to SNFR25 at various depths. Note the change in scale in \ref{fig:SD70R25}A for depths greater than 10 km. Earthquakes within 2 km of each depth slice are represented by black dots in \ref{fig:SD70R25}C. \add[OF]{The outline of the impact structure is represented as black circle.} Each figure is 70 $\times$ 70 km.} 
\label{fig:SD70R25}
\end{figure}

$\phi_{\max}$ shows a four-lobe pattern of alternating polarities around the weaker \change[OF]{crater}{impact structure} but modifications made by the faults are also clearly visible. $\phi_{\max}$ in the surrounding crust approaches 0$^\circ$ as distance from the \change[OF]{crater}{impact structure}'s center or depth increases (Fig. \ref{fig:SD70R25}B). $\phi_{\max}$ within the \change[OF]{crater}{impact structure} is about $-5^{\circ}$ at a depth of 5 km but is subparallel to the regional stress orientation at 10 km depth (Fig. \ref{fig:SD70R25}B). The main effect of the rift faults is a 5$^{\circ}$ to 15$^{\circ}$ $\phi_{\max}$ clockwise rotation that persists along the faults at 5 and 10 km depths. The sense of near-fault $\phi_{\max}$ rotations flips to anticlockwise at 10 km within the \change[OF]{crater}{impact structure} and at depths below the \change[OF]{crater}{impact structure} in the surrounding crust. The anticlockwise rotation also persists along the faults and has a magnitude of about 5$^{\circ}$.

The distribution of positive $\Delta\sigma_{D}^{\prime}$ values, corresponding to increased differential stresses in SD70R25 relative to SNFR25, spatially overlaps with the seismicity in general and particularly well at 10 km (Fig. \ref{fig:SD70R25}C). \add[OF]{About 70\% of the hypocenters fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} We superimpose the relocated hypocenters of earthquakes of \citet{Powell_2017} that occurred within 2 km of each depth slice. The hypocenters are rotated clockwise by 35$^{\circ}$ about the center of the \change[OF]{crater}{impact structure} in order for them to be consistent with the rotated model geometry. Some earthquakes fall in the region of negative $\Delta\sigma_{D}^{\prime}$ near the SW and NE boundary of the \change[OF]{crater}{impact structure} at depths shallower than 15 km.

The $\Delta\phi_{\max}$ maps in Fig. \ref{fig:SD70R25}D show that the rift faults rotate SH$_{\max}$ of SNFR25 further clockwise at 5 and 10 km depths by up to 19$^{\circ}$. The effect of clockwise rotation due to the faults is diminished within the \change[OF]{crater}{impact structure} and flips the sense of rotation to anticlockwise at 10 km (Fig. \ref{fig:SD70R25}D). At depths below the \change[OF]{crater}{impact structure}, the overall impact of the faults decrease everywhere.

Three vertical cross sections of $\Delta\sigma_{D}^{\prime}$ from the SD70R25 model are shown in Fig.~\ref{fig:profiles_70_70_70_2km}. As marked on the 10-km depth slice of $\Delta\sigma_{D}^{\prime}$ (left panel in Fig.~\ref{fig:profiles_70_70_70_2km}), they are all perpendicular to the fault strike. Two cross sections, 1 and 2, go through the central and marginal areas of the \change[OF]{crater}{impact structure} but the cross section 3 does not intersect the \change[OF]{crater}{impact structure}. Also plotted on these cross sections are the hypocenters of the region's earthquakes within 2 km from each cross section. Most of the earthquakes fall within regions of increased differential stress but some are associated with negative or negligible changes in differential stress. In the cross sections going through the \change[OF]{crater}{impact structure}, the broad region between the northernmost and the southernmost fault shows positive $\Delta\sigma_{D}^{\prime}$. In contrast, the relocated hypocenters exhibit well-defined linear trends as observed by~\citet{Powell_2017}.

\begin{figure}[ht]
\centering
\includegraphics[width=25pc]{Figures/SD70R25_profiles.png}
\caption{NW-SE cross sections through the percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$) solution in the SD70R25 model. Earthquakes within 2 km of each cross section are represented by black dots. The three NW-SE cross sections are indicated on the 10-km depth slice showing earthquakes within 2 km of the depth slice. The outline of the \change[OF]{crater}{impact structure} is represented as black circle and curved lines on the depth slice and cross sections, respectively. The depth slice is 70 $\times$ 70 km centered on the impact \change[OF]{crater}{structure}. Note the cross sections have the same color and length scales as the depth slice in~\ref{fig:profiles_70_70_70_2km}A.}
\label{fig:profiles_70_70_70_2km}
\end{figure}

% #############################################################

\subsubsection{SD65R25}
Correlation between the $\Delta\sigma_{D}^{\prime}$ distribution in SD65R25 and the observed seismicity is not as clear as in SD70R25 but shows more fine-scale correlation with the observed seismicity, especially at 10 km depth (Fig. \ref{fig:eff_of_dips}). At 15 km depth, the region of positive $\Delta\sigma_{D}^{\prime}$ correlates with the earthquakes on the northernmost fault but the earthquakes on the middle rift fault fall in regions with negative $\Delta\sigma_{D}^{\prime}$.

\begin{figure}[ht]
\centering
%\includegraphics[width=30pc]{Figures/SD65R25.png}
\includegraphics[width=30pc]{Figures/SD65R25_2.png}
\caption{Percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max})$ and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) at 10 and 15 km depths from the SD65R25 model. Earthquakes within 2 km of each depth slice are represented by black dots in \ref{fig:eff_of_dips}A. \add[OF]{The outline of the impact structure is represented as black circle.} Each figure is 70 $\times$ 70 km.}
\label{fig:eff_of_dips}
\end{figure}

Greater clockwise rotations of SH$_{\max}$ are found in SD65R25 than in SD70R25 at all depths (Fig. \ref{fig:eff_of_dips}) although both models show the four-lobe pattern and magnitudes of $\phi_{\max}$ decreasing with depth. Within the \change[OF]{crater}{impact structure}, SD65R25 shows clockwise rotations of about 5$^\circ$ at 10 km depth and the counterclockwise rotation observed for model SD70R25 is seen only north of the northernmost fault because the other two faults barely cross the \change[OF]{crater}{impact structure} region at this depth due to their shallower dip (Fig. \ref{fig:eff_of_dips}). In the surrounding crust close to the rift faults, $\phi_{\max}$ rotates clockwise by 5$^\circ$ to 16.3$^\circ$ relative to the regional stress direction (Fig. \ref{fig:eff_of_dips}). Counterclockwise rotation of $\phi_{\max}$ relative to the regional SH$_{\max}$ extends to the northeast and southwest of the \change[OF]{crater}{impact structure} in the fault-bounded region.

When compared to SH$_{\max}$ orientations in the reference model, SD65R25 shows greater clockwise rotations of $\phi_{\max}$ by up to 20$^\circ$ near the rift faults and the northeastern boundary of the \change[OF]{crater}{impact structure} at 10 km depth (Fig. \ref{fig:eff_of_dips}). These values of $\Delta \phi_{\max}$ are greater than those of SD70R25 and thus can be attributed to the shallower dips of the faults in SD65R25.

The region of increased differential stress in SD65R25 exhibits well-defined linear trends near the rift faults, and thus gives a better explanation for the narrow and well-defined seismicity near the \change[OF]{crater}{impact structure} \add[OF]{, even though the overall percentage of the hypocenters that fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% is about 25\%.} (Fig. \ref{fig:profiles_65_40_40_2km}). The SD65R25 model shows a region of negative $\Delta\sigma_{D}^{\prime}$ between the observed seismicity on the northernmost and southernmost faults. The earthquakes on the middle rift fault and most of the earthquakes on the southernmost fault outside the \change[OF]{crater}{impact structure} fall in regions with negative $\Delta\sigma_{D}^{\prime}$ (Fig. \ref{fig:profiles_65_40_40_2km}).

\begin{figure}[ht]
\centering
\includegraphics[width=25pc]{Figures/SD65R25_profiles.png}
\caption{Same as Fig. \ref{fig:profiles_70_70_70_2km} but for SD65R25 model.}
\label{fig:profiles_65_40_40_2km}
\end{figure}

\subsection{Effects of the weakness of the damaged \change[OF]{crater}{impact structure} zone}
Two models with the rift faults dipping at 70$^{\circ}$ are constructed such that the ratio of elastic moduli of the \change[OF]{crater}{impact structure} to that of the surrounding crust are 0.5 (SD70R50) and 1.0 (SD70R100), respectively.

\subsubsection{SD70R50}
While the effects of the \change[OF]{crater}{impact structure} and rift faults are still clear and consistent, SD70R50 values of $\Delta \sigma_{D}^{\prime}$ are mostly negative with some exceptions at 10 km depth amounting to about a 10 \% increased stress (Fig. \ref{fig:eff_of_moduli_ratio}A). The region of positive $\Delta\sigma_{D}^{\prime}$ in the SD70R50 model overlaps with the hypocenters only in the southeast corner of the \change[OF]{crater}{impact structure} boundary and the southernmost rift fault (i.e., the Charlevoix fault) at 5 km depth \add[OF]{, amounting to about 45\% of the hypocenters in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} (Fig. \ref{fig:eff_of_moduli_ratio}A). The spatial correlation of seismicity with increased $\sigma_{D}$ relative to the reference model is stronger at 10 km depth.

\begin{figure}[ht]
\centering
%\includegraphics[width=30pc]{Figures/SD70R50_100.png}
\includegraphics[width=30pc]{Figures/SD70R50_100_2.png}
\caption{Same as Fig.~\ref{fig:eff_of_dips} but for the models with different \change[OF]{crater}{impact structure}-crust elastic moduli ratios: (A) SD70R50 and (B) SD70R100.}
\label{fig:eff_of_moduli_ratio}
\end{figure}

$\phi_{\max}$ plots show the four-lobe pattern of alternating polarities and shows the effects of the rift faults. The maximum value of $\phi_{\max}$ is about 13$^\circ$ (Fig. \ref{fig:eff_of_moduli_ratio}A). The $\Delta\phi_{\max}$ maps in Fig. \ref{fig:eff_of_moduli_ratio}A show that the rift faults rotates the $\phi_{\max}$ in the reference model at 5 and 10 km depths up to 16.5$^{\circ}$. The value of $\Delta\phi_{\max}$ decreases to almost zero at 15 km depth, and is anticlockwise up to $-3^{\circ}$ at 20 and 25 km depths.

% #############################################################
\subsubsection{SD70R100}
$\Delta\sigma_{D}^{\prime}$ and $\phi_{\max}$ only exhibit the effects of the rift faults since the \change[OF]{crater}{impact structure} and the crust have the same elastic moduli in model SD70R100 (Fig. \ref{fig:eff_of_moduli_ratio}B).

Positive $\Delta\sigma_{D}^{\prime}$ values in SD70R100 are seen only at a depth of 10 km and their distribution does not fit the observed seismicity (Fig. \ref{fig:eff_of_moduli_ratio}B).  \add[OF]{About 23\% of the hypocenters fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} $\Delta\sigma_{D}^{\prime}$ correlates with observed seismicity below 15 km except for some earthquakes in the northern cluster. However, the model predicts earthquakes throughout the entire length of the rift faults at and below 15 km depth. Figures that shows all the depth slices are in the supplementary materials (Fig. S5). \add[OF]{The result of a model with an intermediate moduli ratio of 0.75 is somewhat between the SD70R50 and SD70R100 models (Fig. S6).}

The distribution of $\phi_{\max}$ values lacks the four-lobe pattern and is negative in the vicinity of the rift faults at 5 and 10 km depth: i.e., $\phi_{\max}$ values are rotated clockwise relative to the regional SH$_{\max}$ (Fig. \ref{fig:eff_of_moduli_ratio}B). The values of $\phi_{\max}$ range from 2$^\circ$ (25 km depth) to 12.8$^\circ$ (5 km depth). $\phi_{\max}$ decreases to 0$^{\circ}$ at about 50 km from the center of the model along the direction perpendicular to the fault strike.

The maximum value of $\Delta\phi_{\max}$ is 12.8$^\circ$ and, being indistinguishable from $\phi_{\max}$, signifies that the  $\Delta\phi_{\max}$ values in SD70R100 are controlled by the rift faults (Fig. \ref{fig:eff_of_moduli_ratio}B). The value of $\Delta\phi_{\max}$ decreases to almost zero at 15 km depth, and becomes anticlockwise in the fault region at 20 and 25 km.

\subsection{Effects of fault strength (SD70R25V)}
We compute $\sigma_{D}$ and $\phi_{\max}$ in a series of models in which the rift faults dip at 70$^{\circ}$ but their friction coefficient ($\mu$) is varied systematically at a constant cohesion of 0 MPa. We assume that the fault parameters are the same for each rift fault and uniform throughout the fault surfaces. $\mu$ varies from 0.1 to 0.6 with an interval of 0.1. We use a mesh resolution of 4 km for SD70R25V models due to the expensive computation time at $\mu$ values of 0.1 and 0.2. Aside from the change in the friction coefficient and the mesh resolution, the six models computed are the same as SD70R25. $\Delta \sigma_{D}^{\prime}$ and $\phi_{\max}$ computed for these models are plotted in Fig. \ref{fig:eff_of_mu}, which shows 10 km depth sections because of the high number of earthquakes within 2 km from that depth.

Magnitudes of $\Delta\sigma_{D}^{\prime}$ decrease as $\mu$ increases (Fig. \ref{fig:eff_of_mu}A) because the model behaviors must approach those of the no-fault model as fault strength increases. When $\mu$ values are 0.1 and 0.2, the area of positive $\Delta\sigma_{D}^{\prime}$ regions does not cover the entire observed seismicity\add[OF]{, with about 3\% and 24\% of the hypocenters in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, respectively}. The regions of positive $\Delta\sigma_{D}^{\prime}$ for $\mu$ values equal to 0.3 and 0.4 show better spatial correspondence with the seismicity of the CSZ. However, the model with $\mu = 0.4$ predicts positive Coulomb stress changes along the entire length of the rift faults, which is contrary to the limited spatial extent of the observed seismicity. \add[OF]{Also, about 66\% of the hypocenters in the model with $\mu$ of 0.3 fall within region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, compare to a value of 35\% when $\mu$ is 0.4. However, when we consider region with $\Delta\sigma_{D}^{\prime} \ge$ 0\%, the percentage increases to 82\% when $\mu$ of 0.4 compare to 73\% in the model with $\mu$ of 0.3.} $\Delta\sigma_{D}^{\prime}$ approaches zero when $\mu$ values are 0.5 and 0.6, for which the faults are locked. \add[OF]{The percentage of hypocenters in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% reduces to 1.4\% and 0\% when $\mu$ values are 0.5 and 0.6, respectively.}

\begin{figure}[ht]
\centering
%\includegraphics[width=30pc]{Figures/SD70R25V.png}
\includegraphics[width=30pc]{Figures/SD70R25V_2.png}
\caption{Effect of friction coefficient on the $\Delta\sigma_{D}^{\prime}$ and $\phi_{\max}$ in the SD70R25V model at 10 km depth. Note the change in scale for $\mu$ greater than 0.3. Earthquakes within 2 km of each depth slice are represented by black dots in \ref{fig:eff_of_mu}A. \add[OF]{The outline of the impact structure is represented as black circle.} Each figure is 70 $\times$ 70 km.} 
\label{fig:eff_of_mu}
\end{figure}

$\phi_{\max}$ maps show a clockwise stress rotation in the entire seismic zone, including the \change[OF]{crater}{impact structure} region, when $\mu$ values are 0.1 and 0.2 (Fig. \ref{fig:eff_of_mu}B). When $\mu$ is 0.3, $\phi_{\max}$ is subparallel to the regional stress orientation within the \change[OF]{crater}{impact structure} region and the four-lobe pattern appears. For $\mu \ge$ 0.4, the distribution of $\phi_{\max}$ approaches that of the reference model.

% #########################################################################################################

\subsection{Effects of velocity models}
LD70R25 and TD70 are the same as SD70R25 except that they use different velocity models. We use the 1D velocity model \citep{lamontagne1999} (Fig.~\ref{figthree}) and the 3D tomography results \citep{Powell_2017} (Fig.~\ref{figfour}) in LD70R25 and TD70 models, respectively. The $V_p$ and $V_s$ tomography model covers and extends beyond the \change[OF]{crater}{impact structure} region, so the \change[OF]{crater}{impact structure}-crust elastic moduli ratio is irrelevant because it is dictated by the velocities.

\subsubsection{LD70R25}
Despite the difference in the 1D velocity models of \citet{lamontagne1999} and \citet{Somerville1990} especially at depths shallower than 20 km (Fig. \ref{figthree}), the results of LD70R25 are similar in spatial distribution and in magnitude to those of SD70R25 (Fig. \ref{fig:eff_of_vel}A). Regions of positive $\Delta\sigma_{D}^{\prime}$ spatially overlap with the observed seismicity at all depths and especially well at 10 km depth (Fig. \ref{fig:eff_of_vel}A).

\begin{figure}[ht]
\centering
%\includegraphics[width=20pc]{Figures/LD70R25_TD70.png}
\includegraphics[width=20pc]{Figures/LD70R25_TD70_2.png}
\caption{Same as Fig.~\ref{fig:eff_of_dips} but only at a depth of 10 km for (A) LD70R25 and (B) TD70.}
\label{fig:eff_of_vel}
\end{figure}

The $\phi_{\max}$ maps also show the four-lobe pattern around the weaker \change[OF]{crater}{impact structure} and modification of the $\phi_{\max}$ by the rift faults is observed (Fig. \ref{fig:eff_of_vel}A). The maximum value of $\phi_{\max}$ is 21.7$^\circ$ and decreases to 12.4$^\circ$ at 10 km depth. The $\Delta\phi_{\max}$ map shows that the rotation of the reference model $\phi_{\max}$ due to the rift faults is up to 10.8$^\circ$ at 10 km depth (Fig. \ref{fig:eff_of_vel}A).

% #############################################################
\subsubsection{TD70}
TD70 shows very different results from those of the models with a layered velocity model and a weak \change[OF]{crater}{impact structure}. As the tomography model does not clearly show low velocities within the \change[OF]{crater}{impact structure} region, $\Delta\sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta\phi_{\max}$ are all very similar to those in SD70R100, in which the \change[OF]{crater}{impact structure} is not distinguished from the surrounding crust in terms of elastic stiffness.

The spatial correlation between $\Delta\sigma_{D}^{\prime}$ and the observed seismicity is poor, especially at 10 km depths (Fig. \ref{fig:eff_of_vel}B). Below 15 km depths, the earthquakes fall within a region of positive $\Delta\sigma_{D}^{\prime}$ but the modeled distribution of $\Delta\sigma_{D}^{\prime}$ predicts earthquakes throughout the entire length of the rift faults.

The $\phi_{\max}$ maps do not show the characteristic four-lobe pattern as seen in the models with the \change[OF]{crater}{impact structure} due to the lack of a significant decrease in the velocity model within the \change[OF]{crater}{impact structure} versus outside the \change[OF]{crater}{impact structure} (Fig. \ref{fig:eff_of_vel}B). The $\phi_{\max}$ maps show a clockwise rotation relative to the regional stress orientation up to 12.4$^\circ$ at 10 km depth (Fig. \ref{fig:eff_of_vel}B).

The $\Delta\phi_{\max}$ is similar in magnitude and in spatial distribution with the $\phi_{\max}$ maps (Fig. \ref{fig:eff_of_vel}B). This similarity in magnitude shows that the stress rotations in TD70 model are due to the presence of the rift faults.

% #############################################################
\section{Discussions}

\subsection{Earthquake distribution}
Our models suggest that having both the rift faults and the impact \change[OF]{crater}{structure} is not only sufficient but also necessary for explaining the distribution of earthquakes in the CSZ. The models without a weaker \change[OF]{crater}{impact structure} zone, SD70R100 and TD70, show regions of positive $\Delta \sigma_{D}^{\prime}$, a proxy for earthquake generation potential, along the entire length of the rift faults (e.g., Fig. \ref{fig:eff_of_moduli_ratio}B). In contrast, when the \change[OF]{crater}{impact structure} is set to be \change[OF]{less elastically stiff}{elastically softer} than the surrounding crust, positive $\Delta \sigma_{D}^{\prime}$ regions spatially coincide with the observed seismicity in the CSZ, especially above 15 km depth (e.g., Fig. \ref{fig:SD70R25}C). Our models predict that earthquake activity should extend to about 20 km \add[OF]{distance} from the \change[OF]{crater}{impact structure} in a northeast direction (Fig. \ref{fig:SD70R25}C). This distribution of positive $\Delta \sigma_{D}^{\prime}$ is not seen in the reference model without the rift faults. These two findings from our models are consistent with the conclusion drawn by~\citet{Thomas_Powell_2017} that the seismicity in CSZ requires both the damaged \change[OF]{crater}{impact structure} zone and the rift faults.

The SD70R25 and SD65R25 models can explain the seismicity of the CSZ at least partially (Figs.~\ref{fig:profiles_70_70_70_2km} and~\ref{fig:profiles_65_40_40_2km}). Correlation between the $\Delta\sigma_{D}^{\prime}$ distribution in SD65R25 and the observed seismicity shows a better and fine-scale correlation than in SD70R25, especially well near and within the \change[OF]{crater}{impact structure} region (Fig. \ref{fig:profiles_65_40_40_2km}) while those in SD70R25 fit the observed seismicity better in the northeast region outside the \change[OF]{crater}{impact structure} (Fig. \ref{fig:profiles_70_70_70_2km}). These differential correlations with seismicity of positive $\Delta \sigma_{D}^{\prime}$ regions in SD70R25 and SD65R25 might be suggesting along-strike variations in the dip angles of the rift faults \add[OF]{$~\citep[e.g.,][]{Baird_2010}$}. The SD65R25 model explains the observed seismic gap between the NW and SE clusters (i.e., between Gouffre Northwest and the Saint-Laurent faults, Fig. \ref{figone}) and can also explain the rimming of earthquakes around the \change[OF]{crater}{impact structure} as noted by~\citet{Powell_2017} especially at 10 km depth (Fig.~\ref{fig:profiles_65_40_40_2km}).

Our present models, however, cannot explain the differences in earthquake activity between the \change[OF]{crater}{impact structure} and the surrounding crust in the CSZ. `b' values of the Gutenberg-Richter relationship for the regions within and outside the \change[OF]{crater}{impact structure} are 0.93 and 0.74, respectively~\citep{Yu_2016}, indicating a higher frequency of small magnitude earthquakes within the \change[OF]{crater}{impact structure}. Also, \change[OF]{the large-magnitude}{most M4+} earthquakes in the CSZ \change[OF]{occurred}{appear to occur} in the northeast region outside the \change[OF]{crater}{impact structure}~\citep[e.g.,][]{lamontagne1999,Powell_2017,Baird_2010}. \add[OF]{Reexamination of historical earthquakes in the Charlevoix area by $\citet{Stevens1980}$ shows that some M4+ earthquakes of the period 1924-1978 also occurred at the SE end of the impact structure.} Our models do not show significantly higher values of $\Delta\sigma_{D}^\prime$ in the seismogenic zone outside the \change[OF]{crater}{impact structure} relative to the regions within the impact \change[OF]{crater}{structure} (Fig. \ref{fig:SD70R25}C). A possible explanation is that faults created in the highly fractured \change[OF]{crater}{impact structure} region~\citep{RONDOT_2000} might have lower friction coefficients than the faults outside the \change[OF]{crater}{impact structure}. Stress build-up on those weaker \change[OF]{crater}{impact structure} faults can be quicker and smaller in magnitude than on faults outside the \change[OF]{crater}{impact structure} under the same tectonic loading, resulting in more numerous, smaller magnitude earthquakes within versus outside the \change[OF]{crater}{impact structure}.

\subsection{Spatial variations of SH$_{\max}$ orientation}
Stress orientations in the CSZ from focal mechanism stress inversions \citep{Zoback_1992,Mazzotti_2010} show relative clockwise rotations within the CSZ and in the CSZ relative to the regional stress orientation. A clockwise rotation of about 47$^\circ$ is observed in the SE relative to NW clusters of earthquakes and about 32$^\circ$ from the stress inversion of the entire CSZ earthquakes relative to the SH$_{\max}$ determined from borehole breakouts~\citep{Zoback_1992,Mazzotti_2010} (Fig. \ref{figone}).

Most of the earthquakes in the NW cluster are within the \change[OF]{crater}{impact structure} region and occur at about 10 km depth (Fig. \ref{figone}). Our model shows that the rift faults tend to rotate the stress orientation clockwise in the upper 15 km depth but the amount of rotation is reduced within the weak \change[OF]{crater}{impact structure} (e.g., Fig. \ref{fig:SD70R25}D). However, the model with a \change[OF]{crater}{impact structure}-crust moduli ratio of 1.0 shows significant clockwise rotations uniformly along the entire length of the rift faults (Fig. \ref{fig:eff_of_moduli_ratio}B). This observation suggests that the impact \change[OF]{crater}{structure} tends to align the $\phi_{\max}$ to the regional tectonic loading direction within the \change[OF]{crater}{impact structure}, particularly at 10 km depth (Fig. \ref{fig:SD70R25}D).

In a model with a \change[OF]{crater}{impact structure} and the rift faults (SD70R25), the stress rotation in the CSZ is clockwise (maximum value of 20.3$^\circ$) and decreases to 0$^\circ$ at an average of 20 km away from the CSZ (Fig. \ref{fig:SD70R25}B). SD70R25 can explain about 60$\%$ of the 32$^\circ$ clockwise stress rotation observed in the CSZ relative to the borehole breakouts, and about 43$\%$ of the 47$^\circ$ rotation in the SE part of the CSZ relative to the NW part. The magnitudes of $\phi_{\max}$ in the SD65R25 model are higher than the SD70R25 model by 6$^\circ$, but show a small clockwise rotation within the \change[OF]{crater}{impact structure} at 10 km depth, and thus can explain about 80$\%$ of the 32$^\circ$ clockwise stress rotation observed in the CSZ relative to the borehole breakouts, and about 55$\%$ of the 47$^\circ$ rotation in the SE part of the CSZ relative to the NW part. The increase in $\phi_{\max}$ in the SD65R25 relative to the SD70R25 models suggests that the remaining observed stress rotations, not explained by \change[OF]{both models}{either model}, could be partly due to change in dip angle of the rift faults with depth.

A clockwise stress rotation of about 44$^\circ$ relative to the stress orientation from borehole breakouts is also observed in the Lower St Lawrence seismic zone \citep{Mazzotti_2010}. The Lower St. Lawrence seismic zone is located along the St. Lawrence River to the NE of the CSZ, and does not contain an impact \change[OF]{crater}{structure}, similar to the SD70R100 model. The rotation suggests that the presence of the rift faults and the relative angles of their strikes with respect to the regional orientation of SH$_{\max}$ alone can result in stress rotations ~\citep[e.g.,][]{Zoback_1992}. However, the combined effect of the impact \change[OF]{crater}{structure} with up to a quarter of the elastic moduli of the surrounding crust, and the rift faults are required in the CSZ to explain the observed clockwise rotations of the $\phi_{\max}$ in the SE cluster of earthquakes relative to the NW cluster, as well as in the entire CSZ relative to the direction of regional tectonic loading.

\subsection{Frictional strengths of the rift faults}
The surface expression of the rift faults used in this study correspond to the Gouffre Northwest Fault, Saint-Laurent fault and Charlevoix Fault (Fig. 1). We did not consider the South Shore fault given its aseismic nature and \change[OF]{its location at the extreme eastern edge of the crater}{it appears to mark a boundary to the active zone}~\citep{lamontagne1999}. Our models show that a $\mu$ of 0.3 and cohesion values of 0 MPa create $\Delta\sigma_{D}^\prime$ maps that spatially correlate with the seismicity of CSZ and the observed stress rotations (Fig. \ref{fig:eff_of_mu}). \add[OF]{A $\mu$ of 0.4 could also be suitable for the rift faults as the $\Delta\sigma_{D}^\prime$ maps also spatially correlate with the seismicity of CSZ, and some earthquakes also occurred at the SW region outside the impact structure (Fig. $\ref{figone}$). However, previous works in the CSZ agreed with a finite extent of the seismic zone $~\citep[e.g.,][]{Stevens1980}$}. \change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig. \ref{figone}).

The fault parameters in our study are not compatible with the analysis of \citet{Hurd_Zoback_2012,Hurd_Zoback2012b} who suggest normal values of $\mu$ (0.6 $-$ 0.8) for the rift faults and hydrostatic pore pressure. Also, \citet{Fereidoni2014} use Coulomb stress theory to investigate stress change in the CSZ caused by the 1663 earthquake (moment magnitude M of 7) and conclude that the rift faults are strong with $\mu$ of 0.8. \citet{Fereidoni2014} showed that decreasing the apparent coefficient of friction reduces the spatial correlation of the regions with enhanced stress and observed seismicity. Specifically, $\mu$ values of 0.2 and 0.4 give 66$\%$ and 75$\%$ spatial correlation, respectively. However, in our model, the regions of positive $\Delta\sigma_{D}^\prime$ significantly decrease in spatial extent when $\mu$ is 0.6, and do not fit the observed seismicity in the CSZ (Fig. \ref{fig:eff_of_mu}).

\remove[OF]{In contrast to the normal faults as suggested by $\citet{Hurd_Zoback_2012,Hurd_Zoback2012b}$ and $\citet{Fereidoni2014}$, $\citet{Baird_2010}$ conclude that the rift faults in the CSZ are very weak with a friction angle of 5$^\circ$ that is equivalent to a $\mu$ of about 0.1. This very low value of $\mu$ was necessary for their stopping criterion for boundary loading, which was $\sigma_{D}$ equal to 200 MPa at 10 km depth.}In our study, we stop increasing boundary displacements when $\sigma_{D}$ reaches 706 MPa at 10 km depth as described earlier without making any assumptions for the intermediate principal stress ($\sigma_2$). \add[OF]{In contrast, $\citet{Baird_2010}$ used a $\sigma_{D}$ equal to 200 MPa at 10 km depth as their stopping criterion for boundary loading. They suggested that the rift faults in the CSZ are very weak with %a friction angle of 5$^\circ$ that is equivalent to 
a $\mu$ of about 0.1. The higher stopping criterion in our study is based on Byerlee's law under the assumption of no pore-fluid pressure on the rift faults, and it is necessary to make faults slip at seismogenic depth. Inclusion of pore-fluid pressure can significantly reduce the magnitude of $\sigma_{D}$ used as the stopping criterion.} The stopping criteria of a $\sigma_{D}$ of 200 MPa at 10 km depth would not make rifts faults with $\mu \ge 0.3$ slip \add[OF]{at seismogenic depth unless high pore fluid pressures are present. Other possible consequences of pore-fluid pressure is that faults could be reactivated at smaller angles from the maximum compressive stress$~\citep[e.g.,][]{ChenChen18}$.}

%This very low value of $\mu$ was necessary for faults to slip under the stopping criterion for boundary loading, which was $\sigma_{D}$ equal to 200 MPa at 10 km depth. \add[OF]{
%, which will act to reduce the effective normal stress on the rift faults 
%Pore-fluid pressure is related to the lithostatic stress ($\rho g z$) by a pore-fluid factor ($\lambda$)~\citep[e.g.,][]{HubbertRubey1959, ZobackTownend2001}. $\lambda$ values are different for different pore-pressure states: e.g., for a hydrostatic state where pore spaces are interconnected up to the water table, $\labmda$ is between 0.3 and 0.4; for a suprahydrostatic state, $0.4 < \lambda \le 1.0$; and for the lithostatic state, $\lambda = 1.0$~\citep[e.g.,][]{Sibson2000,SibsonRowland,PetriniPodladchikov}. It has been suggested that seismic faulting in intraplate seismic zones generally occurs under hydrostatic fluid pressure conditions~$\citep{TownendZoback2000,SibsonRowland}$, except in areas of strong fluid release where $\lambda$ can be up to 1.0~$\citep{ManningIngebritsen99}$.% by up to a factor of two the value of the pore-fluid pressure~\citep[e.g.,][]{ZobackTownend2001}

\subsection{Velocity model of the CSZ}
Our models show that a 1D velocity model of the CSZ \citep{lamontagne1999} (Fig. \ref{figthree}) with embedded \change[OF]{crater}{impact structure} and rift faults can explain the observed seismicity and more than 50$\%$ of the stress rotations (Fig. \ref{fig:eff_of_vel}A). Using the velocity model of the \change[OF]{Sanguenay}{Saguenay} region does not improve this result (Fig. \ref{fig:SD70R25}). Similarly, $\Delta\sigma_{D}^\prime$ in the TD70 model did not spatially fit the recorded earthquakes in the upper 10 km in the CSZ because the distinct and lower-strength damaged zone is not apparent in the 3D tomography \citep{Powell_2017} (Fig. \ref{fig:eff_of_vel}B). \citet{lamontagne1999} \change[OF]{Further investigation is needed to determine why the supposedly better velocity models fail}{is a 1-D velocity model for the Canadian Shield region that does not include lateral variations of} velocity model to explain the seismicity and stress orientations.

\subsection{Limitations of our study}
Our models could not explain some earthquakes in the SW part of the \change[OF]{crater}{impact structure} especially in the upper 10 km depth (Fig. \ref{fig:SD70R25}C). We did not account for stress changes due to a large historic earthquake in the CSZ and the postglacial rebound as modeled by \citet{Fereidoni2014} and \citet{Mazzotti_GPS2005}, respectively.

Our models can only explain about 50\% of the observed $SH_{\max}$ rotation. A possible hypothesis for the remaining stress rotation is a change in the dip of the rift faults with depth and the effect of postglacial rebound. \remove[OF]{The high stress rotation could also be due to unconstrained focal mechanisms used in the stress inversion.} Most of the focal mechanisms used for stress inversion \add[OF]{in the CSZ} are obtained from first motion P and SH waves\add[OF]{$\citep{Mazzotti_2010,lamontagne1998}$}. \change[OF]{Better constrained}{The} focal mechanisms \add[OF]{are good, and we suggest that the focal mechanisms can be further constrained} using waveform modeling \remove[OF]{will be needed} to validate the magnitude of the stress rotation.

We \change[OF]{simplified}{assumed that} the rift faults to be planar however, the fault \change[OF]{trace}{traces} on the geologic map of the CSZ \change[OF]{is not straight}{are not linear} (Fig. \ref{figone}). The scatter of the seismicity within the \change[OF]{crater}{impact structure} indicates that the faults do not remain planar. Future models depicting a more realistic fault geometry may also shed light on the factors controlling stress rotation. Our model also did not incorporate pore pressure which could have affected the calculated $\mu$ \add[OF]{and maximum $\sigma_{D}$}.
The 3D velocity model is not \change[OF]{accurate}{very well defined} in the upper 5 km depth and does not cover the entire seismic zone (Fig. \ref{figfour}).

% #############################################################
\section{Conclusions}
Findings from this study can be summarized as follows:

\begin{itemize}

\item The combined effects of the impact \change[OF]{crater}{impact structure} and the rift faults are required in the CSZ to explain the observed distribution of seismicity and more than 50$\%$ of the observed clockwise rotations of the $\phi_{\max}$ in the CSZ \add[OF]{in respect to the regional maximum compressive stress direction}.

\item \change[OF]{A crater}{An impact structure} elastically weaker than the surrounding crust by up to a factor of 4 is required to explain the seismicity in the upper 10 km of the CSZ and the observed clockwise rotation of the SH$_{\max}$ in the SE relative to the NW part of the \change[OF]{crater}{impact structure}. Below 10 km depth in the \change[OF]{crater}{impact structure}, reactivation of the rift faults explains the observed seismicity in the CSZ.

\item Stress models that spatially correlate with the seismicity of CSZ and the observed stress rotations were obtained when rifts faults have a friction coefficient of 0.3 and zero cohesion \add[OF]{under an assumption of no pore-fluid pressure on the rift faults}.

\item The magnitudes of SH$_{\max}$ rotation are greater in the 65$^\circ$-40$^\circ$-40$^\circ$ fault dip case than the constant 70$^\circ$ fault dip case by 6$^\circ$. The remaining SH$_{\max}$ rotation could be due to a change in the dip of the rift faults with depth.

\item Stress models with dips of 65$^\circ$, 40$^\circ$ and 40$^\circ$ based on a recent hypocenter relocation study show a better correlation between the high differential stress regions and the observed seismicity near and within the \change[OF]{crater}{impact structure} region than those with a constant 70$^\circ$ dip. However, the constant-dip models fit the observed seismicity better in the northeast region outside the \change[OF]{crater}{impact structure}. The partial success of each model might indicate more complex geometry of the faults: e.g., an along-strike variation of the dip angles of the rift faults.

\end{itemize}

%%%%%%%%%%%%%%
% Acronyms
\begin{acronyms}
 \acro{CSZ}
  Charlevoix Seismic Zone
 \acro{SH$_{\max}$}
  Maximum horizontal principal stress 
\end{acronyms}

%%%%%%%%%%%%%%
\acknowledgments
This project is supported by the National Science Foundation (NSF - ICER) under the award title ``EarthCube Building Blocks: Collaborative Proposal: GeoTrust: Improving Sharing and Reproducibility of Geoscience Applications'' with an award number 1639706. We acknowledge the high performance computing (HPC) resource center at the University of Memphis, TN for providing the computing time for this research. \add[OF]{Earthquake hypocenters are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakescanada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).}

%%%%%%%%%%%%%%
% Citation
%% Example \citet and \citep:
%  ...as shown by \citet{Boug10}, \citet{Buiz07}, \citet{Fra10},
%  \citet{Ghel00}, and \citet{Leit74}.

%  ...as shown by \citep{Boug10}, \citep{Buiz07}, \citep{Fra10},
%  \citep{Ghel00, Leit74}.

%  ...has been shown \citep [e.g.,][]{Boug10,Buiz07,Fra10}.

\bibliography{biblio}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%

%  Numbered lines in equations:
%  To add line numbers to lines in equations,
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

%% Enter Figures and Tables near as possible to where they are first mentioned:
%
% DO NOT USE \psfrag or \subfigure commands.
%
% Figure captions go below the figure.
% Table titles go above tables;  other caption information
%  should be placed in last line of the table, using
% \multicolumn2l{$^a$ This is a table note.}
%
%----------------
% EXAMPLE FIGURE
%
% \begin{figure}[h]
% \centering
% when using pdflatex, use pdf file:
% \includegraphics[width=20pc]{figsamp.pdf}
%
% when using dvips, use .eps file:
% \includegraphics[width=20pc]{figsamp.eps}
%
% \caption{Short caption}
% \label{figone}
%  \end{figure}
%
% ---------------
% EXAMPLE TABLE
%
% \begin{table}
% \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
% \centering
% \begin{tabular}{l c}
% \hline
%  Run  & Time (min)  \\
% \hline
%   $l1$  & 260   \\
%   $l2$  & 300   \\
%   $l3$  & 340   \\
%   $h1$  & 270   \\
%   $h2$  & 250   \\
%   $h3$  & 380   \\
%   $r1$  & 370   \\
%   $r2$  & 390   \\
% \hline
% \multicolumn{2}{l}{$^{a}$Footnote text here.}
% \end{tabular}
% \end{table}

%% SIDEWAYS FIGURE and TABLE 
% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
%
% \begin{sidewaysfigure}
% \includegraphics[width=20pc]{figsamp}
% \caption{caption here}
% \label{newfig}
% \end{sidewaysfigure}
% 
%  \begin{sidewaystable}
%  \caption{Caption here}
% \label{tab:signif_gap_clos}
%  \begin{tabular}{ccc}
% one&two&three\\
% four&five&six
%  \end{tabular}
%  \end{sidewaystable}

%% If using numbered lines, please surround equations with \begin{linenomath*}...\end{linenomath*}
%\begin{linenomath*}
%\begin{equation}
%y|{f} \sim g(m, \sigma),
%\end{equation}
%\end{linenomath*}

%%% End of body of article

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% The \appendix command resets counters and redefines section heads
%
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% A: Here Is Appendix Title
%
%\appendix
%\section{Here is a sample appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary, Notation or Acronym section goes here:
%
%%%%%%%%%%%%%%  
% Glossary is only allowed in Reviews of Geophysics
%  \begin{glossary}
%  \term{Term}
%   Term Definition here
%  \term{Term}
%   Term Definition here
%  \term{Term}
%   Term Definition here
%  \end{glossary}

%
%%%%%%%%%%%%%%
% Acronyms
%\begin{acronyms}
% \acro{CSZ}
%  Charlevoix Seismic Zone
% \acro{SH$_{max}$}
%  Maximum horinzontal principal stress 
%\end{acronyms}

%
%%%%%%%%%%%%%%
% Notation 
%   \begin{notation}
%   \notation{$a+b$} Notation Definition here
%   \notation{$e=mc^2$} 
%   Equation in German-born physicist Albert Einstein's theory of special
%  relativity that showed that the increased relativistic mass ($m$) of a
%  body comes from the energy of motion of the body—that is, its kinetic
%  energy ($E$)—divided by the speed of light squared ($c^2$).
%   \end{notation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS
%
% The acknowledgments must list:
%
% •	All funding sources related to this work from all authors
%
% •	Any real or perceived financial conflicts of interests for any
%	author
%
% •	Other affiliations for any author that may be perceived as
% 	having a conflict of interest with respect to the results of this
% 	paper.
%
% •	A statement that indicates to the reader where the data
% 	supporting the conclusions can be obtained (for example, in the
% 	references, tables, supporting information, and other databases).
%
% It is also the appropriate place to thank colleagues and other contributors. 
% AGU does not normally allow dedications.

%% ------------------------------------------------------------------------ %%
%% Citations

% Please use ONLY \citet and \citep for reference citations.
% DO NOT use other cite commands (e.g., \cite, \citeyear, \nocite, \citealp, etc.).

%% Example \citet and \citep:
%  ...as shown by \citet{Boug10}, \citet{Buiz07}, \citet{Fra10},
%  \citet{Ghel00}, and \citet{Leit74}.

%  ...as shown by \citep{Boug10}, \citep{Buiz07}, \citep{Fra10},
%  \citep{Ghel00, Leit74}.

%  ...has been shown \citep [e.g.,][]{Boug10,Buiz07,Fra10}.

%%  REFERENCE LIST AND TEXT CITATIONS
%
% Either type in your references using
%
% \begin{thebibliography}{}
% \bibitem[{\textit{Kobayashi et~al.}}(2003)]{R2013} Kobayashi, T.,
% Tran, A.~H., Nishijo, H., Ono, T., and Matsumoto, G.  (2003).
% Contribution of hippocampal place cell activity to learning and
% formation of goal-directed navigation in rats. \textit{Neuroscience}
% 117, 1025--1035.
%
% \bibitem{}
% Text
% \end{thebibliography}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Or, to use BibTeX:
%
% Follow these steps
%
% 1. Type in \bibliography{<name of your .bib file>} 
%    Run LaTeX on your LaTeX file.
%
% 2. Run BiBTeX on your LaTeX file.
%
% 3. Open the new .bbl file containing the reference list and
%   copy all the contents into your LaTeX file here.
%
% 4. Run LaTeX on your new file which will produce the citations.
%
% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.

%\bibliography{bibliography/biblio}

%% After you run BibTeX, Copy in the contents of the .bbl file here:

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supporting Information
%% (Optional) See AGUSuppInfoSamp.tex/pdf for requirements 
%% for Supporting Information.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

% If you are using line numbers, remember to surround
% equations with \begin{linenomath*}...\end{linenomath*}

%  To add line numbers to lines in equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

### 2019-06-27 main_full_manuscript.tex
took citations out of trackchanges commands

@@
-o%% March 2018
+%% March 2018
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \ref{figone}).
-The impact \change[OF]{crater}{structure} has a radius of 28 km and is \change[OF]{15}{approximately 12} km deep \add[OF]{$\citep{RONDOT1994}$}.
+The impact \change[OF]{crater}{structure} has a radius of 28 km and is \change[OF]{15}{approximately 12} km deep~\citep{RONDOT1994}.
 The \change[OF]{crater}{impact structure} has a more damaged interior zone with a surface radius of 18 km (Fig.
@@
 \hline
-\multicolumn{8}{1}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}. $^{*}$K, G at 10 km depth.}
+%\multicolumn{8}{1}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}.}%$^{*}$K, G at 10 km depth.}
 \end{tabular}
@@
 \ref{fig:profiles_70_70_70_2km}).
-These differential correlations with seismicity of positive $\Delta \sigma_{D}^{\prime}$ regions in SD70R25 and SD65R25 might be suggesting along-strike variations in the dip angles of the rift faults \add[OF]{$~\citep[e.g.,][]{Baird_2010}$}.
+These differential correlations with seismicity of positive $\Delta \sigma_{D}^{\prime}$ regions in SD70R25 and SD65R25 might be suggesting along-strike variations in the dip angles of the rift faults~\citep[e.g.,][]{Baird_2010}.
 The SD65R25 model explains the observed seismic gap between the NW and SE clusters (i.e., between Gouffre Northwest and the Saint-Laurent faults, Fig.
@@
 Also, \change[OF]{the large-magnitude}{most M4+} earthquakes in the CSZ \change[OF]{occurred}{appear to occur} in the northeast region outside the \change[OF]{crater}{impact structure}~\citep[e.g.,][]{lamontagne1999,Powell_2017,Baird_2010}.
-\add[OF]{Reexamination of historical earthquakes in the Charlevoix area by $\citet{Stevens1980}$ shows that some M4+ earthquakes of the period 1924-1978 also occurred at the SE end of the impact structure.} Our models do not show significantly higher values of $\Delta\sigma_{D}^\prime$ in the seismogenic zone outside the \change[OF]{crater}{impact structure} relative to the regions within the impact \change[OF]{crater}{structure} (Fig.
+\add[OF]{Reexamination of historical earthquakes in the Charlevoix area by}~\citet{Stevens1980} \add[OF]{shows that some M4+ earthquakes of the period 1924-1978 also occurred at the SE end of the impact structure.} Our models do not show significantly higher values of $\Delta\sigma_{D}^\prime$ in the seismogenic zone outside the \change[OF]{crater}{impact structure} relative to the regions within the impact \change[OF]{crater}{structure} (Fig.
 \ref{fig:SD70R25}C).
@@
 $\ref{figone}$).
-However, previous works in the CSZ agreed with a finite extent of the seismic zone $~\citep[e.g.,][]{Stevens1980}$}.
+However, previous works in the CSZ agreed with a finite extent of the seismic zone} ~\citep[e.g.,][]{Stevens1980}.
 \change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig.
@@
 
-\remove[OF]{In contrast to the normal faults as suggested by $\citet{Hurd_Zoback_2012,Hurd_Zoback2012b}$ and $\citet{Fereidoni2014}$, $\citet{Baird_2010}$ conclude that the rift faults in the CSZ are very weak with a friction angle of 5$^\circ$ that is equivalent to a $\mu$ of about 0.1.
-This very low value of $\mu$ was necessary for their stopping criterion for boundary loading, which was $\sigma_{D}$ equal to 200 MPa at 10 km depth.}In our study, we stop increasing boundary displacements when $\sigma_{D}$ reaches 706 MPa at 10 km depth as described earlier without making any assumptions for the intermediate principal stress ($\sigma_2$).
-\add[OF]{In contrast, $\citet{Baird_2010}$ used a $\sigma_{D}$ equal to 200 MPa at 10 km depth as their stopping criterion for boundary loading.
+\remove[OF]{In contrast to the normal faults as suggested by} \citet{Hurd_Zoback_2012,Hurd_Zoback2012b,Fereidoni2014}, \citet{Baird_2010} \remove[OF]{conclude that the rift faults in the CSZ are very weak with a friction angle of 5$^\circ$ that is equivalent to a $\mu$ of about 0.1.
+This very low value of $\mu$ was necessary for their stopping criterion for boundary loading, which was $\sigma_{D}$ equal to 200 MPa at 10 km depth.} In our study, we stop increasing boundary displacements when $\sigma_{D}$ reaches 706 MPa at 10 km depth as described earlier without making any assumptions for the intermediate principal stress ($\sigma_2$).
+\add[OF]{In contrast,} \citet{Baird_2010} \add[OF]{used a $\sigma_{D}$ equal to 200 MPa at 10 km depth as their stopping criterion for boundary loading.
 They suggested that the rift faults in the CSZ are very weak with %a friction angle of 5$^\circ$ that is equivalent to
@@
 Inclusion of pore-fluid pressure can significantly reduce the magnitude of $\sigma_{D}$ used as the stopping criterion.} The stopping criteria of a $\sigma_{D}$ of 200 MPa at 10 km depth would not make rifts faults with $\mu \ge 0.3$ slip \add[OF]{at seismogenic depth unless high pore fluid pressures are present.
-Other possible consequences of pore-fluid pressure is that faults could be reactivated at smaller angles from the maximum compressive stress$~\citep[e.g.,][]{ChenChen18}$.}
+Other possible consequences of pore-fluid pressure is that faults could be reactivated at smaller angles from the maximum compressive stress}~\citep[e.g.,][]{ChenChen18}.
 
@@
 A possible hypothesis for the remaining stress rotation is a change in the dip of the rift faults with depth and the effect of postglacial rebound.
-\remove[OF]{The high stress rotation could also be due to unconstrained focal mechanisms used in the stress inversion.} Most of the focal mechanisms used for stress inversion \add[OF]{in the CSZ} are obtained from first motion P and SH waves\add[OF]{$\citep{Mazzotti_2010,lamontagne1998}$}.
+\remove[OF]{The high stress rotation could also be due to unconstrained focal mechanisms used in the stress inversion.} Most of the focal mechanisms used for stress inversion \add[OF]{in the CSZ} are obtained from first motion P and SH waves~\citep{Mazzotti_2010,lamontagne1998}.
 \change[OF]{Better constrained}{The} focal mechanisms \add[OF]{are good, and we suggest that the focal mechanisms can be further constrained} using waveform modeling \remove[OF]{will be needed} to validate the magnitude of the stress rotation.

### 2019-06-27 Rebuttal_Letter.tex
Addressng comments in the rebuttal letter

@@
   PyLith, the modeling software used in this study, internally converts P and S wave velocities and density to bulk and shear moduli.
-\add[EC]{For readers' reference, however, we now list representative values of elastic moduli in Table 1.}\note[EC]{Seun, please take care of this.}
+For readers' reference, however, we now list representative values of elastic moduli in Table 1.
+  %\add[EC]{For readers' reference, however, we now list representative values of elastic moduli in Table 1.}\note[EC]{Seun, please take care of this.}
 \end{response}
@@
 No significant changes in the model results were found in these models.
-The 10\% reduction in the density of corresponding crustal rock is to model a \annote[EC]{realistic}{Without further justification or proper citation of supporting evidence, you cannot say this.
-Support it or remove it.} damaged crustal rock \annote[EC]{(Lines 174-175).}{The main text should be accordingly revised.
+The 10\% reduction in the density of corresponding crustal rock is to model a  damaged crustal rock (Lines 174-175).
+  %\annote[EC]{realistic}{Without further justification or proper citation of supporting evidence, you cannot say this. Support it or remove it.} 
+  %{The main text should be accordingly revised.
 The point should be that, in all the presented models, the impact structure has elastic moduli reduced by 10 \% relative to the surrounding crust but the model results were insensitive to other amounts of reduction as see in Fig.
@@
 
-    The faults in our models extend to 40 km but \annote[EC]{slips on them occur only down to about 10 km due to our stopping criterion.}{Correct this if I'm wrong.} Since the non-slipping portion of the faults are irrelevant, the condition of low normal stress is already being satisfied.
+    The faults in our models extend to 40 km but slips on them occur only down to about 10 km due to our stopping criterion. 
+    %{Correct this if I'm wrong.} 
+    Since the non-slipping portion of the faults are irrelevant, the condition of low normal stress is already being satisfied.
 For reference, however, we have explored non-zero values of cohesion and their impact on the results are shown in Fig.
@@
 I meant quantitative.}
-   of the correlation between the change in differential stress and the observed seismicity \add[OF]{by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\%} without accounting for uncertainty in hypocenter relocation (Line 199-202).
+   of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 199-202).
 We added a discussion on the choice of the friction coefficient in Lines 506-509.
@@
 
-  \annote[EC]{We have justified}{You cannot simply say like this. Do describe what is the justification here as well.} the mesh size in Section 2.1 (Lines 118-121).
+ % \annote[EC]{We have justified}{You cannot simply say like this. Do describe what is the justification here as well.} the mesh size in Section 2.1 
+  We use a mesh size of 4 km to determine the effect of friction coefficient due to the expensive computation time of models with $\mu$ values of 0.1 and 0.2 (Lines 118-121).
 \end{response}

### 2019-06-27 main_full_manuscript.tex
Addressng comments in the rebuttal letter

--- 2019-06-27 main_full_manuscript.tex
@@
 We do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper.
-However, we use an element size of 4 km for models with friction coefficient ($\mu$) values of 0.1 and 0.2 due to their expensive computation time.}
+However, we use a mesh size of 4 km to determine the effect of friction coefficient due to the expensive computation time of the models with $\mu$ values of 0.1 and 0.2.}
+%we use an element size of 4 km for models with friction coefficient ($\mu$) values of 0.1 and 0.2 due to their expensive computation time.
 
@@
 For simplicity, we assume that the \change[OF]{crater}{impact structure}'s bulk and shear moduli are a certain fraction of those of the crust~\citep[e.g.,][]{Baird_2010}.
-Similarly, the density of the \change[OF]{crater}{impact structure} is reduced by 10 \% from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a realistic damaged crustal rock.
-Lower values of density ratios does not significantly affect the model results (Fig.
-S3).}
+Similarly, the density of the \change[OF]{crater}{impact structure} is reduced by 10 \% from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a damaged crustal rock but the model results were insensitive to other amounts of reduction as seen in Fig.
+S3 in the supplementary information.}
 

### 2019-06-27 main_full_manuscript.tex
Update main_full_manuscript.tex

@@
 For simplicity, we assume that the \change[OF]{crater}{impact structure}'s bulk and shear moduli are a certain fraction of those of the crust~\citep[e.g.,][]{Baird_2010}.
-Similarly, the density of the \change[OF]{crater}{impact structure} is reduced by 10 \% from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a damaged crustal rock but the model results were insensitive to other amounts of reduction as seen in Fig.
+Similarly, the density of the \change[OF]{crater}{impact structure} is reduced by 10 \% from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a damaged crustal rock, but the model results were insensitive to other amounts of reduction as seen in Fig.
 S3 in the supplementary information.}

### 2019-06-27 main_full_manuscript.tex
saving minor changes

--- 2019-06-27 main_full_manuscript.tex
@@
 The impact \change[OF]{crater}{structure} is superimposed on three major rift faults trending N35$^\circ$E and dipping to the southeast~\citep{anglin1984,Rondot_1971}.
-The CSZ \change[OF]{is considered to pose a high risk of seismic hazard}{has a high seismic hazards} due to its history of generating \change[OF]{large}{moderate to large} earthquakes \citep{anglin1984,lamontagne1999}.
+The CSZ \change[OF]{is considered to pose a high risk of seismic hazard}{has high risk of seismic hazards} due to its history of generating \change[OF]{large}{moderate to large} earthquakes \citep{anglin1984,lamontagne1999}.
 Over 200 earthquakes are recorded each year in the CSZ (Nuttli magnitude, mN \add[OF]{mostly} $\leq$ 3) \citep{Baird_2010} and the hypocenters have a bimodal distribution with peaks at 10 and 22 km depths \citep{Vlahovic_2003}.
@@
 \caption{Topography\add[OF]{, bathymetry,} and seismicity of the Charlevoix Seismic Zone (CSZ) as well as the locations of the impact \change[OF]{crater}{structure} (outer cyan circle) and the more damaged inner \change[OF]{crater}{impact structure} (inner cyan circle).
-Small circles \add[OF]{and diamonds} are the relocated epicenters \citep{Powell_2017} \add[OF]{and the complete dataset for the years 1988-2011, respectively,} and their colors represent the focal depths.
+Small circles \add[OF]{and diamonds} are the relocated epicenters~\citep{Powell_2017} \add[OF]{and the complete dataset for the years 1988-2011, respectively,} and their colors represent the focal depths.
 The focal mechanisms are for the earthquakes used by \citet{Mazzotti_2010} for the stress inversion.
@@
 We do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper.
-However, we use a mesh size of 4 km to determine the effect of friction coefficient due to the expensive computation time of the models with $\mu$ values of 0.1 and 0.2.}
-%we use an element size of 4 km for models with friction coefficient ($\mu$) values of 0.1 and 0.2 due to their expensive computation time.
+However, we use an element size of 4 km for models with friction coefficient ($\mu$) values of 0.1 and 0.2 due to their expensive computation time.}
 
@@
 For simplicity, we assume that the \change[OF]{crater}{impact structure}'s bulk and shear moduli are a certain fraction of those of the crust~\citep[e.g.,][]{Baird_2010}.
-Similarly, the density of the \change[OF]{crater}{impact structure} is reduced by 10 \% from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a damaged crustal rock but the model results were insensitive to other amounts of reduction as seen in Fig.
-S3 in the supplementary information.}
+Similarly, the density of the \change[OF]{crater}{impact structure} is reduced by 10 \% from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a realistic damaged crustal rock.
+Lower values of density ratios does not significantly affect the model results (Fig.
+S3).}
 

### 2019-06-27 Rebuttal_Letter.tex

@@
 Never confess; only justify.} on the high differential stress at seismogenic depth in our study, due to}
-  The differential stress of 706 MPa at 10 km depth is based on Byerlee's law under the assumption of  \add[EC]{$\mu$ equal to XX and} the absence of pore-fluid pressure.
+  The differential stress of 706 MPa at 10 km depth is based on Byerlee's law under the assumption of  
+  %$\mu$ equal to 0.6 and \add[OF]{The equation of Byerlee's law has a μ value of 0.6. It is not an assumption in our study.}
+  %\add[EC]{$\mu$ equal to 0.6 and} 
+  the absence of pore-fluid pressure.
 The full derivation of this value is now provided in the supplementary information.
@@
 
-  \annote[EC]{Some earthquakes occurred at the SW region outside the impact structure, as shown in the updated Fig.
+  The distribution of historical earthquakes in the Charlevoix area by Stevens (1980) shows that earthquakes are not distributed along the entire fault length.
+However, some earthquakes  in recent catalog are located at the SW region outside the impact structure, as shown in the updated Fig.
+1.
+
+ %\annote[EC]{Some earthquakes occurred at the SW region outside the impact structure, as shown in the updated Fig.
 1.
@@
 }
+
 \end{response}
@@
 https://geoscan.nrcan.gc.ca/starweb/geoscan/servlet.starweb?
-path=geoscan/downloade.web&search1=R=209378}
+path=geoscan/downloade.web\&search1=R=209378}
 

### 2019-06-27 main_full_manuscript.tex

--- 2019-06-27 main_full_manuscript.tex
@@
 
-Magnitudes of $\Delta\sigma_{D}^{\prime}$ decrease as $\mu$ increases (Fig.
+Magnitudes of $\Delta \sigma_{D}^{\prime}$ decrease as $\mu$ increases (Fig.
 \ref{fig:eff_of_mu}A) because the model behaviors must approach those of the no-fault model as fault strength increases.

### 2019-06-27 Supporting_Information.tex
saving progress

@@
 %
+\usepackage{rotating}
 \usepackage{graphicx}
@@
 \noindent\textbf{Resolution Test}
+\vspace{10mm}
 
@@
 
-\vspace{5mm} %5mm vertical space
-
-\begin{sidewaysfigure}
-\setfigurenum{S1}
-\includegraphics[width=25pc]{Figures/res_test_CSZ.png}
-\caption{Errors in displacement components and differential stress ($\sigma_{D}$) for models with element sizes ranging from 2 to 8 km relative to a model with 1 km element size.}
-\label{S1}
-\end{sidewaysfigure}
-
-\vspace{10mm} %5mm vertical space
-
 This resolution test shows that the error generally increases with mesh resolution (Fig.
@@
 However, due to expensive computation time, we will use an element size of 4 km to evaluate model parameters, e.g., coefficient of friction.
+%
+\begin{figure}[h!]
+\setfigurenum{S1}
+\includegraphics[width=25pc]{Figures/res_test_CSZ.png}
+\caption{Errors in displacement components and differential stress ($\sigma_{D}$) for models with element sizes ranging from 2 to 8 km relative to a model with 1 km element size.}
+\label{S1}
+\end{figure}
 
@@
 
-\begin{sidewaysfigure}
+\begin{figure}[ht]
 \setfigurenum{S2}
@@
 \label{S2}
-\end{sidewaysfigure}
+\end{figure}
 
@@
 
-From $\Delta$ABC,
+From $\Delta$ABC in Fig.~\ref{S2},
 \[
- \sin(\alpha) = \frac{\sigma_{1}-\sigma_{3}}{2}/[\frac{250}{3} + \frac{\sigma_{1}+\sigma_{3}}{2}],
+ \sin \alpha = \frac{\sigma_{1}-\sigma_{3}}{2} / \left[\frac{250}{3} + \frac{\sigma_{1}+\sigma_{3}}{2} \right],
 \]
@@
 \[
- \sin(\alpha) = \frac{3(\sigma_{1}-\sigma_{3})}{3(\sigma_{1}+\sigma_{3})+500},
+ \sin \alpha = \frac{3(\sigma_{1}-\sigma_{3})}{3(\sigma_{1}+\sigma_{3})+500},
 \]
@@
 \[
- \sigma_{1} = \frac{\sigma_{3}+[\sigma_{3}+\frac{500}{3}]\times \sin(\alpha)}{1-\sin(\alpha)},
+ \sigma_{1} = \frac{\sigma_{3}+[\sigma_{3}+\frac{500}{3}] \sin(\alpha)}{1-\sin \alpha},
 \]
 
-Based on Byerlee's law, $\tau$  = 50 MPa + 0.6$\,\sigma_n$, under the assumption of absence of pore-fluid pressure along the rift faults, $\tan(\alpha) = 0.6$, hence, $\sin(\alpha)= 0.5145$.
+Based on Byerlee's law, $\tau$  = 50 MPa + 0.6$\,\sigma_n$, under the assumption of absence of pore-fluid pressure along the rift faults, $\tan \alpha = 0.6$, hence, $\sin \alpha = 0.5145$.
 $\sigma_{3}$ corresponds to the lithostatic stress, and assuming it is equal to 250 MPa at 10 km depth, gives $\sigma_{1}$ = 956.4882 MPa.
@@
 
-\begin{sidewaysfigure}
+\begin{figure}[ht]
 \setfigurenum{S3}
@@
 \label{S3}
-\end{sidewaysfigure}
+\end{figure}
 
@@
 
-\begin{sidewaysfigure}
+\begin{figure}[ht]
 \setfigurenum{S4}
@@
 \label{S4}
-\end{sidewaysfigure}
+\end{figure}
 
@@
 
-\begin{sidewaysfigure}
+\begin{figure}[ht]
 \setfigurenum{S5}
@@
 \label{S5}
-\end{sidewaysfigure}
+\end{figure}
 
@@
 
-\begin{sidewaysfigure}
+\begin{figure}[ht]
 \setfigurenum{S6}
@@
 \label{S6}
-\end{sidewaysfigure}
+\end{figure}
 
@@
 
-%\pagebreak
+\pagebreak
 
@@
 %
-% \begin{sidewaysfigure}
+% \begin{figure}
 % \includegraphics[width=20pc]{samplefigure.eps}
@@
 % \label{label_here}
-% \end{sidewaysfigure}
+% \end{figure}
 %

### 2019-06-27 main_full_manuscript.tex
saving progress

@@
 
-We conducted resolution tests in which the change in displacement and stress solutions relative to a 1 km-resolution model are monitored as a function of element size \add[OF]{(Fig.
+We conducted resolution tests in which the change in displacement and stress solutions relative to a 1 km-resolution model are monitored as a function of element size.
+\change[OF]{Displacement was almost constant for 2 km or smaller element sizes}{Displacements and differential stresses do not change much for elements sizes equal to 4 km or smaller (Fig.
 S1)}.
-Displacement was almost constant for 2 km or smaller element sizes.
-\add[OF]{We use an element size of 4 km for more computational expensive models due to its consistent displacement, but slightly higher stress solutions relative to the 2 km-resolution model.} We also observe edge effects by comparing a 420 $\times$ 420 $\times$ 40 km model with the original 220 $\times$ 220 $\times$ 40 km model, finding that the seismogenic parts around the \change[OF]{crater}{impact structure} show consistent displacement and stress solutions for both domain sizes.
+\add[OF]{Based on the resolution tests, we use the element size of 2 km for most of the models and 4 km for more computationally expensive ones like those for exploring the effects of friction coefficient.} We also observe edge effects by comparing a 420 $\times$ 420 $\times$ 40 km model with the original 220 $\times$ 220 $\times$ 40 km model, finding that the seismogenic parts around the \change[OF]{crater}{impact structure} show consistent displacement and stress solutions for both domain sizes.
 Based on this result, we choose the smaller domain for this study and set the element size to be about 2 km.
-\add[OF]{We use an average computation time of about 16 days for fault models ($\mu$ = 0.3) with 2 km element size using 16 cores on the University of Memphis High Performance Computing cluster, except for the 65$^\circ$-40$^\circ$-40$^\circ$ fault dip model, which took about twice longer to run for the same model time.
-We do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper.
-However, we use a mesh size of 4 km to determine the effect of friction coefficient due to the expensive computation time of the models with $\mu$ values of 0.1 and 0.2.}
+\add[OF]{The average computation time was about 16 days for fault models ($\mu$ = 0.3) with 2 km element size on 16 cores on the University of Memphis High Performance Computing cluster.
+The model with fault dips, 65$^\circ$-40$^\circ$-40$^\circ$ took about twice longer to run for the same model time.
+We do not clearly understand why the model with shallower-dipping faults is slower than the others roughly by a factor of two and further analyzing computational efficiency is beyond the scope of this paper.}
 %we use an element size of 4 km for models with friction coefficient ($\mu$) values of 0.1 and 0.2 due to their expensive computation time.
@@
 The magnitude of boundary velocity does not represent any tectonic loading in the continental interiors but has the sole purpose of increasing the differential stress ($\sigma_D$ = $\sigma_1 - \sigma_3$).
-Noting that \change[OF]{most earthquakes in the crater occur near 10 km depth}{the distribution of earthquakes within the impact structure has a peak at 10 km} \citep{Baird_2010,Powell_2017}, we increase the boundary displacement until $\sigma_D$ reaches 706 MPa at 10 km depth based on Byerlee's law, $\tau$  = 50 MPa + 0.6$\,\sigma_n$~\citep{Byerlee_1978}.
-$\sigma_3$ corresponds to the lithostatic stress.
-Lithostatic (compressive) stress is negative.
-\add[OF]{We assume the absence of pore-fluid pressure along the rift faults (Fig.
-S2).}
+Noting that \change[OF]{most earthquakes in the crater occur near 10 km depth}{the distribution of earthquakes within the impact structure has a peak at 10 km} \citep{Baird_2010,Powell_2017}, we increase the boundary displacement until $\sigma_D$ reaches 706 MPa at 10 km depth based on Byerlee's law for dry rocks, $\tau$  = 50 MPa + 0.6$\,\sigma_n$~\citep{Byerlee_1978}.
+\add[OF]{Supplementary Information provides more details of the full derivation of the stopping criterion for boundary loading.
+We assume that} $\sigma_3$ corresponds to the lithostatic stress \change[OF]{.
+C}{and adopt the sign convention that ompressive stress is negative.}
 
@@
 For simplicity, we assume that the \change[OF]{crater}{impact structure}'s bulk and shear moduli are a certain fraction of those of the crust~\citep[e.g.,][]{Baird_2010}.
-Similarly, the density of the \change[OF]{crater}{impact structure} is reduced by 10 \% from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a damaged crustal rock, but the model results were insensitive to other amounts of reduction as seen in Fig.
-S3 in the supplementary information.}
+Similarly, the density of the \change[OF]{crater}{impact structure} is reduced \remove[OF]{by 10 \%} from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a damaged crustal rock.
+Models with density reduced by 0 to 20 \% were run but did not exhibit significant changes as shown in Fig.
+S3 in the supplementary information.
+Unless stated otherwise, models presented in this study has 10 \% of density reduction in the impact structure.}
 
@@
 We assume that $\mu$ and $C$ are uniform on the fault planes in each model but investigate the consequences of varying $\mu$ from 0.1 to 0.6 at a constant $C$ of 0 MPa.
-\add[OF]{We compute a series of models in which the rift faults dip at 70$^{\circ}$ but their cohesion ($C$) is varied systematically at a constant friction coefficient ($\mu$) of 0.3.
-We use six models with cohesion values of 0, 3, 5, 10, 20 and 30 MPa (Fig.
+\add[OF]{We choose zero cohesion because it is appropriate for pre-existing faults with low normal stress}~\citep{Marone_Chris} \add[OF]{and slips on the model faults occur only down to about 10 km depth satisfying this condition.} \note[EC]{I think the following sentences should be in discussion, not here.}\add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig.
 S4).
-Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.} We choose a cohesion of 0 MPa based on a report that a zero cohesion is sufficient for most pre-existing faults~\citep{Marone_Chris}.
+Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.}
 
@@
 Positive and negative values of $\phi_{\max}$ correspond to anticlockwise and clockwise rotation from the direction of applied loading, respectively.
-\add[OF]{In order to quantify the fitting between the simulated stress change and the earthquake hypocenters, we determine the percentage of hypocenters that fall within region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5 \%.
+\add[OF]{In order to quantify the spatial correlation between the simulated stress changes and the earthquake hypocenters, we determine the percentage of hypocenters that fall within region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5 \%.
 We did not account for the uncertainty in hypocenter relocation and the effect of any along-strike variation in the fault dips in reality.}
@@
 \begin{table}
-\caption{List of numerical models}
+\caption{List of numerical models \note[EC]{Each symbol needs a description. Cohesion needs a unit. I gave a try with the $\dagger$ symbol.}}
 \centering
@@
 \hline
-Model & Velocity Model & Dip of Rift Faults & Moduli ratio & $\mu$ & $C$ & K$^{*}$ (MPa) & G$^{*}$ (MPa) \\
+Model & Velocity Model & Dip of Rift Faults & Moduli ratio & $\mu^{\dagger}$ & $C^{\dagger}$ & K$^{\dagger,*}$ (MPa) & G$^{\dagger,*}$ (MPa) \\
 \hline
@@
 \hline
-%\multicolumn{8}{1}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}.}%$^{*}$K, G at 10 km depth.}
+\multicolumn{8}{l}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}.$^{*}$K, G at 10 km depth.} \\
+\multicolumn{8}{l}{$^{\dagger}$$\mu$, $C$, $K$ and $G$ are friction coefficient, cohesion, bulk and shear modulus, respectively.}
+
 \end{tabular}
@@
 
-The region of increased differential stress in SD65R25 exhibits well-defined linear trends near the rift faults, and thus gives a better explanation for the narrow and well-defined seismicity near the \change[OF]{crater}{impact structure} \add[OF]{, even though the overall percentage of the hypocenters that fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% is about 25\%.} (Fig.
+The region of increased differential stress in SD65R25 exhibits well-defined linear trends near the rift faults, and thus gives a better explanation for the narrow and well-defined seismicity near the \change[OF]{crater}{impact structure} \note[EC]{Why do you say ``even though''?
+Does the percentage betray your or a general expectation?} \add[OF]{, even though the overall percentage of the hypocenters that fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% is about 25\%.} (Fig.
 \ref{fig:profiles_65_40_40_2km}).

### 2019-06-27 main_full_manuscript.tex
Updated

--- 2019-06-27 main_full_manuscript.tex
@@
 The impact \change[OF]{crater}{structure} is superimposed on three major rift faults trending N35$^\circ$E and dipping to the southeast~\citep{anglin1984,Rondot_1971}.
-The CSZ \change[OF]{is considered to pose a high risk of seismic hazard}{has high risk of seismic hazards} due to its history of generating \change[OF]{large}{moderate to large} earthquakes \citep{anglin1984,lamontagne1999}.
+The CSZ \change[OF]{is considered to pose a high risk of seismic hazard}{has a high seismic hazards} due to its history of generating \change[OF]{large}{moderate to large} earthquakes \citep{anglin1984,lamontagne1999}.
 Over 200 earthquakes are recorded each year in the CSZ (Nuttli magnitude, mN \add[OF]{mostly} $\leq$ 3) \citep{Baird_2010} and the hypocenters have a bimodal distribution with peaks at 10 and 22 km depths \citep{Vlahovic_2003}.
@@
 \caption{Topography\add[OF]{, bathymetry,} and seismicity of the Charlevoix Seismic Zone (CSZ) as well as the locations of the impact \change[OF]{crater}{structure} (outer cyan circle) and the more damaged inner \change[OF]{crater}{impact structure} (inner cyan circle).
-Small circles \add[OF]{and diamonds} are the relocated epicenters~\citep{Powell_2017} \add[OF]{and the complete dataset for the years 1988-2011, respectively,} and their colors represent the focal depths.
+Small circles \add[OF]{and diamonds} are the relocated epicenters \citep{Powell_2017} \add[OF]{and the complete dataset for the years 1988-2011, respectively,} and their colors represent the focal depths.
 The focal mechanisms are for the earthquakes used by \citet{Mazzotti_2010} for the stress inversion.

### 2019-06-27 Rebuttal_Letter.tex
Addressed comments

@@
 \begin{response}{I recommend the authors to justify the assumption of the independency effect of involved factors on stress perturbations, or that they have consistently monotonous effects.}
-    The indepnedency effect, if we understand it correctly, is not assumed but achieved by our experiment design, in which a reference model is compared with a model with only one parameter changed.
+    The independency effect, if we understand it correctly, is not assumed but achieved by our experiment design, in which a reference model is compared with a model with only one parameter changed.
 We also believe our original results were already showing that that the controlled parameters have consistently monotonous effects.
@@
 
-  We have added the computational efficiency of our model in the model geometry section (Lines 125-130) of the manuscript.
+  We have added the computational efficiency of our model in the model geometry section (Lines 126-132) of the manuscript.
 We did not add the computational efficiency to Table 1 because it does not change significantly among the models except for the SD65R25 model, which took about twice longer to run for the same model time.
@@
 Shear stress was not considered as a stopping criterion.
-In addition, we have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 528-538).
+In addition, we have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 530-540).
 
@@
 No significant changes in the model results were found in these models.
-The 10\% reduction in the density of corresponding crustal rock is to model a  damaged crustal rock (Lines 174-175).
+The 10\% reduction in the density of corresponding crustal rock is to model a  damaged crustal rock (Lines 177-180).
   %\annote[EC]{realistic}{Without further justification or proper citation of supporting evidence, you cannot say this. Support it or remove it.} 
@@
 
-    The faults in our models extend to 40 km but slips on them occur only down to about 10 km due to our stopping criterion. 
-    %{Correct this if I'm wrong.} 
-    Since the non-slipping portion of the faults are irrelevant, the condition of low normal stress is already being satisfied.
+   % The faults in our models extend to 40 km but slips on them occur only down to about 10 km due to our stopping criterion. %{Correct this if I'm wrong.} 
+   % Since the non-slipping portion of the faults are irrelevant, the condition of low normal stress is already being satisfied.
 For reference, however, we have explored non-zero values of cohesion and their impact on the results are shown in Fig.
 S4 in the supplementary information.
+
+    We have explored non-zero values of cohesion and their impact on the results are shown in Fig.
+S4 in the supplementary information.
+However, low-cohesion results show a better spatial correlation with seismicity.
+
 \end{response}
@@
 I meant quantitative.}
-   of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 199-202).
+   of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 199-203).
 We added a discussion on the choice of the friction coefficient in Lines 506-509.
@@
  % \annote[EC]{We have justified}{You cannot simply say like this. Do describe what is the justification here as well.} the mesh size in Section 2.1 
-  We use a mesh size of 4 km to determine the effect of friction coefficient due to the expensive computation time of models with $\mu$ values of 0.1 and 0.2 (Lines 118-121).
+  We use a mesh size of 4 km to determine the effect of friction coefficient due to the expensive computation time of models with $\mu$ values of 0.1 and 0.2 (Lines 118-122).
 \end{response}
@@
 
-  We have edited the manuscript accordingly (see Lines 448-450). We have also included the findings of Steven (1980) in our discussion.
+  We have edited the manuscript accordingly (see Lines 447-449). We have also included the findings of Steven (1980) in our discussion.
 \end{response}
@@
 
- The focal mechanisms are good, and we suggest that the focal mechanisms can be further constrained using waveform modeling to validate the magnitude of the stress rotation (Lines 561-563).
+ The focal mechanisms are good, and we suggest that the focal mechanisms can be further constrained using waveform modeling to validate the magnitude of the stress rotation (Lines 563-565).
 \end{response}
@@
 The higher stopping criterion in our study is necessary to make faults slip at seismogenic depth under the assumption.
-We have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 528-538).
+We have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 530-540).
 \end{response}

### 2019-06-27 Supporting_Information.tex
Addressed comments

@@
 
-The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio.
+The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio (Fig.
+\ref{S3}).
 The maps show no significant change with density ratio.
@@
 
-\noindent\textbf{Effect of cohesion}
+\noindent\textbf{Effects of no impact structure (SD70R100 model)}
 
-We compute $\Delta \sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ in a series of models in which the rift faults dip at 70$^{\circ}$ (i.e., SD70R25) but their cohesion ($C$) is varied systematically at a constant coefficient of friction ($\mu$) of 0.3.
-We assume that the fault parameters are the same for each rift fault and uniform throughout the fault surfaces.
-Six models with 0, 3, 5, 10, 20 and 30 MPa are constructed (Fig.
+The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model (Fig.
 \ref{S4}).
-
-Magnitudes of $\Delta\sigma_D^{\prime}$ and $\phi_{\max}$ decrease with increasing cohesion.
-$\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity at all the fault cohesions, especially well when the cohesion is less than 5 MPa (Fig.
-\ref{S4}A).
-However, the models could not explain some earthquakes in the SW corner of the crater.
-The $\Delta\sigma_D^{\prime}$ is not affected by a change in cohesion between 0 and 5 MPa.
-However, $\phi_{\max}$ approaches the reference no-fault model as the cohesion increases (Fig.
-\ref{S4}B).
-As cohesion increases, $\Delta\phi_{\max}$ decreases in value and the rotation is concentrated in the fault region outside the crater (Fig.
-\ref{S4}C).
-$\Delta\phi_{\max}$ is up to 10.8$^\circ$ when the cohesion is less than 5 MPa.
-
-Figure \ref{S4} shows that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope.
-We use a cohesion value of 0 MPa to explain the spatial distribution of observed seismicity in the CSZ.
+$\Delta\sigma_{D}^{\prime}$ shows increased $\sigma_{D}$ relative to SNFR25 throughout the entire length of the rift faults at and below 15 km depth, hence the model predicts earthquakes in those regions.
 
@@
 \setfigurenum{S4}
-\includegraphics[width=25pc]{Figures/SD70R25C_S2.png}
-\caption{Same as \ref{S3} but for the models with different cohesion values.}
-\label{S4}
-\end{figure}
-
-\vspace{10mm} %5mm vertical space
-
-\noindent\textbf{Effects of no impact structure (SD70R100 model)}
-
-The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model.
-$\Delta\sigma_{D}^{\prime}$ shows increased $\sigma_{D}$ relative to SNFR25 throughout the entire length of the rift faults at and below 15 km depth, hence the model predicts earthquakes in those regions.
-
-\vspace{10mm} %5mm vertical space
-
-\begin{figure}[ht]
-\setfigurenum{S5}
 \includegraphics[width=25pc]{Figures/SD70R100_S1.png}
@@
 Each figure is 70 $\times$ 70 km.}
-\label{S5}
+\label{S4}
 \end{figure}
@@
 
-We test the response of the model results with different impact structure-crust moduli ratio.
+We test the response of the model results with different impact structure-crust moduli ratio (Fig.
+\ref{S5}).
 The model with a moduli ratio of 1.0 does not have the impact crater.
@@
 \begin{figure}[ht]
-\setfigurenum{S6}
+\setfigurenum{S5}
 \includegraphics[width=25pc]{Figures/effect_of_moduli_ratio.png}
 \caption{Same as \ref{S3} but for the models with different impact structure-crust moduli ratio.}
+\label{S5}
+\end{figure}
+
+\vspace{10mm} %5mm vertical space
+
+\noindent\textbf{Effect of cohesion}
+
+We compute $\Delta \sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ in a series of models in which the rift faults dip at 70$^{\circ}$ (i.e., SD70R25) but their cohesion ($C$) is varied systematically at a constant coefficient of friction ($\mu$) of 0.3.
+We assume that the fault parameters are the same for each rift fault and uniform throughout the fault surfaces.
+Six models with 0, 3, 5, 10, 20 and 30 MPa are constructed (Fig.
+\ref{S6}).
+
+Magnitudes of $\Delta\sigma_D^{\prime}$ and $\phi_{\max}$ decrease with increasing cohesion.
+$\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity at all the fault cohesions, especially well when the cohesion is less than 5 MPa (Fig.
+\ref{S6}A).
+However, the models could not explain some earthquakes in the SW corner of the crater.
+The $\Delta\sigma_D^{\prime}$ is not affected by a change in cohesion between 0 and 5 MPa.
+However, $\phi_{\max}$ approaches the reference no-fault model as the cohesion increases (Fig.
+\ref{S6}B).
+As cohesion increases, $\Delta\phi_{\max}$ decreases in value and the rotation is concentrated in the fault region outside the crater (Fig.
+\ref{S6}C).
+$\Delta\phi_{\max}$ is up to 10.8$^\circ$ when the cohesion is less than 5 MPa.
+
+Figure \ref{S6} shows that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope.
+We use a cohesion value of 0 MPa to explain the spatial distribution of observed seismicity in the CSZ.
+
+\vspace{10mm} %5mm vertical space
+
+\begin{figure}[ht]
+\setfigurenum{S6}
+\includegraphics[width=25pc]{Figures/SD70R25C_S2.png}
+\caption{Same as \ref{S3} but for the models with different cohesion values.}
 \label{S6}

### 2019-06-27 main_full_manuscript.tex
Addressed comments

--- 2019-06-27 main_full_manuscript.tex
@@
 We assume that} $\sigma_3$ corresponds to the lithostatic stress \change[OF]{.
-C}{and adopt the sign convention that ompressive stress is negative.}
+C}{and adopt the sign convention that compressive stress is negative.}
 
@@
 We assume that $\mu$ and $C$ are uniform on the fault planes in each model but investigate the consequences of varying $\mu$ from 0.1 to 0.6 at a constant $C$ of 0 MPa.
-\add[OF]{We choose zero cohesion because it is appropriate for pre-existing faults with low normal stress}~\citep{Marone_Chris} \add[OF]{and slips on the model faults occur only down to about 10 km depth satisfying this condition.} \note[EC]{I think the following sentences should be in discussion, not here.}\add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig.
+\add[OF]{We choose zero cohesion because it is appropriate for pre-existing faults with low normal stress}~\citep{Marone_Chris}.
+%\add[OF]{and slips on the model faults occur only down to about 10 km depth satisfying this condition.} 
+%\note[EC]{I think the following sentences should be in discussion, not here.}\add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig.
 S4).
@@
 \begin{table}
-\caption{List of numerical models \note[EC]{Each symbol needs a description. Cohesion needs a unit. I gave a try with the $\dagger$ symbol.}}
+\caption{List of numerical models} 
+%\note[EC]{Each symbol needs a description. Cohesion needs a unit. I gave a try with the $\dagger$ symbol.}}
 \centering
@@
 \hline
-Model & Velocity Model & Dip of Rift Faults & Moduli ratio & $\mu^{\dagger}$ & $C^{\dagger}$ & K$^{\dagger,*}$ (MPa) & G$^{\dagger,*}$ (MPa) \\
+Model & Velocity Model & Dip of Rift Faults & Moduli ratio & $\mu^{\dagger}$ & $C^{\dagger}$ (MPa) & K$^{\dagger,*}$ (MPa) & G$^{\dagger,*}$ (MPa) \\
 \hline
@@
 
-The region of increased differential stress in SD65R25 exhibits well-defined linear trends near the rift faults, and thus gives a better explanation for the narrow and well-defined seismicity near the \change[OF]{crater}{impact structure} \note[EC]{Why do you say ``even though''?
-Does the percentage betray your or a general expectation?} \add[OF]{, even though the overall percentage of the hypocenters that fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% is about 25\%.} (Fig.
+The region of increased differential stress in SD65R25 exhibits well-defined linear trends near the rift faults, and thus gives a better explanation for the narrow and well-defined seismicity near the \change[OF]{crater}{impact structure} (Fig.
 \ref{fig:profiles_65_40_40_2km}).
+\add[OF]{About 25\% of the hypocenters fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.}.
 The SD65R25 model shows a region of negative $\Delta\sigma_{D}^{\prime}$ between the observed seismicity on the northernmost and southernmost faults.
@@
 \ref{fig:profiles_65_40_40_2km}).
+
+%\note[EC]{Why do you say ``even though''?
+Does the percentage betray your or a general expectation?} \add[OF]{, even though the overall percentage of the hypocenters that fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% is about 25\%.}
 
@@
 Figures that shows all the depth slices are in the supplementary materials (Fig.
-S5).
+S4).
 \add[OF]{The result of a model with an intermediate moduli ratio of 0.75 is somewhat between the SD70R50 and SD70R100 models (Fig.
-S6).}
+S5).}
 
@@
 \ref{fig:eff_of_mu}).
-\add[OF]{A $\mu$ of 0.4 could also be suitable for the rift faults as the $\Delta\sigma_{D}^\prime$ maps also spatially correlate with the seismicity of CSZ, and some earthquakes also occurred at the SW region outside the impact structure (Fig.
+\add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig.
+S6).
+Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.} \add[OF]{A $\mu$ of 0.4 could also be suitable for the rift faults as the $\Delta\sigma_{D}^\prime$ maps also spatially correlate with the seismicity of CSZ, and some earthquakes also occurred at the SW region outside the impact structure (Fig.
 $\ref{figone}$).

### 2019-06-28 main_full_manuscript.tex
Some edits by Chris

@@
 The inset shows the location of the CSZ in eastern Canada.
-Earthquake \change[OF]{epicenters}{hypocenters} from the National Resources Canada catalog for the years 1988-2011.}
+Earthquake \change[OF]{epicenters}{dataset} from the National Resources Canada catalog for the years 1988-2011.}
 \label{figone}
@@
 \citet{Vlahovic_2003} conducted a three-dimensional (3D) P-wave velocity study of the CSZ.
-The tomography model shows several \change[OF]{high-velocity}{higher P velocity} bodies at mid-crustal depths.
-A significant fraction of the CSZ earthquakes occurs around these \change[OF]{high-velocity}{higher P velocity} bodies and some larger earthquakes occur along the northern edges of the high velocity bodies.
+The tomography model shows several \change[OF]{high-velocity}{higher P-wave velocity} bodies at mid-crustal depths.
+A significant fraction of the CSZ earthquakes occurs around these \change[OF]{high-velocity}{higher P-wave velocity} bodies and some larger earthquakes occur along the northern edges of the high velocity bodies.
 
@@
 We conducted resolution tests in which the change in displacement and stress solutions relative to a 1 km-resolution model are monitored as a function of element size.
-\change[OF]{Displacement was almost constant for 2 km or smaller element sizes}{Displacements and differential stresses do not change much for elements sizes equal to 4 km or smaller (Fig.
+\change[OF]{Displacement was almost constant for 2 km or smaller element sizes}{Displacements and differential stresses do not change appreciably for elements sizes equal to 4 km or smaller (Fig.
 S1)}.
-\add[OF]{Based on the resolution tests, we use the element size of 2 km for most of the models and 4 km for more computationally expensive ones like those for exploring the effects of friction coefficient.} We also observe edge effects by comparing a 420 $\times$ 420 $\times$ 40 km model with the original 220 $\times$ 220 $\times$ 40 km model, finding that the seismogenic parts around the \change[OF]{crater}{impact structure} show consistent displacement and stress solutions for both domain sizes.
+\add[OF]{Based on the resolution tests, we use the element size of 2 km for most of the models and 4 km for more computationally expensive models like those for exploring the effects of the friction coefficient.} We also observe edge effects by comparing a 420 $\times$ 420 $\times$ 40 km model with the original 220 $\times$ 220 $\times$ 40 km model, finding that the seismogenic parts around the \change[OF]{crater}{impact structure} show consistent displacement and stress solutions for both domain sizes.
 Based on this result, we choose the smaller domain for this study and set the element size to be about 2 km.
 \add[OF]{The average computation time was about 16 days for fault models ($\mu$ = 0.3) with 2 km element size on 16 cores on the University of Memphis High Performance Computing cluster.
-The model with fault dips, 65$^\circ$-40$^\circ$-40$^\circ$ took about twice longer to run for the same model time.
+The model with fault dips of 65$^\circ$-40$^\circ$-40$^\circ$ took about twice longer to run for the same model time.
 We do not clearly understand why the model with shallower-dipping faults is slower than the others roughly by a factor of two and further analyzing computational efficiency is beyond the scope of this paper.}
@@
 The magnitude of boundary velocity does not represent any tectonic loading in the continental interiors but has the sole purpose of increasing the differential stress ($\sigma_D$ = $\sigma_1 - \sigma_3$).
-Noting that \change[OF]{most earthquakes in the crater occur near 10 km depth}{the distribution of earthquakes within the impact structure has a peak at 10 km} \citep{Baird_2010,Powell_2017}, we increase the boundary displacement until $\sigma_D$ reaches 706 MPa at 10 km depth based on Byerlee's law for dry rocks, $\tau$  = 50 MPa + 0.6$\,\sigma_n$~\citep{Byerlee_1978}.
-\add[OF]{Supplementary Information provides more details of the full derivation of the stopping criterion for boundary loading.
+Noting that \change[OF]{most earthquakes in the crater occur near 10 km depth}{the depth distribution of earthquakes within the impact structure has a peak at 10 km} \citep{Baird_2010,Powell_2017}, we increase the boundary displacement until $\sigma_D$ reaches 706 MPa at 10 km depth based on Byerlee's law for dry rocks, $\tau$  = 50 MPa + 0.6$\,\sigma_n$~\citep{Byerlee_1978}.
+\add[OF]{More details of the full derivation of the stopping criterion for boundary loading is given in the supplementary information.
 We assume that} $\sigma_3$ corresponds to the lithostatic stress \change[OF]{.
@@
 S3 in the supplementary information.
-Unless stated otherwise, models presented in this study has 10 \% of density reduction in the impact structure.}
+Unless stated otherwise, models presented in this study have 10 \% of density reduction in the impact structure.}
 
@@
 Positive and negative values of $\phi_{\max}$ correspond to anticlockwise and clockwise rotation from the direction of applied loading, respectively.
-\add[OF]{In order to quantify the spatial correlation between the simulated stress changes and the earthquake hypocenters, we determine the percentage of hypocenters that fall within region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5 \%.
-We did not account for the uncertainty in hypocenter relocation and the effect of any along-strike variation in the fault dips in reality.}
+\add[OF]{In order to quantify the spatial correlation between the simulated stress changes and the earthquake hypocenters, we determine the percentage of hypocenters that fall within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5 \%.
+We did not account for the uncertainty in hypocenter relocation and the effect of any along-strike variation in the fault dips.} % in reality
 
@@
 Earthquakes within 2 km of each depth slice are represented by black dots in \ref{fig:SD70R25}C.
-\add[OF]{The outline of the impact structure is represented as black circle.} Each figure is 70 $\times$ 70 km.}
+\add[OF]{The outline of the impact structure is represented as a black circle.} Each figure is 70 $\times$ 70 km.}
 \label{fig:SD70R25}
@@
 \ref{fig:SD70R25}C).
-\add[OF]{About 70\% of the hypocenters fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} We superimpose the relocated hypocenters of earthquakes of \citet{Powell_2017} that occurred within 2 km of each depth slice.
+\add[OF]{About 70\% of the hypocenters fall in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} We superimpose the relocated hypocenters of earthquakes of \citet{Powell_2017} that occurred within 2 km of each depth slice.
 The hypocenters are rotated clockwise by 35$^{\circ}$ about the center of the \change[OF]{crater}{impact structure} in order for them to be consistent with the rotated model geometry.
@@
 Earthquakes within 2 km of each depth slice are represented by black dots in \ref{fig:eff_of_dips}A.
-\add[OF]{The outline of the impact structure is represented as black circle.} Each figure is 70 $\times$ 70 km.}
+\add[OF]{The outline of the impact structure is represented as a black circle.} Each figure is 70 $\times$ 70 km.}
 \label{fig:eff_of_dips}
@@
 \ref{fig:profiles_65_40_40_2km}).
-\add[OF]{About 25\% of the hypocenters fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.}.
+\add[OF]{About 25\% of the hypocenters fall in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.}.
 The SD65R25 model shows a region of negative $\Delta\sigma_{D}^{\prime}$ between the observed seismicity on the northernmost and southernmost faults.
@@
 \ref{fig:eff_of_moduli_ratio}A).
-The region of positive $\Delta\sigma_{D}^{\prime}$ in the SD70R50 model overlaps with the hypocenters only in the southeast corner of the \change[OF]{crater}{impact structure} boundary and the southernmost rift fault (i.e., the Charlevoix fault) at 5 km depth \add[OF]{, amounting to about 45\% of the hypocenters in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} (Fig.
+The region of positive $\Delta\sigma_{D}^{\prime}$ in the SD70R50 model overlaps with the hypocenters only in the southeast corner of the \change[OF]{crater}{impact structure} boundary and the southernmost rift fault (i.e., the Charlevoix fault) at 5 km depth \add[OF]{, amounting to about 45\% of the hypocenters in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} (Fig.
 \ref{fig:eff_of_moduli_ratio}A).
@@
 \ref{fig:eff_of_moduli_ratio}B).
-\add[OF]{About 23\% of the hypocenters fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} $\Delta\sigma_{D}^{\prime}$ correlates with observed seismicity below 15 km except for some earthquakes in the northern cluster.
+\add[OF]{About 23\% of the hypocenters fall in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} $\Delta\sigma_{D}^{\prime}$ correlates with observed seismicity below 15 km except for some earthquakes in the northern cluster.
 However, the model predicts earthquakes throughout the entire length of the rift faults at and below 15 km depth.
@@
 \ref{fig:eff_of_mu}A) because the model behaviors must approach those of the no-fault model as fault strength increases.
-When $\mu$ values are 0.1 and 0.2, the area of positive $\Delta\sigma_{D}^{\prime}$ regions does not cover the entire observed seismicity\add[OF]{, with about 3\% and 24\% of the hypocenters in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, respectively}.
+When $\mu$ values are 0.1 and 0.2, the area of positive $\Delta\sigma_{D}^{\prime}$ regions does not cover the entire observed seismicity\add[OF]{, with about 3\% and 24\% of the hypocenters in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, respectively}.
 The regions of positive $\Delta\sigma_{D}^{\prime}$ for $\mu$ values equal to 0.3 and 0.4 show better spatial correspondence with the seismicity of the CSZ.
 However, the model with $\mu = 0.4$ predicts positive Coulomb stress changes along the entire length of the rift faults, which is contrary to the limited spatial extent of the observed seismicity.
-\add[OF]{Also, about 66\% of the hypocenters in the model with $\mu$ of 0.3 fall within region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, compare to a value of 35\% when $\mu$ is 0.4.
-However, when we consider region with $\Delta\sigma_{D}^{\prime} \ge$ 0\%, the percentage increases to 82\% when $\mu$ of 0.4 compare to 73\% in the model with $\mu$ of 0.3.} $\Delta\sigma_{D}^{\prime}$ approaches zero when $\mu$ values are 0.5 and 0.6, for which the faults are locked.
-\add[OF]{The percentage of hypocenters in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% reduces to 1.4\% and 0\% when $\mu$ values are 0.5 and 0.6, respectively.}
+\add[OF]{Also, about 66\% of the hypocenters in the model with a $\mu$ of 0.3 fall within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, compared to a value of 35\% when $\mu$ is 0.4.
+However, when we consider the region with $\Delta\sigma_{D}^{\prime} \ge$ 0\%, the percentage increases to 82\% when $\mu$ is 0.4 compared to 73\% in the model with $\mu$ equal 0.3.} $\Delta\sigma_{D}^{\prime}$ approaches zero when $\mu$ values are 0.5 and 0.6, for which the faults are locked.
+\add[OF]{The percentage of hypocenters in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% reduces to 1.4\% and 0\% when $\mu$ values are 0.5 and 0.6, respectively.}
 
@@
 Earthquakes within 2 km of each depth slice are represented by black dots in \ref{fig:eff_of_mu}A.
-\add[OF]{The outline of the impact structure is represented as black circle.} Each figure is 70 $\times$ 70 km.}
+\add[OF]{The outline of the impact structure is represented as a black circle.} Each figure is 70 $\times$ 70 km.}
 \label{fig:eff_of_mu}
@@
 Also, \change[OF]{the large-magnitude}{most M4+} earthquakes in the CSZ \change[OF]{occurred}{appear to occur} in the northeast region outside the \change[OF]{crater}{impact structure}~\citep[e.g.,][]{lamontagne1999,Powell_2017,Baird_2010}.
-\add[OF]{Reexamination of historical earthquakes in the Charlevoix area by}~\citet{Stevens1980} \add[OF]{shows that some M4+ earthquakes of the period 1924-1978 also occurred at the SE end of the impact structure.} Our models do not show significantly higher values of $\Delta\sigma_{D}^\prime$ in the seismogenic zone outside the \change[OF]{crater}{impact structure} relative to the regions within the impact \change[OF]{crater}{structure} (Fig.
+\add[OF]{Reexamination of historical earthquakes in the Charlevoix area by}~\citet{Stevens1980} \add[OF]{shows that some M4+ earthquakes in the period 1924-1978 also occurred at the SE end of the impact structure.} Our models do not show significantly higher values of $\Delta\sigma_{D}^\prime$ in the seismogenic zone outside the \change[OF]{crater}{impact structure} relative to the regions within the impact \change[OF]{crater}{structure} (Fig.
 \ref{fig:SD70R25}C).
@@
 S6).
-Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.} \add[OF]{A $\mu$ of 0.4 could also be suitable for the rift faults as the $\Delta\sigma_{D}^\prime$ maps also spatially correlate with the seismicity of CSZ, and some earthquakes also occurred at the SW region outside the impact structure (Fig.
-$\ref{figone}$).
-However, previous works in the CSZ agreed with a finite extent of the seismic zone} ~\citep[e.g.,][]{Stevens1980}.
-\change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig.
-\ref{figone}).
+Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.} \add[OF]{A $\mu$ of 0.4 could also be suitable for the rift faults as the $\Delta\sigma_{D}^\prime$ maps also spatially correlate with the seismicity of the CSZ, and some earthquakes also occurred at the SW region outside the impact structure (Fig.
+$\ref{figone}$).} %However, previous works in the CSZ agreed with a finite extent of the seismic zone} ~\citep[e.g.,][]{Stevens1980}.
+\change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig. \ref{figone}).
 
@@
 
-\remove[OF]{In contrast to the normal faults as suggested by} \citet{Hurd_Zoback_2012,Hurd_Zoback2012b,Fereidoni2014}, \citet{Baird_2010} \remove[OF]{conclude that the rift faults in the CSZ are very weak with a friction angle of 5$^\circ$ that is equivalent to a $\mu$ of about 0.1.
+\remove[OF]{In contrast to the normal faults as suggested by} 
+%\citet{Hurd_Zoback_2012,Hurd_Zoback2012b,Fereidoni2014}, \citet{Baird_2010} 
+\remove[OF]{conclude that the rift faults in the CSZ are very weak with a friction angle of 5$^\circ$ that is equivalent to a $\mu$ of about 0.1.
 This very low value of $\mu$ was necessary for their stopping criterion for boundary loading, which was $\sigma_{D}$ equal to 200 MPa at 10 km depth.} In our study, we stop increasing boundary displacements when $\sigma_{D}$ reaches 706 MPa at 10 km depth as described earlier without making any assumptions for the intermediate principal stress ($\sigma_2$).
@@
 The higher stopping criterion in our study is based on Byerlee's law under the assumption of no pore-fluid pressure on the rift faults, and it is necessary to make faults slip at seismogenic depth.
-Inclusion of pore-fluid pressure can significantly reduce the magnitude of $\sigma_{D}$ used as the stopping criterion.} The stopping criteria of a $\sigma_{D}$ of 200 MPa at 10 km depth would not make rifts faults with $\mu \ge 0.3$ slip \add[OF]{at seismogenic depth unless high pore fluid pressures are present.
-Other possible consequences of pore-fluid pressure is that faults could be reactivated at smaller angles from the maximum compressive stress}~\citep[e.g.,][]{ChenChen18}.
+Inclusion of pore-fluid pressure can significantly reduce the magnitude of $\sigma_{D}$ used as the stopping criterion.} The stopping criteria of a $\sigma_{D}$ of 200 MPa at 10 km depth would not make rifts faults with $\mu \ge 0.3$ slip \add[OF]{at seismogenic depths unless high pore fluid pressures are present.
+Another possible consequences of pore-fluid pressure is that faults could be reactivated at smaller angles from the maximum compressive stress}~\citep[e.g.,][]{ChenChen18}.
 
@@
 \ref{fig:eff_of_vel}B).
-\citet{lamontagne1999} \change[OF]{Further investigation is needed to determine why the supposedly better velocity models fail}{is a 1-D velocity model for the Canadian Shield region that does not include lateral variations of} velocity model to explain the seismicity and stress orientations.
+\citet{lamontagne1999} \change[OF]{Further investigation is needed to determine why the supposedly better velocity models fail}{constructed a 1-D velocity model for the Canadian Shield region that does not include lateral variations of} velocity model to explain the seismicity and stress orientations.
 
@@
 
-\item The combined effects of the impact \change[OF]{crater}{impact structure} and the rift faults are required in the CSZ to explain the observed distribution of seismicity and more than 50$\%$ of the observed clockwise rotations of the $\phi_{\max}$ in the CSZ \add[OF]{in respect to the regional maximum compressive stress direction}.
+\item The combined effects of the impact \change[OF]{crater}{impact structure} and the rift faults are required in the CSZ to explain the observed distribution of seismicity and more than 50$\%$ of the observed clockwise rotations of the $\phi_{\max}$ in the CSZ \add[OF]{with respect to the regional maximum compressive stress direction}.
 

### 2019-06-28 main_full_manuscript.tex
Update main_full_manuscript.tex

@@
 We acknowledge the high performance computing (HPC) resource center at the University of Memphis, TN for providing the computing time for this research.
-\add[OF]{Earthquake hypocenters are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakescanada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).}
+\add[OF]{Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakescanada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).}
 

### 2019-06-28 main_full_manuscript.tex
Changed diamonds to stars in Fig. 1

--- 2019-06-28 main_full_manuscript.tex
@@
 \caption{Topography\add[OF]{, bathymetry,} and seismicity of the Charlevoix Seismic Zone (CSZ) as well as the locations of the impact \change[OF]{crater}{structure} (outer cyan circle) and the more damaged inner \change[OF]{crater}{impact structure} (inner cyan circle).
-Small circles \add[OF]{and diamonds} are the relocated epicenters~\citep{Powell_2017} \add[OF]{and the complete dataset for the years 1988-2011, respectively,} and their colors represent the focal depths.
+Small circles \add[OF]{and stars} are the relocated epicenters~\citep{Powell_2017} \add[OF]{and the complete dataset for the years 1988-2011, respectively,} and their colors represent the focal depths.
 The focal mechanisms are for the earthquakes used by \citet{Mazzotti_2010} for the stress inversion.

### 2019-06-28 Rebuttal_Letter.tex
changes saved.

@@
 
+\title{}
 %\title{Statement on the Revision of \meta{Paper \#2019JB017831} \\
@@
 \begin{response}{I recommend the authors to justify the assumption of the independency effect of involved factors on stress perturbations, or that they have consistently monotonous effects.}
-    The independency effect, if we understand it correctly, is not assumed but achieved by our experiment design, in which a reference model is compared with a model with only one parameter changed.
-We also believe our original results were already showing that that the controlled parameters have consistently monotonous effects.
+    If the term, ``the independency effect of involved factors'', means the effects of independently controlled parameters on model results.
+the independency is never assumed and only a logical outcome from our experiment design, in which a reference model is compared with a model with only one parameter changed.
+
+As for the monotonicity of model responses to varied parameters, our original results are already showing that that the controlled parameters have consistently monotonous effects.
 However, in this revision, we have run more models so that all the explored parameters have more regular intervals and thus the monotonicity of model responses can be exposed more clearly.
@@
     We have addressed this concern by running new models, making parameter intervals more regular.
-The combined set of models not only clearly exhibit the sensitivity but also show that it is a monotonous one.
-We have justified that the choice of model parameters such as $\mu$, moduli ratio, and have included additional figures in the supplementary information (Figs.
-S3, S4 and S6)
-    %\annote[EC]{(Figs. S1-S4 and S6)}{Not all are relevant to this comment. Refer to only those directly relevant.}.
+The expanded set of models not only provide the sensitivity information but also confirm that the model responses are monotonous to the control parameters in the considered ranges of values.
+Furthermore, the revised manuscript includes an updated justification for the choice of model parameters such as friction coefficient and elastic moduli ratio.\note[EC]{Seun, specify where in the revised manuscript to look at for this information.} as well as  in the supplementary information (Figs.
+S3, S4 and \note[EC]{Why S5 is not listed?}S6)
 \end{response}
@@
 We did not add the computational efficiency to Table 1 because it does not change significantly among the models except for the SD65R25 model, which took about twice longer to run for the same model time.
-We do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper.
+We do not clearly understand why this model is particularly slow but further analyzing computational efficiency is beyond the scope of this paper.
 
@@
 
-  We ran extra models to have a series of models from 0 to 20 \% reduction.
+  The revised manuscript now includes a justification that the 10\% reduction of the density in the impact structure represents damage made to crustal rocks by the impact (Lines 177-180).
+Since it is not known quantitatively how much the impact affected the crustal density and elastic moduli, we ran extra models to explore the effects of density reduction from 0 to 20 \%.
 No significant changes in the model results were found in these models.
-The 10\% reduction in the density of corresponding crustal rock is to model a  damaged crustal rock (Lines 177-180).
-  %\annote[EC]{realistic}{Without further justification or proper citation of supporting evidence, you cannot say this. Support it or remove it.} 
-  %{The main text should be accordingly revised.
-The point should be that, in all the presented models, the impact structure has elastic moduli reduced by 10 \% relative to the surrounding crust but the model results were insensitive to other amounts of reduction as see in Fig.
-S3 in the supplementary information.}
+These new results are now included in the supplementary information and Fig.
+S3 therein.
 \end{response}
@@
 S4 in the supplementary information.
-However, low-cohesion results show a better spatial correlation with seismicity.
+However, since low-cohesion results show a better spatial correlation with seismicity, the revised manuscript still presents models with zero cohesion as the main results.
 
@@
 
-   We have added a quantitative assessment
-   %\annote[EC]{qualitative assessment}{Why is it still only qualitative?
-Have you tried one of the ideas I suggested?
-If none worked, you are supposed to let me know and look at another solution.
-Unless you have a good reason to ignore the reviewer's suggestion, the editor and the reviewer would be very curious why you didn't follow the suggestion.
-This is indeed the main reason why I asked if you had run into any trouble while revising the manuscript.
-Please take care of this and let me know if you need hlep.} \add[OF]{I am sorry it was a typo.
-I meant quantitative.}
-   of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 199-203).
-We added a discussion on the choice of the friction coefficient in Lines 506-509.
+   We have added a quantitative assessment of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 199-203).
+This metric is now used for describing the model results and comparing different models throughout the revised manuscript.
+We also added a discussion on the choice of the friction coefficient in Lines 506-509.
     %: 1) the change in differential stress maps changes with fault geometry, and we have established an along-strike variation in the fault dips in this study; and 2) the 3D velocity model is very well defined in the upper 5 km depth which may introduced an uncertainty in the hypocenter relocation.
@@
 
- % \annote[EC]{We have justified}{You cannot simply say like this. Do describe what is the justification here as well.} the mesh size in Section 2.1 
-  We use a mesh size of 4 km to determine the effect of friction coefficient due to the expensive computation time of models with $\mu$ values of 0.1 and 0.2 (Lines 118-122).
+We decided to run this particular group of models to acquire necessary information without increasing computational cost too much.
+Low-friction models, especially those with $\mu$ equal to 0.1 and 0.2, take \annote[EC]{up to XX weeks}{Seun, please fill out this part} due to slow convergence rate in the non-linear solution scheme.
+Running all the models in this group at the same mesh resolution of 4 km ensures intra-group consistency; and comparison with 2 km-resolution models is also justified because the descritization error does not dramatically increase as the resolution increases to 4 km (Fig.
+S1).
+This discussion is now included in Lines \annote[EC]{XXX-YYY}{Seun, please do add this discussion and fill out the line numbers here} of the revised manuscript.
 \end{response}

### 2019-06-28 main_full_manuscript.tex

--- 2019-06-28 main_full_manuscript.tex
@@
 \add[OF]{The average computation time was about 16 days for fault models ($\mu$ = 0.3) with 2 km element size on 16 cores on the University of Memphis High Performance Computing cluster.
-The model with fault dips of 65$^\circ$-40$^\circ$-40$^\circ$ took about twice longer to run for the same model time.
+The model with fault dips of 65$^\circ$-40$^\circ$-40$^\circ$ took about two times as long to run for the same model time.
 We do not clearly understand why the model with shallower-dipping faults is slower than the others roughly by a factor of two and further analyzing computational efficiency is beyond the scope of this paper.}
@@
 1).
-We did not consider the South Shore fault given its aseismic nature and \change[OF]{its location at the extreme eastern edge of the crater}{it appears to mark a boundary to the active zone}~\citep{lamontagne1999}.
+We did not consider the South Shore fault given its aseismic nature \change[OF]{and its location at the extreme eastern edge of the crater}{, although it appears to mark a boundary to the active zone}~\citep{lamontagne1999}.
 Our models show that a $\mu$ of 0.3 and cohesion values of 0 MPa create $\Delta\sigma_{D}^\prime$ maps that spatially correlate with the seismicity of CSZ and the observed stress rotations (Fig.
@@
 S6).
-Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.} \add[OF]{A $\mu$ of 0.4 could also be suitable for the rift faults as the $\Delta\sigma_{D}^\prime$ maps also spatially correlate with the seismicity of the CSZ, and some earthquakes also occurred at the SW region outside the impact structure (Fig.
-$\ref{figone}$).} %However, previous works in the CSZ agreed with a finite extent of the seismic zone} ~\citep[e.g.,][]{Stevens1980}.
+Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.} \add[OF]{A $\mu$ of 0.4 could also be suitable for the rift faults as the $\Delta\sigma_{D}^\prime$ maps spatially correlate with the seismicity of the CSZ.
+Some earthquakes also occurred at the SW region outside the impact structure (Fig.
+$\ref{figone}$), however, previous studies in the CSZ agreed with a finite extent of the seismicity}~\citep[e.g.,][]{Stevens1980}.
 \change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig. \ref{figone}).

### 2019-06-28 Rebuttal_Letter.tex
Addressed remaining comments in the Rebuttal letter and have updated the manuscript

@@
     If the term, ``the independency effect of involved factors'', means the effects of independently controlled parameters on model results.
-the independency is never assumed and only a logical outcome from our experiment design, in which a reference model is compared with a model with only one parameter changed.
+The independency is never assumed and only a logical outcome from our experiment design, in which a reference model is compared with a model with only one parameter changed.
 
@@
 The expanded set of models not only provide the sensitivity information but also confirm that the model responses are monotonous to the control parameters in the considered ranges of values.
-Furthermore, the revised manuscript includes an updated justification for the choice of model parameters such as friction coefficient and elastic moduli ratio.\note[EC]{Seun, specify where in the revised manuscript to look at for this information.} as well as  in the supplementary information (Figs.
-S3, S4 and \note[EC]{Why S5 is not listed?}S6)
+Furthermore, the revised manuscript includes an updated justification for the choice of model parameters such as friction coefficient and elastic moduli ratio (Lines 368-374 and 422-425) as well as  in the supplementary information (Figs.
+S3-6)
+    %\note[EC]{Seun, specify where in the revised manuscript to look at for this information.} %\note[EC]{Why S5 is not listed?}
 \end{response}
@@
 
-  We have added the computational efficiency of our model in the model geometry section (Lines 126-132) of the manuscript.
+  We have added the computational efficiency of our model in the model geometry section (Lines 131-137) of the manuscript.
 We did not add the computational efficiency to Table 1 because it does not change significantly among the models except for the SD65R25 model, which took about twice longer to run for the same model time.
@@
 Shear stress was not considered as a stopping criterion.
-In addition, we have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 530-540).
+In addition, we have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 534-546).
 
@@
 
-  The revised manuscript now includes a justification that the 10\% reduction of the density in the impact structure represents damage made to crustal rocks by the impact (Lines 177-180).
+  The revised manuscript now includes a justification that the 10\% reduction of the density in the impact structure represents damage made to crustal rocks by the impact (Lines 181-186).
 Since it is not known quantitatively how much the impact affected the crustal density and elastic moduli, we ran extra models to explore the effects of density reduction from 0 to 20 \%.
@@
 
-   We have added a quantitative assessment of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 199-203).
+   We have added a quantitative assessment of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 205-209).
 This metric is now used for describing the model results and comparing different models throughout the revised manuscript.
-We also added a discussion on the choice of the friction coefficient in Lines 506-509.
+We also added a discussion on the choice of the friction coefficient in Lines 512-518.
     %: 1) the change in differential stress maps changes with fault geometry, and we have established an along-strike variation in the fault dips in this study; and 2) the 3D velocity model is very well defined in the upper 5 km depth which may introduced an uncertainty in the hypocenter relocation.
@@
 We decided to run this particular group of models to acquire necessary information without increasing computational cost too much.
-Low-friction models, especially those with $\mu$ equal to 0.1 and 0.2, take \annote[EC]{up to XX weeks}{Seun, please fill out this part} due to slow convergence rate in the non-linear solution scheme.
+Low-friction models, especially those with $\mu$ equal to 0.1 and 0.2, are very expensive
+%take \annote[EC]{up to XX weeks}{Seun, please fill out this part} 
+due to slow convergence rate in the non-linear solution scheme.
 Running all the models in this group at the same mesh resolution of 4 km ensures intra-group consistency; and comparison with 2 km-resolution models is also justified because the descritization error does not dramatically increase as the resolution increases to 4 km (Fig.
 S1).
-This discussion is now included in Lines \annote[EC]{XXX-YYY}{Seun, please do add this discussion and fill out the line numbers here} of the revised manuscript.
+This discussion is now included in Lines 118 to 127 of the revised manuscript.
+% \annote[EC]{XXX-YYY}{Seun, please do add this discussion and fill out the line numbers here}
 \end{response}
@@
 
-  We have added an appropriate reference (Line 436).
+  We have added an appropriate reference (Line 443).
 \end{response}
@@
 
-  We have edited the manuscript accordingly (see Lines 447-449). We have also included the findings of Steven (1980) in our discussion.
+  We have edited the manuscript accordingly (see Lines 454-456). We have also included the findings of Steven (1980) in our discussion.
 \end{response}
@@
 
- The focal mechanisms are good, and we suggest that the focal mechanisms can be further constrained using waveform modeling to validate the magnitude of the stress rotation (Lines 563-565).
+ The focal mechanisms are good, and we suggest that the focal mechanisms can be further constrained using waveform modeling to validate the magnitude of the stress rotation (Lines 569-572).
 \end{response}
@@
 The higher stopping criterion in our study is necessary to make faults slip at seismogenic depth under the assumption.
-We have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 530-540).
+We have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 534-546).
 \end{response}

### 2019-06-28 main_full_manuscript.tex
Addressed remaining comments in the Rebuttal letter and have updated the manuscript

@@
 S1)}.
-\add[OF]{Based on the resolution tests, we use the element size of 2 km for most of the models and 4 km for more computationally expensive models like those for exploring the effects of the friction coefficient.} We also observe edge effects by comparing a 420 $\times$ 420 $\times$ 40 km model with the original 220 $\times$ 220 $\times$ 40 km model, finding that the seismogenic parts around the \change[OF]{crater}{impact structure} show consistent displacement and stress solutions for both domain sizes.
+\add[OF]{Based on the resolution tests, we use the element size of 2 km for most of the models and 4 km for more computationally expensive models like those for exploring the effects of the friction coefficient.
+Low-friction models, especially those with $\mu$ equal to 0.1 and 0.2, are very expensive due to slow convergence rate in the non-linear solution scheme.
+Running all the models in this group at the same mesh resolution of 4 km ensures intra-group consistency; and the comparison with 2 km-resolution models is also justified because the descritization error does not dramatically increase as the resolution increases to 4 km (Fig.
+S1).} We also observe edge effects by comparing a 420 $\times$ 420 $\times$ 40 km model with the original 220 $\times$ 220 $\times$ 40 km model, finding that the seismogenic parts around the \change[OF]{crater}{impact structure} show consistent displacement and stress solutions for both domain sizes.
 Based on this result, we choose the smaller domain for this study and set the element size to be about 2 km.
@@
 \ref{fig:eff_of_moduli_ratio}B).
-In contrast, when the \change[OF]{crater}{impact structure} is set to be \change[OF]{less elastically stiff}{elastically softer} than the surrounding crust, positive $\Delta \sigma_{D}^{\prime}$ regions spatially coincide with the observed seismicity in the CSZ, especially above 15 km depth (e.g., Fig.
+In contrast, when the \change[OF]{crater}{impact structure} is set to be \change[OF]{less elastically stiff}{elastically softer} than the surrounding crust \add[OF]{ by up to a factor of 4}, positive $\Delta \sigma_{D}^{\prime}$ regions spatially coincide with the observed seismicity in the CSZ, especially above 15 km depth (e.g., Fig.
 \ref{fig:SD70R25}C).

### 2019-06-29 Rebuttal_Letter.tex
saving progress.

@@
 No significant changes in the model results were found in these models.
-These new results are now included in the supplementary information and Fig.
+These new results are included in the supplementary information and Fig.
 S3 therein.
@@
 
-We decided to run this particular group of models to acquire necessary information without increasing computational cost too much.
-Low-friction models, especially those with $\mu$ equal to 0.1 and 0.2, are very expensive
-%take \annote[EC]{up to XX weeks}{Seun, please fill out this part} 
-due to slow convergence rate in the non-linear solution scheme.
-Running all the models in this group at the same mesh resolution of 4 km ensures intra-group consistency; and comparison with 2 km-resolution models is also justified because the descritization error does not dramatically increase as the resolution increases to 4 km (Fig.
+We decided to run the models for various friction coefficients at the 4 km resolution to acquire necessary information without increasing computational cost too much.
+The low-friction models suffer slow convergence rate in the non-linear solution scheme.
+For instance, the models with $\mu$ equal to 0.1 and 0.2 were let run for 4 weeks on 40 cores to progress only to about half of the target model time.
+Running all the models in this group at the same mesh resolution of 4 km ensures intra-group consistency but at the same time, comparison with 2 km-resolution models is also justified because the descritization error does not significantly increase as the resolution increases from 2 to 4 km (Fig.
 S1).
 This discussion is now included in Lines 118 to 127 of the revised manuscript.
-% \annote[EC]{XXX-YYY}{Seun, please do add this discussion and fill out the line numbers here}
 \end{response}

### 2019-06-29 Supporting_Information.tex
saving progress.

@@
 \usepackage{rotating}
+\usepackage[inline]{trackchanges}
+\addeditor{EC}
+\addeditor{OF}
 \usepackage{graphicx}
@@
 
-From $\Delta$ABC in Fig.~\ref{S2},
+From $\Delta$ABC in Fig.~\ref{S2}, the illustration of the Mohr circle and the Byerlees law, we get
 \[
- \sin \alpha = \frac{\sigma_{1}-\sigma_{3}}{2} / \left[\frac{250}{3} + \frac{\sigma_{1}+\sigma_{3}}{2} \right],
+ \sin \alpha = \frac{\sigma_{1}-\sigma_{3}}{2} / \left[\frac{250}{3} + \frac{\sigma_{1}+\sigma_{3}}{2} \right].
 \]
 %
+%\[
+% \sin \alpha = \frac{3(\sigma_{1}-\sigma_{3})}{3(\sigma_{1}+\sigma_{3})+500},
+%\]
+%
+After simpligying and solving for $\sigma_{1}$, we ge the following expression:
 \[
- \sin \alpha = \frac{3(\sigma_{1}-\sigma_{3})}{3(\sigma_{1}+\sigma_{3})+500},
-\]
-%
-\[
- \sigma_{1} = \frac{\sigma_{3}+[\sigma_{3}+\frac{500}{3}] \sin(\alpha)}{1-\sin \alpha},
+ \sigma_{1} = \frac{\sigma_{3}+[\sigma_{3}+\frac{500}{3}] \sin(\alpha)}{1-\sin \alpha}.
 \]
@@
 Based on Byerlee's law, $\tau$  = 50 MPa + 0.6$\,\sigma_n$, under the assumption of absence of pore-fluid pressure along the rift faults, $\tan \alpha = 0.6$, hence, $\sin \alpha = 0.5145$.
-$\sigma_{3}$ corresponds to the lithostatic stress, and assuming it is equal to 250 MPa at 10 km depth, gives $\sigma_{1}$ = 956.4882 MPa.
-Hence, the differential stress at 10 km depth with no pore-fluid pressure ($\sigma_{D} = \sigma_{1} - \sigma_{3})$ is 706.4882 MPa.
+$\sigma_{3}$ corresponds to the lithostatic stress amounting to 250.0 MPa at 10 km depth \add[EC]{for a density of XXXX kg/m$^{3}$}.
+With these values and the above expression, we get $\sigma_{1}$ = \annote[EC]{956.5}{Pay attention to the number of significant figures!
+I don't think our calculations can afford 7 or 8-digit precision so I rounded off the original value leaving 4 digits.} MPa.
+The differential stress at 10 km depth with no pore-fluid pressure, defined as $\sigma_{D} = \sigma_{1} - \sigma_{3})$, is 706.5 MPa.
 
@@
 
-The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio (Fig.
+\note[EC]{Turn the first long phrase into a sentence.
+Right now it reads like a figure caption but it shouldn't in a normal paragraph.} The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio (Fig.
 \ref{S3}).
 The maps show no significant change with density ratio.
-We use density ratio of 10\% in this study to model a realistic damaged crustal rock.
+In this study, we choose the density ratio of 10\% to represent damaged crustal rock.
 \vspace{10mm} %5mm vertical space
@@
 \includegraphics[width=25pc]{Figures/effect_of_density.png}
-\caption{Effect of impact structure-crust density ratio on the $\Delta\sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ at 10 km depth.
+\caption{\note[EC]{Symbol descriptions are missing.
+Include those in Fig.
+S4 caption.} Effect of impact structure-crust density ratio on the $\Delta\sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ at 10 km depth.
 Earthquakes within 2 km of each depth slice are represented by black dots in \ref{S3}A.
@@
 
-The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model (Fig.
+\note[EC]{Turn the first long phrase into a sentence.
+Right now it reads like a figure caption but it shouldn't in a normal paragraph.} The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model (Fig.
 \ref{S4}).
@@
 \includegraphics[width=25pc]{Figures/SD70R100_S1.png}
-\caption{Percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the SNFR25 at various depths depths from the SD70R100 model.
+\caption{Percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) in SD70R100 relative to SNFR25 at various depths.
 Earthquakes within 2 km of each depth slice are represented by black dots in \ref{S3}A.
@@
 
-We test the response of the model results with different impact structure-crust moduli ratio (Fig.
-\ref{S5}).
-The model with a moduli ratio of 1.0 does not have the impact crater.
+We run 4 models in total to assess the effects of impact structure-to-crust moduli ratio assuming that the impact structure was softened.
+The ratio equal to 1, for instance, means that the impact structure was not softened and thus has the elastic moduli with those of the surrounding crust.
 The models show a better spatial correlation with the observed seismicity when the moduli ratio is 0.25.
@@
 
-We compute $\Delta \sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ in a series of models in which the rift faults dip at 70$^{\circ}$ (i.e., SD70R25) but their cohesion ($C$) is varied systematically at a constant coefficient of friction ($\mu$) of 0.3.
-We assume that the fault parameters are the same for each rift fault and uniform throughout the fault surfaces.
-Six models with 0, 3, 5, 10, 20 and 30 MPa are constructed (Fig.
+We compute $\Delta \sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ in a series of models in which the rift faults dip at 70$^{\circ}$ (i.e., SD70R25) but their cohesion ($C$) is varied from 0 to 30 MPa while the friction coefficient ($\mu$) is fixed at 0.3 (Fig.~\ref{S6}).
+We assume that the fault parameters are the same for each of the three rift faults and uniform throughout the fault surfaces.
+%Six models with 0, 3, 5, 10, 20 and 30 MPa are constructed (Fig.
 \ref{S6}).
 
-Magnitudes of $\Delta\sigma_D^{\prime}$ and $\phi_{\max}$ decrease with increasing cohesion.
-$\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity at all the fault cohesions, especially well when the cohesion is less than 5 MPa (Fig.
+Magnitudes of $\Delta\sigma_D^{\prime}$ and \annote[EC]{$\phi_{\max}$}{Fig.
+S6B doesn't support this.} decrease with increasing cohesion.
+$\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity for all the fault cohesions\annote[EC]{, especially well when the cohesion is less than 5 MPa}{What makes you say so?
+Can't you use the new metric for this argument?} (Fig.
 \ref{S6}A).
-However, the models could not explain some earthquakes in the SW corner of the crater.
+However, the models could not explain a few earthquakes in the SW corner of the crater, where $\Delta\sigma_D^{\prime}$ is negative.
 The $\Delta\sigma_D^{\prime}$ is not affected by a change in cohesion between 0 and 5 MPa.
@@
 
-Figure \ref{S6} shows that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope.
-We use a cohesion value of 0 MPa to explain the spatial distribution of observed seismicity in the CSZ.
+\note[EC]{Why do you make remarks on $\mu$ mentioning cohesion only little in the paragraph for the effects of cohesion?} Figure \ref{S6} suggests that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope.
+We present models with zero cohesion in the main text because to explain the spatial distribution of observed seismicity in the CSZ.
 

### 2019-06-29 main_full_manuscript.tex
saving progress

@@
 Low-friction models, especially those with $\mu$ equal to 0.1 and 0.2, are very expensive due to slow convergence rate in the non-linear solution scheme.
-Running all the models in this group at the same mesh resolution of 4 km ensures intra-group consistency; and the comparison with 2 km-resolution models is also justified because the descritization error does not dramatically increase as the resolution increases to 4 km (Fig.
+Running all the models in this group at the same mesh resolution of 4 km ensures intra-group consistency; and the comparison with 2 km-resolution models is also justified because the descritization error does not significantly increase as the resolution increases to 4 km (Fig.
 S1).} We also observe edge effects by comparing a 420 $\times$ 420 $\times$ 40 km model with the original 220 $\times$ 220 $\times$ 40 km model, finding that the seismogenic parts around the \change[OF]{crater}{impact structure} show consistent displacement and stress solutions for both domain sizes.
@@
 For simplicity, we assume that the \change[OF]{crater}{impact structure}'s bulk and shear moduli are a certain fraction of those of the crust~\citep[e.g.,][]{Baird_2010}.
-Similarly, the density of the \change[OF]{crater}{impact structure} is reduced \remove[OF]{by 10 \%} from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a damaged crustal rock.
+Similarly, the density of the \change[OF]{crater}{impact structure} is reduced \remove[OF]{by 10 \%} from that of the 1D velocity models over the corresponding depth range \add[OF]{to model damaged crustal rocks.
 Models with density reduced by 0 to 20 \% were run but did not exhibit significant changes as shown in Fig.
 S3 in the supplementary information.
-Unless stated otherwise, models presented in this study have 10 \% of density reduction in the impact structure.}
+All the models presented in this study have 10 \% of density reduction in the impact structure.}
 
@@
 We assume that $\mu$ and $C$ are uniform on the fault planes in each model but investigate the consequences of varying $\mu$ from 0.1 to 0.6 at a constant $C$ of 0 MPa.
-\add[OF]{We choose zero cohesion because it is appropriate for pre-existing faults with low normal stress}~\citep{Marone_Chris}.
+\add[OF]{Although cohesion values from 0 to 30 MPa have been tested and found to have significant effects, we choose to present models with zero cohesion in this study because it is appropriate for pre-existing faults with low normal stress}~\citep[e.g.,][]{Marone_Chris}.
+\add[OF]{We note that the deep portions of the model faults might not satisfy the condition of low normal stress and thus a further investigation on the depth-variation of cohesion is desirable.}
 %\add[OF]{and slips on the model faults occur only down to about 10 km depth satisfying this condition.} 
@@
 \ref{fig:eff_of_mu}A) because the model behaviors must approach those of the no-fault model as fault strength increases.
-When $\mu$ values are 0.1 and 0.2, the area of positive $\Delta\sigma_{D}^{\prime}$ regions does not cover the entire observed seismicity\add[OF]{, with about 3\% and 24\% of the hypocenters in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, respectively}.
+When $\mu$ values are 0.1 and 0.2, the area of positive $\Delta\sigma_{D}^{\prime}$ regions does not cover the entire observed seismicity\add[OF]{, with about 3 and 24\% of the hypocenters within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, respectively}.
 The regions of positive $\Delta\sigma_{D}^{\prime}$ for $\mu$ values equal to 0.3 and 0.4 show better spatial correspondence with the seismicity of the CSZ.
 However, the model with $\mu = 0.4$ predicts positive Coulomb stress changes along the entire length of the rift faults, which is contrary to the limited spatial extent of the observed seismicity.
-\add[OF]{Also, about 66\% of the hypocenters in the model with a $\mu$ of 0.3 fall within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, compared to a value of 35\% when $\mu$ is 0.4.
-However, when we consider the region with $\Delta\sigma_{D}^{\prime} \ge$ 0\%, the percentage increases to 82\% when $\mu$ is 0.4 compared to 73\% in the model with $\mu$ equal 0.3.} $\Delta\sigma_{D}^{\prime}$ approaches zero when $\mu$ values are 0.5 and 0.6, for which the faults are locked.
+\add[OF]{Also, about 66\% of the hypocenters in the model with $\mu$ = 0.3 fall within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% while only 35\% do when $\mu$ = 0.4.
+However, when the hypocenters falling in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0\% are considered, the percentages increase to 73 and 82\% for $\mu$ equal to 0.3 and 0.4.}
+$\Delta\sigma_{D}^{\prime}$ approaches zero when $\mu$ values are 0.5 and 0.6, for which the faults are locked.
 \add[OF]{The percentage of hypocenters in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% reduces to 1.4\% and 0\% when $\mu$ values are 0.5 and 0.6, respectively.}
@@
 S6).
-Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.} \add[OF]{A $\mu$ of 0.4 could also be suitable for the rift faults as the $\Delta\sigma_{D}^\prime$ maps spatially correlate with the seismicity of the CSZ.
-Some earthquakes also occurred at the SW region outside the impact structure (Fig.
+Cohesion values less than 5 MPa could better explain the spatial distribution of observed seismicity in the CSZ than the greater values.} \add[OF]{$\mu$ equal to 0.4 also seems suitable to the rift faults as the $\Delta\sigma_{D}^\prime$ maps spatially correlate well with the seismicity of the CSZ.
+A small number of earthquakes also occurred at the SW region outside the impact structure (Fig.
 $\ref{figone}$), however, previous studies in the CSZ agreed with a finite extent of the seismicity}~\citep[e.g.,][]{Stevens1980}.
-\change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig. \ref{figone}).
+\note[EC]{I don't understand the point of the sentence about the finite extent of the seismicity.
+Is it necessary?}
+\change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig.
+\ref{figone}).
+\note[EC]{This sentence should be in the model setup unless you want to discuss implications of this difference.}
 
@@
 a $\mu$ of about 0.1.
-The higher stopping criterion in our study is based on Byerlee's law under the assumption of no pore-fluid pressure on the rift faults, and it is necessary to make faults slip at seismogenic depth.
-Inclusion of pore-fluid pressure can significantly reduce the magnitude of $\sigma_{D}$ used as the stopping criterion.} The stopping criteria of a $\sigma_{D}$ of 200 MPa at 10 km depth would not make rifts faults with $\mu \ge 0.3$ slip \add[OF]{at seismogenic depths unless high pore fluid pressures are present.
+The higher stopping criterion in our study is based on Byerlee's law under the assumption of no pore-fluid pressure on the rift faults, and it is necessary to make faults slip at seismogenic depth when $\mu$ is 0.3 as assumed in this study.
+Inclusion of pore-fluid pressure can significantly reduce the magnitude of $\sigma_{D}$ used as the stopping criterion.
+In other words, the lower stopping criterion, $\sigma_{D}$ equal to 200 MPa at 10 km depth, might be sufficient for rifts faults with $\mu$ = 0.3 or 0.4 to slip if pore fluid pressure is sufficiently high.
 Another possible consequences of pore-fluid pressure is that faults could be reactivated at smaller angles from the maximum compressive stress}~\citep[e.g.,][]{ChenChen18}.
@@
 \remove[OF]{The high stress rotation could also be due to unconstrained focal mechanisms used in the stress inversion.} Most of the focal mechanisms used for stress inversion \add[OF]{in the CSZ} are obtained from first motion P and SH waves~\citep{Mazzotti_2010,lamontagne1998}.
-\change[OF]{Better constrained}{The} focal mechanisms \add[OF]{are good, and we suggest that the focal mechanisms can be further constrained} using waveform modeling \remove[OF]{will be needed} to validate the magnitude of the stress rotation.
+\change[OF]{Better constrained}{The} focal mechanisms \note[EC]{What do you mean by ``focal mechanisms are `good\rq{}''?
+It would be good/nice to have better constrained ones, you mean?}\add[OF]{are good, and we suggest that the focal mechanisms can be further constrained} using waveform modeling \remove[OF]{will be needed} to validate the magnitude of the stress rotation.
 

### 2019-06-30 Rebuttal_Letter.tex
Addressed comments and changed figure background from transp to white.

--- 2019-06-28 Rebuttal_Letter.tex
@@
 The expanded set of models not only provide the sensitivity information but also confirm that the model responses are monotonous to the control parameters in the considered ranges of values.
-Furthermore, the revised manuscript includes an updated justification for the choice of model parameters such as friction coefficient and elastic moduli ratio (Lines 368-374 and 422-425) as well as  in the supplementary information (Figs.
+Furthermore, the revised manuscript includes an updated justification for the choice of model parameters such as friction coefficient and elastic moduli ratio (Lines 377-383 and 431-434) as well as  in the supplementary information (Figs.
 S3-6)
@@
 Shear stress was not considered as a stopping criterion.
-In addition, we have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 534-546).
+In addition, we have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 538-549).
 
@@
 
-   We have added a quantitative assessment of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 205-209).
+   We have added a quantitative assessment of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 209-213).
 This metric is now used for describing the model results and comparing different models throughout the revised manuscript.
@@
 
-  We have added an appropriate reference (Line 443).
+  We have added an appropriate reference (Line 447).
 \end{response}
@@
 1.
-We represented the relocated hypocenters of Powell and Lamontagne (2017) as circles and the other earthquakes that are not in the relocated catalog as diamonds.
+We represented the relocated hypocenters of Powell and Lamontagne (2017) as circles and the other earthquakes that are not in the relocated catalog as stars.
 \end{response}
@@
 
-  We have edited the manuscript accordingly (see Lines 454-456). We have also included the findings of Steven (1980) in our discussion.
+  We have edited the manuscript accordingly (see Lines 458-460). We have also included the findings of Steven (1980) in our discussion.
 \end{response}
@@
 
- The focal mechanisms are good, and we suggest that the focal mechanisms can be further constrained using waveform modeling to validate the magnitude of the stress rotation (Lines 569-572).
+ The focal mechanisms are well defined, and we suggest that the focal mechanisms can be further constrained using waveform modeling to validate the magnitude of the stress rotation (Lines 572-575).
 \end{response}
@@
 The higher stopping criterion in our study is necessary to make faults slip at seismogenic depth under the assumption.
-We have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 534-546).
+We have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 538-549).
 \end{response}

### 2019-06-30 Supporting_Information.tex
Addressed comments and changed figure background from transp to white.

@@
 \noindent\textbf{Stopping criterion of differential stress at 10 km depth}
-\vspace{10mm} %5mm vertical space
+%\vspace{10mm} %5mm vertical space
 
@@
 Based on Byerlee's law, $\tau$  = 50 MPa + 0.6$\,\sigma_n$, under the assumption of absence of pore-fluid pressure along the rift faults, $\tan \alpha = 0.6$, hence, $\sin \alpha = 0.5145$.
-$\sigma_{3}$ corresponds to the lithostatic stress amounting to 250.0 MPa at 10 km depth \add[EC]{for a density of XXXX kg/m$^{3}$}.
-With these values and the above expression, we get $\sigma_{1}$ = \annote[EC]{956.5}{Pay attention to the number of significant figures!
-I don't think our calculations can afford 7 or 8-digit precision so I rounded off the original value leaving 4 digits.} MPa.
-The differential stress at 10 km depth with no pore-fluid pressure, defined as $\sigma_{D} = \sigma_{1} - \sigma_{3})$, is 706.5 MPa.
+$\sigma_{3}$ corresponds to the lithostatic stress amounting to 250.0 MPa at 10 km depth for a density of 2.55 kg/m$^{3}$.
+%\add[EC]{for a density of XXXX kg/m$^{3}$}. 
+With these values and the above expression, we get $\sigma_{1}$ = 956.5 MPa.
+%\annote[EC]{956.5}{Pay attention to the number of significant figures! I don't think our calculations can afford 7 or 8-digit precision so I rounded off the original value leaving 4 digits.} MPa. 
+The differential stress at 10 km depth with no pore-fluid pressure, defined as $\sigma_{D} = \sigma_{1} - \sigma_{3}$, is 706.5 MPa.
 
@@
 
-\note[EC]{Turn the first long phrase into a sentence.
+%\note[EC]{Turn the first long phrase into a sentence.
 Right now it reads like a figure caption but it shouldn't in a normal paragraph.} The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio (Fig.
 \ref{S3}).
-The maps show no significant change with density ratio.
+
+We explore the effects of density reduction from 0 to 20 \% in a series of models in which the rift faults dip at 70$^{\circ}$ (i.e., SD70R25) (Fig.
+\ref{S3}).
+No significant changes in the model results were found in these models.
 In this study, we choose the density ratio of 10\% to represent damaged crustal rock.
@@
 \includegraphics[width=25pc]{Figures/effect_of_density.png}
-\caption{\note[EC]{Symbol descriptions are missing.
-Include those in Fig.
-S4 caption.} Effect of impact structure-crust density ratio on the $\Delta\sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ at 10 km depth.
+\caption{
+%\note[EC]{Symbol descriptions are missing. Include those in Fig. S4 caption.} 
+Effect of impact structure-crust density ratio on the percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$) and the change in $\phi_{\max}$ ($\Delta \phi_{\max}^{\prime}$) at 10 km depth.
 Earthquakes within 2 km of each depth slice are represented by black dots in \ref{S3}A.
@@
 
-\note[EC]{Turn the first long phrase into a sentence.
+We compute $\Delta \sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ in the SD70R100 model (Fig.
+\ref{S4}).
+The model exhibit the effects of the rift faults since the impact structure and the crust have the same elastic moduli.
+%\note[EC]{Turn the first long phrase into a sentence.
 Right now it reads like a figure caption but it shouldn't in a normal paragraph.} The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model (Fig.
@@
 
-We run 4 models in total to assess the effects of impact structure-to-crust moduli ratio assuming that the impact structure was softened.
+We run 4 models in total to assess the effects of impact structure-to-crust moduli ratio assuming that the impact structure was softened (Fig.
+\ref{S5}).
 The ratio equal to 1, for instance, means that the impact structure was not softened and thus has the elastic moduli with those of the surrounding crust.
@@
 
-Magnitudes of $\Delta\sigma_D^{\prime}$ and \annote[EC]{$\phi_{\max}$}{Fig.
-S6B doesn't support this.} decrease with increasing cohesion.
-$\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity for all the fault cohesions\annote[EC]{, especially well when the cohesion is less than 5 MPa}{What makes you say so?
-Can't you use the new metric for this argument?} (Fig.
+%\vspace{10mm} %5mm vertical space
+
+\begin{figure}[ht]
+\setfigurenum{S6}
+\includegraphics[width=25pc]{Figures/SD70R25C_S6.png}
+\caption{Same as \ref{S3} but for the models with different cohesion values.}
+\label{S6}
+\end{figure}
+
+%\vspace{10mm} %5mm vertical space
+
+Magnitudes of $\Delta\sigma_D^{\prime}$ % and \annote[EC]{$\phi_{\max}$}{Fig. S6B doesn't support this.} 
+decrease with increasing cohesion. $\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity %for all the fault cohesions, especially well 
+when the cohesion is less than 5 MPa with about 70\% of the hypocenters fall in the region with $\Delta\sigma_D^{\prime} \ge$ 0.5\% (Fig.
 \ref{S6}A).
+%The percentages of the hypocenters in the region with $\Delta\sigma_D^{\prime} \ge$ 0.5\% decrease to 61\% and 47\% for cohesion values of 20 and 30 MPa, respectively.
+%\annote[EC]{, especially well when the cohesion is less than 5 MPa}{What makes you say so? Can't you use the new metric for this argument?} (Fig. \ref{S6}A). 
 However, the models could not explain a few earthquakes in the SW corner of the crater, where $\Delta\sigma_D^{\prime}$ is negative.
@@
 $\Delta\phi_{\max}$ is up to 10.8$^\circ$ when the cohesion is less than 5 MPa.
+We present models with zero cohesion in the main text to explain the spatial distribution of observed seismicity in the CSZ.
 
-\note[EC]{Why do you make remarks on $\mu$ mentioning cohesion only little in the paragraph for the effects of cohesion?} Figure \ref{S6} suggests that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope.
+%\note[EC]{Why do you make remarks on $\mu$ mentioning cohesion only little in the paragraph for the effects of cohesion?} Figure \ref{S6} suggests that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope.
 We present models with zero cohesion in the main text because to explain the spatial distribution of observed seismicity in the CSZ.
 
-\vspace{10mm} %5mm vertical space
-
-\begin{figure}[ht]
-\setfigurenum{S6}
-\includegraphics[width=25pc]{Figures/SD70R25C_S2.png}
-\caption{Same as \ref{S3} but for the models with different cohesion values.}
-\label{S6}
-\end{figure}
-
-\vspace{10mm} %5mm vertical space
-
-\pagebreak
+%\pagebreak
 

### 2019-06-30 main_full_manuscript.tex
Addressed comments and changed figure background from transp to white.

@@
 \usepackage{apacite} 
+\bibliographystyle{apacite}
+
 \usepackage{comment}
@@
 \hline
-\multicolumn{8}{l}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}.$^{*}$K, G at 10 km depth.} \\
+\multicolumn{8}{l}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}. $^{*}$K, G at 10 km depth.} \\
 \multicolumn{8}{l}{$^{\dagger}$$\mu$, $C$, $K$ and $G$ are friction coefficient, cohesion, bulk and shear modulus, respectively.}
@@
 A small number of earthquakes also occurred at the SW region outside the impact structure (Fig.
-$\ref{figone}$), however, previous studies in the CSZ agreed with a finite extent of the seismicity}~\citep[e.g.,][]{Stevens1980}.
+$\ref{figone}$)}.
+%, however, previous studies in the CSZ agreed with a finite extent of the seismicity}~\citep[e.g.,][]{Stevens1980}.
 \note[EC]{I don't understand the point of the sentence about the finite extent of the seismicity.
-Is it necessary?}
-\change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig.
+Is it necessary?}\change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig.
 \ref{figone}).
@@
 \remove[OF]{The high stress rotation could also be due to unconstrained focal mechanisms used in the stress inversion.} Most of the focal mechanisms used for stress inversion \add[OF]{in the CSZ} are obtained from first motion P and SH waves~\citep{Mazzotti_2010,lamontagne1998}.
-\change[OF]{Better constrained}{The} focal mechanisms \note[EC]{What do you mean by ``focal mechanisms are `good\rq{}''?
-It would be good/nice to have better constrained ones, you mean?}\add[OF]{are good, and we suggest that the focal mechanisms can be further constrained} using waveform modeling \remove[OF]{will be needed} to validate the magnitude of the stress rotation.
+\change[OF]{Better constrained}{The} focal mechanisms %\note[EC]{What do you mean by ``focal mechanisms are `good\rq{}''?
+It would be good/nice to have better constrained ones, you mean?}
+\add[OF]{are well defined, and we suggest that the focal mechanisms can be further constrained} using waveform modeling \remove[OF]{will be needed} to validate the magnitude of the stress rotation.
 

### 2019-07-01 Rebuttal_Letter.tex
Removed all comments and created a manuscript without trackchanges

@@
 \title{}
-%\title{Statement on the Revision of \meta{Paper \#2019JB017831} \\
-%  Based on the Referees' Report}
-%\author{Oluwaseun Idowu Fadugba \and Eunseo Choi \and Christine A. Powell}
-%\date{\today}
 \date{}
@@
 \noindent Dear Dr Yehuda Ben-Zion,
-%\add[EC]{[the name of the handling editor]}, 
 \\\vspace{1em}
@@
 S3-6)
-    %\note[EC]{Seun, specify where in the revised manuscript to look at for this information.} %\note[EC]{Why S5 is not listed?}
 \end{response}
-
-%\textbf{We addressed the line-by-line comments below.}
 
@@
 
-  %\add[EC]{, which took about twice longer to run for the same model time.} \annote[EC]{which may be due to the shallower fault dips.}{The shallower fault dips are the difference of SD65R25 from the others but does not directly explain why this model should take much less time.
-We can go ahead and speculate about possible reasons but it would be just enough to say that we do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper.}
-  %\annote[EC]{except for the SD65R25 model}{This model then needs further explanation why it took a significantly longer or short time}. 
-  %\note[EC]{Is there a reason why you did not follow the reviewer's suggestion to add this into to Table 1?}
 \end{response}
@@
 
-  %\annote[EC]{We agree with the reviewer}{Agree only when you are sure that doing so would not negatively affect your arguments, assumptions or the overall integrity of your paper.
-Never confess; only justify.} on the high differential stress at seismogenic depth in our study, due to}
-  The differential stress of 706 MPa at 10 km depth is based on Byerlee's law under the assumption of  
-  %$\mu$ equal to 0.6 and \add[OF]{The equation of Byerlee's law has a μ value of 0.6. It is not an assumption in our study.}
-  %\add[EC]{$\mu$ equal to 0.6 and} 
-  the absence of pore-fluid pressure.
+  The differential stress of 706 MPa at 10 km depth is based on Byerlee's law under the assumption of the absence of pore-fluid pressure.
 The full derivation of this value is now provided in the supplementary information.
@@
 For readers' reference, however, we now list representative values of elastic moduli in Table 1.
-  %\add[EC]{For readers' reference, however, we now list representative values of elastic moduli in Table 1.}\note[EC]{Seun, please take care of this.}
+
 \end{response}
@@
 
-   % The faults in our models extend to 40 km but slips on them occur only down to about 10 km due to our stopping criterion. %{Correct this if I'm wrong.} 
-   % Since the non-slipping portion of the faults are irrelevant, the condition of low normal stress is already being satisfied.
-For reference, however, we have explored non-zero values of cohesion and their impact on the results are shown in Fig.
-S4 in the supplementary information.
-
     We have explored non-zero values of cohesion and their impact on the results are shown in Fig.
@@
 We also added a discussion on the choice of the friction coefficient in Lines 512-518.
-    %: 1) the change in differential stress maps changes with fault geometry, and we have established an along-strike variation in the fault dips in this study; and 2) the 3D velocity model is very well defined in the upper 5 km depth which may introduced an uncertainty in the hypocenter relocation.
+
 \end{response}
@@
 We decided to run this particular group of models to acquire necessary information without increasing computational cost too much.
-Low-friction models, especially those with $\mu$ equal to 0.1 and 0.2, are very expensive
-%take \annote[EC]{up to XX weeks}{Seun, please fill out this part} 
-due to slow convergence rate in the non-linear solution scheme.
+Low-friction models, especially those with $\mu$ equal to 0.1 and 0.2, are very expensive due to slow convergence rate in the non-linear solution scheme.
 Running all the models in this group at the same mesh resolution of 4 km ensures intra-group consistency; and comparison with 2 km-resolution models is also justified because the descritization error does not dramatically increase as the resolution increases to 4 km (Fig.
@@
 This discussion is now included in Lines 118 to 127 of the revised manuscript.
-% \annote[EC]{XXX-YYY}{Seun, please do add this discussion and fill out the line numbers here}
+
 \end{response}
@@
 1.
-
- %\annote[EC]{Some earthquakes occurred at the SW region outside the impact structure, as shown in the updated Fig.
-1.
-However, reexamination of historical earthquakes in the Charlevoix area by Stevens (1980) also supports a finite extent of the observed seismicity in the CSZ.}{This response is not addressing the reviewer's concern.
-}
 

### 2019-07-01 Supporting_Information.tex
Removed all comments and created a manuscript without trackchanges

@@
 
-This supplement presents the resolution test in our study, the derivation of the stopping criterion, effect of density ratio, cohesion, and moduli ratio on stress models.
+This supplement presents the resolution test in our study, the derivation of the stopping criterion, effect of density ratio, moduli ratio, and cohesion on stress models.
 
@@
 \ref{S1}).
-%For example, the model has an error of about 0.02 and 0.16 in the $\sigma_{D}$ and $\phi_{\max}$ in element size of 2 km relative to 1 km, respectively (Fig.
-\ref{S2}).
-The error values increase to 0.06 and 0.26 when the element size is 4 km.
 The errors in displacement components and differential stress in models with element sizes of 2 km is less than 5 \% of the corresponding values in the model with 1 km resolution.
@@
 \noindent\textbf{Stopping criterion of differential stress at 10 km depth}
-%\vspace{10mm} %5mm vertical space
 
@@
 %
-%\[
-% \sin \alpha = \frac{3(\sigma_{1}-\sigma_{3})}{3(\sigma_{1}+\sigma_{3})+500},
-%\]
-%
-After simpligying and solving for $\sigma_{1}$, we ge the following expression:
+After simplifying and solving for $\sigma_{1}$, we ge the following expression:
 \[
@@
 $\sigma_{3}$ corresponds to the lithostatic stress amounting to 250.0 MPa at 10 km depth for a density of 2.55 kg/m$^{3}$.
-%\add[EC]{for a density of XXXX kg/m$^{3}$}. 
 With these values and the above expression, we get $\sigma_{1}$ = 956.5 MPa.
-%\annote[EC]{956.5}{Pay attention to the number of significant figures! I don't think our calculations can afford 7 or 8-digit precision so I rounded off the original value leaving 4 digits.} MPa. 
 The differential stress at 10 km depth with no pore-fluid pressure, defined as $\sigma_{D} = \sigma_{1} - \sigma_{3}$, is 706.5 MPa.
@@
 \noindent\textbf{Effects of density ratio in the impact structure}
-
-%\note[EC]{Turn the first long phrase into a sentence.
-Right now it reads like a figure caption but it shouldn't in a normal paragraph.} The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio (Fig.
-\ref{S3}).
 
@@
 \includegraphics[width=25pc]{Figures/effect_of_density.png}
-\caption{
-%\note[EC]{Symbol descriptions are missing. Include those in Fig. S4 caption.} 
-Effect of impact structure-crust density ratio on the percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$) and the change in $\phi_{\max}$ ($\Delta \phi_{\max}^{\prime}$) at 10 km depth.
+\caption{Effect of impact structure-crust density ratio on the percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$) and the change in $\phi_{\max}$ ($\Delta \phi_{\max}^{\prime}$) at 10 km depth.
 Earthquakes within 2 km of each depth slice are represented by black dots in \ref{S3}A.
-The outline of the impact structure is represented as black circle.
+The outline of the impact structure is represented as a black circle.
 Each figure is 70 $\times$ 70 km.}
@@
 The model exhibit the effects of the rift faults since the impact structure and the crust have the same elastic moduli.
-%\note[EC]{Turn the first long phrase into a sentence.
-Right now it reads like a figure caption but it shouldn't in a normal paragraph.} The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model (Fig.
-\ref{S4}).
 $\Delta\sigma_{D}^{\prime}$ shows increased $\sigma_{D}$ relative to SNFR25 throughout the entire length of the rift faults at and below 15 km depth, hence the model predicts earthquakes in those regions.
@@
 \vspace{10mm} %5mm vertical space
-%\pagebreak
 
@@
 We assume that the fault parameters are the same for each of the three rift faults and uniform throughout the fault surfaces.
-%Six models with 0, 3, 5, 10, 20 and 30 MPa are constructed (Fig.
-\ref{S6}).
-
-%\vspace{10mm} %5mm vertical space
 
@@
 
-%\vspace{10mm} %5mm vertical space
-
-Magnitudes of $\Delta\sigma_D^{\prime}$ % and \annote[EC]{$\phi_{\max}$}{Fig. S6B doesn't support this.} 
-decrease with increasing cohesion. $\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity %for all the fault cohesions, especially well 
-when the cohesion is less than 5 MPa with about 70\% of the hypocenters fall in the region with $\Delta\sigma_D^{\prime} \ge$ 0.5\% (Fig.
+Magnitudes of $\Delta\sigma_D^{\prime}$ decrease with increasing cohesion.
+$\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity when the cohesion is less than 5 MPa with about 70\% of the hypocenters fall in the region with $\Delta\sigma_D^{\prime} \ge$ 0.5\% (Fig.
 \ref{S6}A).
-%The percentages of the hypocenters in the region with $\Delta\sigma_D^{\prime} \ge$ 0.5\% decrease to 61\% and 47\% for cohesion values of 20 and 30 MPa, respectively.
-%\annote[EC]{, especially well when the cohesion is less than 5 MPa}{What makes you say so? Can't you use the new metric for this argument?} (Fig. \ref{S6}A). 
 However, the models could not explain a few earthquakes in the SW corner of the crater, where $\Delta\sigma_D^{\prime}$ is negative.
@@
 We present models with zero cohesion in the main text to explain the spatial distribution of observed seismicity in the CSZ.
-
-%\note[EC]{Why do you make remarks on $\mu$ mentioning cohesion only little in the paragraph for the effects of cohesion?} Figure \ref{S6} suggests that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope.
-We present models with zero cohesion in the main text because to explain the spatial distribution of observed seismicity in the CSZ.
-
-%\pagebreak
 

### 2019-07-01 main_full_manuscript.tex
Removed all comments and created a manuscript without trackchanges

@@
 \usepackage{apacite} 
-\bibliographystyle{apacite}
-
 \usepackage{comment}
@@
 
-  \item The CSZ seismicity and stress orientations are the combined effects of the rift faults and the impact \change[OF]{crater}{structure}.
+  \item The CSZ seismicity and stress orientations are the combined effects of the rift faults and the impact structure.
 
@@
 
-  \item \change[OF]{A crater}{An impact structure} four times less elastically stiff than the surrounding crust can explain the seismicity in the CSZ.
+  \item An impact structure four times less elastically stiff than the surrounding crust can explain the seismicity in the CSZ.
 
@@
 \begin{abstract}
-The Charlevoix Seismic Zone (CSZ) \change[OF]{occurs}{is located} along the early Paleozoic St.
-Lawrence rift zone in southeastern Quebec at the location of a major Devonian impact \change[OF]{crater}{structure}.
-The \change[OF]{crater}{impact structure} superimposed major, steeply dipping basement faults trending \add[OF]{approximately} N35$^\circ$E.
-\change[OF]{Many}{Approximately 250} earthquakes are recorded each year in the CSZ and are concentrated within and beneath the impact \change[OF]{crater}{structure}.
-\change[OF]{Some large-magnitude}{Most M4+} earthquakes associated with the rift faults occurred outside the \change[OF]{crater}{impact structure}.
+The Charlevoix Seismic Zone (CSZ) is located along the early Paleozoic St.
+Lawrence rift zone in southeastern Quebec at the location of a major Devonian impact structure.
+The impact structure superimposed major, steeply dipping basement faults trending approximately N35$^\circ$E.
+Approximately 250 earthquakes are recorded each year in the CSZ and are concentrated within and beneath the impact structure.
+Most M4+ earthquakes associated with the rift faults occurred outside the impact structure.
 Apart from the unique distribution of earthquakes in the CSZ, stress inversion of focal mechanisms shows stress rotations within the CSZ, and in the CSZ relative to the stress orientation determined from borehole breakouts.
@@
 We also discuss the effects of resolved velocity anomalies.
-We find that the observed stress rotation is due to the combined effect of the rift faults and the \change[OF]{crater impact}{impact structure}.
-1D velocity models of the CSZ with an embedded \change[OF]{crater}{impact structure} and a combination of 65$^\circ$-40$^\circ$-40$^\circ$ and constant 70$^\circ$ fault dip models \add[OF]{for the three main rift faults} with a \add[OF]{very low} friction coefficient of 0.3 and cohesion of 0 MPa can explain the observed seismicity and more than 50$\%$ of the stress rotations.
+We find that the observed stress rotation is due to the combined effect of the rift faults and the impact structure.
+1D velocity models of the CSZ with an embedded impact structure and a combination of 65$^\circ$-40$^\circ$-40$^\circ$ and constant 70$^\circ$ fault dip models for the three main rift faults with a very low friction coefficient of 0.3 and cohesion of 0 MPa can explain the observed seismicity and more than 50$\%$ of the stress rotations.
 \end{abstract}
@@
 The Charlevoix Seismic Zone (CSZ) is the most seismically active region in eastern Canada.
-The CSZ is within the \change[OF]{Cambro-Ordovician}{Late Precambrian} St.
-Lawrence rift zone in southeastern Quebec and is overprinted by a Devonian impact \change[OF]{crater}{structure} (Fig.
+The CSZ is within the Late Precambrian St.
+Lawrence rift zone in southeastern Quebec and is overprinted by a Devonian impact structure (Fig.
 \ref{figone}).
-The impact \change[OF]{crater}{structure} has a radius of 28 km and is \change[OF]{15}{approximately 12} km deep~\citep{RONDOT1994}.
-The \change[OF]{crater}{impact structure} has a more damaged interior zone with a surface radius of 18 km (Fig.
+The impact structure has a radius of 28 km and is approximately 12 km deep~\citep{RONDOT1994}.
+The impact structure has a more damaged interior zone with a surface radius of 18 km (Fig.
 \ref{figone}).
-The impact \change[OF]{crater}{structure} is superimposed on three major rift faults trending N35$^\circ$E and dipping to the southeast~\citep{anglin1984,Rondot_1971}.
-The CSZ \change[OF]{is considered to pose a high risk of seismic hazard}{has high risk of seismic hazards} due to its history of generating \change[OF]{large}{moderate to large} earthquakes \citep{anglin1984,lamontagne1999}.
-Over 200 earthquakes are recorded each year in the CSZ (Nuttli magnitude, mN \add[OF]{mostly} $\leq$ 3) \citep{Baird_2010} and the hypocenters have a bimodal distribution with peaks at 10 and 22 km depths \citep{Vlahovic_2003}.
-The vast majority of earthquakes in the CSZ occur within the volume bounded by the rift faults \citep{Yu_2016} and those with greater magnitudes occur northeast of the \change[OF]{crater}{impact structure}~\citep{Mazzotti_2010} (Fig.
+The impact structure is superimposed on three major rift faults trending N35$^\circ$E and dipping to the southeast~\citep{anglin1984,Rondot_1971}.
+The CSZ has high risk of seismic hazards due to its history of generating moderate to large earthquakes \citep{anglin1984,lamontagne1999}.
+Over 200 earthquakes are recorded each year in the CSZ (Nuttli magnitude, mN mostly $\leq$ 3) \citep{Baird_2010} and the hypocenters have a bimodal distribution with peaks at 10 and 22 km depths \citep{Vlahovic_2003}.
+The vast majority of earthquakes in the CSZ occur within the volume bounded by the rift faults \citep{Yu_2016} and those with greater magnitudes occur northeast of the impact structure~\citep{Mazzotti_2010} (Fig.
 \ref{figone}).
@@
 \includegraphics[width=18.5pc]{Figures/Map_of_CSZ_2.png} 
-\caption{Topography\add[OF]{, bathymetry,} and seismicity of the Charlevoix Seismic Zone (CSZ) as well as the locations of the impact \change[OF]{crater}{structure} (outer cyan circle) and the more damaged inner \change[OF]{crater}{impact structure} (inner cyan circle).
-Small circles \add[OF]{and stars} are the relocated epicenters~\citep{Powell_2017} \add[OF]{and the complete dataset for the years 1988-2011, respectively,} and their colors represent the focal depths.
+\caption{Topography, bathymetry, and seismicity of the Charlevoix Seismic Zone (CSZ) as well as the locations of the impact structure (outer cyan circle) and the more damaged inner impact structure (inner cyan circle).
+Small circles and stars are the relocated epicenters~\citep{Powell_2017} and the complete dataset for the years 1988-2011, respectively, and their colors represent the focal depths.
 The focal mechanisms are for the earthquakes used by \citet{Mazzotti_2010} for the stress inversion.
-Large circles labeled as NW and SE show orientations of SH$_{\max}$ from the stress inversion of focal mechanism (SH$_S$) and from borehole breakout measurements (SH$_B$) for the earthquake clusters northwest and southeast of the \change[OF]{crater}{impact structure} center.
+Large circles labeled as NW and SE show orientations of SH$_{\max}$ from the stress inversion of focal mechanism (SH$_S$) and from borehole breakout measurements (SH$_B$) for the earthquake clusters northwest and southeast of the impact structure center.
 Solid black lines mark the rift faults known in the region: GNF, Gouffre Northwest Fault; SLF, Saint-Laurent fault; CHF, Charlevoix Fault; and SSF, South Shore Fault \citep{Rondot_1971,lamontagne1999}.
 The inset shows the location of the CSZ in eastern Canada.
-Earthquake \change[OF]{epicenters}{dataset} from the National Resources Canada catalog for the years 1988-2011.}
+Earthquake dataset from the National Resources Canada catalog for the years 1988-2011.}
 \label{figone}
@@
 \citet{Vlahovic_2003} conducted a three-dimensional (3D) P-wave velocity study of the CSZ.
-The tomography model shows several \change[OF]{high-velocity}{higher P-wave velocity} bodies at mid-crustal depths.
-A significant fraction of the CSZ earthquakes occurs around these \change[OF]{high-velocity}{higher P-wave velocity} bodies and some larger earthquakes occur along the northern edges of the high velocity bodies.
+The tomography model shows several higher P-wave velocity bodies at mid-crustal depths.
+A significant fraction of the CSZ earthquakes occurs around these higher P-wave velocity bodies and some larger earthquakes occur along the northern edges of the high velocity bodies.
 
@@
 \citet{Mazzotti_2010} observed a number of relative stress rotations in SH$_{\max}$ determined from different partitions of the earthquakes in the CSZ.
-The largest stress rotation occurs in the cluster of earthquakes located southeast of the \change[OF]{crater}{impact structure} midpoint relative to the earthquakes in the northwest of the \change[OF]{crater}{impact structure} midpoint.
-Specifically, SH$_{\max}$ in the cluster of earthquakes located southeast of the \change[OF]{crater}{impact structure} midpoint shows about a 47$^\circ$ clockwise rotation whereas the cluster located to the northwest has a SH$_{\max}$ that is compatible with the regional SH$_{\max}$~\citep{Mazzotti_2010} (Fig.
+The largest stress rotation occurs in the cluster of earthquakes located southeast of the impact structure midpoint relative to the earthquakes in the northwest of the impact structure midpoint.
+Specifically, SH$_{\max}$ in the cluster of earthquakes located southeast of the impact structure midpoint shows about a 47$^\circ$ clockwise rotation whereas the cluster located to the northwest has a SH$_{\max}$ that is compatible with the regional SH$_{\max}$~\citep{Mazzotti_2010} (Fig.
 \ref{figone}).
@@
 \citet{Baird_2010} explain the distribution of seismicity in the CSZ as products of the interactions between the impact structure and the rift faults.
-Their numerical models for the rift faults and impact \change[OF]{crater}{structure} subjected to the regional stress show increased differential stresses near the fault planes, which is consistent with the distribution of the earthquakes.
-Stress solutions from their numerical models show greater differential stress in the northeast of the \change[OF]{crater}{impact structure}, where \change[OF]{more}{most of the larger} earthquakes occur, than in the southwest.
+Their numerical models for the rift faults and impact structure subjected to the regional stress show increased differential stresses near the fault planes, which is consistent with the distribution of the earthquakes.
+Stress solutions from their numerical models show greater differential stress in the northeast of the impact structure, where most of the larger earthquakes occur, than in the southwest.
 However, their models could not fully explain the SH$_{\max}$ rotations in the CSZ relative to the regional SH$_{\max}$.
@@
 
-In this study, we present a new set of numerical models that can assess the impacts \change[OF]{on}{of} stress distribution due to fault geometry, frictional strengths of faults, elastic properties of the \change[OF]{crater}{impact structure} and velocity models for the region.
-We then try to correlate modeled stress distributions with the recently-relocated hypocenters \citep{Powell_2017} and discuss implications for the non-uniform stress orientation around the \change[OF]{crater}{impact structure} that was previously recognized.
+In this study, we present a new set of numerical models that can assess the impacts of stress distribution due to fault geometry, frictional strengths of faults, elastic properties of the impact structure and velocity models for the region.
+We then try to correlate modeled stress distributions with the recently-relocated hypocenters \citep{Powell_2017} and discuss implications for the non-uniform stress orientation around the impact structure that was previously recognized.
 
@@
 \section{Model Setup}
-We create numerical models that include three major rift faults and the damaged impact \change[OF]{crater}{structure} (Fig.
+We create numerical models that include three major rift faults and the damaged impact structure (Fig.
 \ref{figtwo}A).
@@
 \subsection{Model geometry}
-Our models are composed of three units, crust, \change[OF]{crater}{impact structure} and rift faults, reflecting a simplification of the geology of the region (Fig.
+Our models are composed of three units, crust, impact structure and rift faults, reflecting a simplification of the geology of the region (Fig.
 \ref{figtwo}A).
-The crust is a 220 $\times$ 220 $\times$ 40 km box with the \change[OF]{crater}{impact structure} cut out.
-The impact \change[OF]{crater}{structure} is modeled as a spherical cap with a surface diameter of 60 km and a depth of 15 km.
+The crust is a 220 $\times$ 220 $\times$ 40 km box with the impact structure cut out.
+The impact structure is modeled as a spherical cap with a surface diameter of 60 km and a depth of 15 km.
 
 The three rift faults have a strike of N35$^\circ$E and are embedded in the crust layer except for the top surface edge that is exposed on the surface.
-The three faults correspond to the Gouffre \add[OF]{NW} River, St.
+The three faults correspond to the Gouffre NW River, St.
 Laurent, and the Charlevoix faults (Fig.
@@
 They did not model the Charlevoix fault.
-The locations of the rift faults relative to the \change[OF]{crater}{impact structure} are based on geologic maps by \citet{lamontagne1999} and \citet{Rondot_1971}.
+The locations of the rift faults relative to the impact structure are based on geologic maps by \citet{lamontagne1999} and \citet{Rondot_1971}.
 We create two sets of models with different dip angles of the faults based on two proposed geometries of the rift faults.
@@
 We conducted resolution tests in which the change in displacement and stress solutions relative to a 1 km-resolution model are monitored as a function of element size.
-\change[OF]{Displacement was almost constant for 2 km or smaller element sizes}{Displacements and differential stresses do not change appreciably for elements sizes equal to 4 km or smaller (Fig.
-S1)}.
-\add[OF]{Based on the resolution tests, we use the element size of 2 km for most of the models and 4 km for more computationally expensive models like those for exploring the effects of the friction coefficient.
+Displacements and differential stresses do not change appreciably for elements sizes equal to 4 km or smaller (Fig.
+S1).
+Based on the resolution tests, we use the element size of 2 km for most of the models and 4 km for more computationally expensive models like those for exploring the effects of the friction coefficient.
 Low-friction models, especially those with $\mu$ equal to 0.1 and 0.2, are very expensive due to slow convergence rate in the non-linear solution scheme.
 Running all the models in this group at the same mesh resolution of 4 km ensures intra-group consistency; and the comparison with 2 km-resolution models is also justified because the descritization error does not significantly increase as the resolution increases to 4 km (Fig.
-S1).} We also observe edge effects by comparing a 420 $\times$ 420 $\times$ 40 km model with the original 220 $\times$ 220 $\times$ 40 km model, finding that the seismogenic parts around the \change[OF]{crater}{impact structure} show consistent displacement and stress solutions for both domain sizes.
+S1).
+We also observe edge effects by comparing a 420 $\times$ 420 $\times$ 40 km model with the original 220 $\times$ 220 $\times$ 40 km model, finding that the seismogenic parts around the impact structure show consistent displacement and stress solutions for both domain sizes.
 Based on this result, we choose the smaller domain for this study and set the element size to be about 2 km.
-\add[OF]{The average computation time was about 16 days for fault models ($\mu$ = 0.3) with 2 km element size on 16 cores on the University of Memphis High Performance Computing cluster.
+The average computation time was about 16 days for fault models ($\mu$ = 0.3) with 2 km element size on 16 cores on the University of Memphis High Performance Computing cluster.
 The model with fault dips of 65$^\circ$-40$^\circ$-40$^\circ$ took about two times as long to run for the same model time.
-We do not clearly understand why the model with shallower-dipping faults is slower than the others roughly by a factor of two and further analyzing computational efficiency is beyond the scope of this paper.}
-%we use an element size of 4 km for models with friction coefficient ($\mu$) values of 0.1 and 0.2 due to their expensive computation time.
+We do not clearly understand why the model with shallower-dipping faults is slower than the others roughly by a factor of two and further analyzing computational efficiency is beyond the scope of this paper.
 
@@
 \label{Initial_and_boundary_conditions}
-Initial stresses are assumed to be lithostatic but due to the non-planar geometry of the \change[OF]{crater}{impact structure}, computing initial lithostatic equilibrium stresses is not trivial.
+Initial stresses are assumed to be lithostatic but due to the non-planar geometry of the impact structure, computing initial lithostatic equilibrium stresses is not trivial.
 We first compute lithostatic stresses based on the density distribution from an adopted velocity model for the CSZ (Table~\ref{tableone}) and use it as an initial stress distribution.
@@
 The magnitude of boundary velocity does not represent any tectonic loading in the continental interiors but has the sole purpose of increasing the differential stress ($\sigma_D$ = $\sigma_1 - \sigma_3$).
-Noting that \change[OF]{most earthquakes in the crater occur near 10 km depth}{the depth distribution of earthquakes within the impact structure has a peak at 10 km} \citep{Baird_2010,Powell_2017}, we increase the boundary displacement until $\sigma_D$ reaches 706 MPa at 10 km depth based on Byerlee's law for dry rocks, $\tau$  = 50 MPa + 0.6$\,\sigma_n$~\citep{Byerlee_1978}.
-\add[OF]{More details of the full derivation of the stopping criterion for boundary loading is given in the supplementary information.
-We assume that} $\sigma_3$ corresponds to the lithostatic stress \change[OF]{.
-C}{and adopt the sign convention that compressive stress is negative.}
+Noting that the depth distribution of earthquakes within the impact structure has a peak at 10 km \citep{Baird_2010,Powell_2017}, we increase the boundary displacement until $\sigma_D$ reaches 706 MPa at 10 km depth based on Byerlee's law for dry rocks, $\tau$  = 50 MPa + 0.6$\,\sigma_n$~\citep{Byerlee_1978}.
+More details of the full derivation of the stopping criterion for boundary loading is given in the supplementary information.
+We assume that $\sigma_3$ corresponds to the lithostatic stress and adopt the sign convention that compressive stress is negative.
 
@@
 \includegraphics[width=25pc]{Figures/model_geometry.png}
-\caption{(A) Model domain with the \change[OF]{crater}{impact structure} (gray) and crust (red).
+\caption{(A) Model domain with the impact structure (gray) and crust (red).
 The three rift faults (black lines), dimensions, boundary conditions and the total amount of displacement are annotated.
@@
 (B) The orientation of the model domain (red dotted box) and the associated coordinate axes (red arrows) relative to the geographic reference frame.
-The red dotted box is not the actual model domain but just a box that shows its "orientation." Cyan circles on the geographic map show the inner and outer \change[OF]{crater}{impact structure} boundaries and black solid lines trace rift faults (see Fig.
+The red dotted box is not the actual model domain but just a box that shows its "orientation." Cyan circles on the geographic map show the inner and outer impact structure boundaries and black solid lines trace rift faults (see Fig.
 \ref{figone}).}
@@
 \subsection{Elastic moduli from velocity models}
-We assume linear elasticity for both crust and \change[OF]{crater}{impact structure}.
+We assume linear elasticity for both crust and impact structure.
 To obtain elastic moduli and density distributions, we consider three regional velocity models and one recent model based on local earthquake tomography~\citep{Powell_2017}.
-The regional models are for the Saguenay region in Quebec~\citep{Somerville1990}, the 1D standardized halfspace velocity model of eastern Canada~\citep{lamontagne1999}, and the 1D velocity model derived from \change[OF]{seismic refraction studies}{a simultaneous inversion of hypocenters and velocities of the CSZ}~\citep{lamontagne1999} (Fig.
+The regional models are for the Saguenay region in Quebec~\citep{Somerville1990}, the 1D standardized halfspace velocity model of eastern Canada~\citep{lamontagne1999}, and the 1D velocity model derived from a simultaneous inversion of hypocenters and velocities of the CSZ~\citep{lamontagne1999} (Fig.
 \ref{figthree}).
@@
 \caption{Velocity models used in this study.
-Red, blue and black lines are velocity models for the Saguenay region \citep{Somerville1990}, \change[OF]{a standardized velocity}{the Geological Survey of Canada (GSC) standard velocity model} of Eastern Canada \citep{lamontagne1999} and the \add[OF]{Canadian Shield (North Shore)} velocity model of CSZ \citep{lamontagne1999}.}
+Red, blue and black lines are velocity models for the Saguenay region \citep{Somerville1990}, the Geological Survey of Canada (GSC) standard velocity model of Eastern Canada \citep{lamontagne1999} and the Canadian Shield (North Shore) velocity model of CSZ \citep{lamontagne1999}.}
 \label{figthree}
@@
 
-For simplicity, we assume that the \change[OF]{crater}{impact structure}'s bulk and shear moduli are a certain fraction of those of the crust~\citep[e.g.,][]{Baird_2010}.
-Similarly, the density of the \change[OF]{crater}{impact structure} is reduced \remove[OF]{by 10 \%} from that of the 1D velocity models over the corresponding depth range \add[OF]{to model damaged crustal rocks.
+For simplicity, we assume that the impact structure's bulk and shear moduli are a certain fraction of those of the crust~\citep[e.g.,][]{Baird_2010}.
+Similarly, the density of the impact structure is reduced from that of the 1D velocity models over the corresponding depth range to model damaged crustal rocks.
 Models with density reduced by 0 to 20 \% were run but did not exhibit significant changes as shown in Fig.
 S3 in the supplementary information.
-All the models presented in this study have 10 \% of density reduction in the impact structure.}
+All the models presented in this study have 10 \% of density reduction in the impact structure.
 
@@
 We assume that $\mu$ and $C$ are uniform on the fault planes in each model but investigate the consequences of varying $\mu$ from 0.1 to 0.6 at a constant $C$ of 0 MPa.
-\add[OF]{Although cohesion values from 0 to 30 MPa have been tested and found to have significant effects, we choose to present models with zero cohesion in this study because it is appropriate for pre-existing faults with low normal stress}~\citep[e.g.,][]{Marone_Chris}.
-\add[OF]{We note that the deep portions of the model faults might not satisfy the condition of low normal stress and thus a further investigation on the depth-variation of cohesion is desirable.}
-%\add[OF]{and slips on the model faults occur only down to about 10 km depth satisfying this condition.} 
-%\note[EC]{I think the following sentences should be in discussion, not here.}\add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig.
-S4).
-Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.}
+Although cohesion values from 0 to 30 MPa have been tested and found to have significant effects, we choose to present models with zero cohesion in this study because it is appropriate for pre-existing faults with low normal stress~\citep[e.g.,][]{Marone_Chris}.
+We note that the deep portions of the model faults might not satisfy the condition of low normal stress and thus a further investigation on the depth-variation of cohesion is desirable.
 
@@
 This is equivalent to a model with infinitely strong faults.
-The initial stress state is close to the initially assumed lithostatic stress after the nonplanar correction due to the \change[OF]{crater}{impact structure}.
+The initial stress state is close to the initially assumed lithostatic stress after the nonplanar correction due to the impact structure.
 We determine the percentage change in differential stress, $\Delta\sigma_{D}^{\prime}=100\,( \sigma_{D}-\sigma_{D,ref}) / \sigma_{D,ref}$, and the change in the orientation of SH$_{max}$,  $\Delta\phi_{\max}=\phi_{\max}-\phi_{\max,ref}$, where $\phi_{\max}$ denotes the orientation of the maximum principal stress ($\sigma_1$).
-Since our model domain was rotated clockwise about the center of the \change[OF]{crater}{impact structure} by 35$^\circ$, $\phi_{\max}$ equal to zero should be understood as parallel to the regional stress field.
+Since our model domain was rotated clockwise about the center of the impact structure by 35$^\circ$, $\phi_{\max}$ equal to zero should be understood as parallel to the regional stress field.
 Positive and negative values of $\phi_{\max}$ correspond to anticlockwise and clockwise rotation from the direction of applied loading, respectively.
-\add[OF]{In order to quantify the spatial correlation between the simulated stress changes and the earthquake hypocenters, we determine the percentage of hypocenters that fall within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5 \%.
-We did not account for the uncertainty in hypocenter relocation and the effect of any along-strike variation in the fault dips.} % in reality
+In order to quantify the spatial correlation between the simulated stress changes and the earthquake hypocenters, we determine the percentage of hypocenters that fall within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5 \%.
+We did not account for the uncertainty in hypocenter relocation and the effect of any along-strike variation in the fault dips.
 
 \subsection{Control Parameters}
-We create a series of models in which the following parameters are varied: dips of the rift faults, friction coefficients, \change[OF]{crater}{impact structure}-crust elastic moduli ratios, and the velocity models.
+We create a series of models in which the following parameters are varied: dips of the rift faults, friction coefficients, impact structure-crust elastic moduli ratios, and the velocity models.
 Two fault geometries for the CSZ are considered.
@@
 
-\change[OF]{crater}{Impact structure}-crust elastic moduli ratios tested are 0.25, 0.5 and 1.0.
-When the modulus ratio is 1.0, the \change[OF]{crater}{impact structure} has the same velocity model as the crust.
+Impact structure-crust elastic moduli ratios tested are 0.25, 0.5 and 1.0.
+When the modulus ratio is 1.0, the impact structure has the same velocity model as the crust.
 The friction coefficient, $\mu$, is varied from 0.1 to 0.6 at a constant cohesion of 0 MPa in one set of models.
-We assume that $\mu$ and $C$ are the same for the three rift faults and it is uniform on the fault planes, including the part of the faults within the \change[OF]{crater}{impact structure} region.
+We assume that $\mu$ and $C$ are the same for the three rift faults and it is uniform on the fault planes, including the part of the faults within the impact structure region.
 
@@
 \ref{figthree} and \ref{figfour}).
-When the tomography model is used, the \change[OF]{crater}{impact structure}-crust moduli ratio becomes irrelevant.
+When the tomography model is used, the impact structure-crust moduli ratio becomes irrelevant.
 All the models presented in this paper are listed in Table~\ref{tableone}.
@@
 \caption{List of numerical models} 
-%\note[EC]{Each symbol needs a description. Cohesion needs a unit. I gave a try with the $\dagger$ symbol.}}
 \centering
@@
 SD70R25V  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1-0.6 & 0 & 55.7 & 32.7 \\
-%SD70R25M1 &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1 & 0 \\
 SD65R25  &  & $65^\circ-40^\circ-40^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7\\
@@
 \subsection{Reference Model (SNFR25)} \label{Ref_Model}
-The effects of the weaker \change[OF]{crater}{impact structure} are dominant in SNFR25.
-$\sigma_D$ is smaller by 100s MPa in the \change[OF]{crater}{impact structure} region relative to the surrounding crustal rock as shown by 5 and 10-km depth sections (Fig.
+The effects of the weaker impact structure are dominant in SNFR25.
+$\sigma_D$ is smaller by 100s MPa in the impact structure region relative to the surrounding crustal rock as shown by 5 and 10-km depth sections (Fig.
 \ref{fig:SNFR25_ref}A).
@@
 is more negative) in the direction perpendicular to the applied loading than in the parallel direction.
-At depths below the \change[OF]{crater}{impact structure} (i.e., depths $\ge$ 15 km), $\sigma_D$ is more negative at the central region by about 300 MPa relative to the average $\sigma_D$ at those depths (Fig.
+At depths below the impact structure (i.e., depths $\ge$ 15 km), $\sigma_D$ is more negative at the central region by about 300 MPa relative to the average $\sigma_D$ at those depths (Fig.
 \ref{fig:SNFR25_ref}A).
 The higher negative value of $\sigma_D$ at 15 km depth decreases to the average value at that depth within 20 km from the center of the model geometry.
-The effect of the \change[OF]{crater}{impact structure} weakens at 20 km and eventually becomes insignificant at 25 km (Fig.
+The effect of the impact structure weakens at 20 km and eventually becomes insignificant at 25 km (Fig.
 \ref{fig:SNFR25_ref}A).
 
-$\phi_{\max}$, the orientation of SH$_{\max}$, shows a four-lobe pattern of alternating polarities around the \change[OF]{crater}{impact structure} (Fig.
+$\phi_{\max}$, the orientation of SH$_{\max}$, shows a four-lobe pattern of alternating polarities around the impact structure (Fig.
 \ref{fig:SNFR25_ref}B).
-$\phi_{\max}$ uniformly approaches 0$^\circ$, the loading direction, away from the \change[OF]{crater}{impact structure} and also with depth (Fig.
+$\phi_{\max}$ uniformly approaches 0$^\circ$, the loading direction, away from the impact structure and also with depth (Fig.
 \ref{fig:SNFR25_ref}B).
-In the SE corner of the \change[OF]{crater}{impact structure}, $\phi_{\max}$ shows a maximum clockwise (i.e., negative) rotation of about 18.3$^\circ$ from the regional stress direction (5 km panel in Fig.
+In the SE corner of the impact structure, $\phi_{\max}$ shows a maximum clockwise (i.e., negative) rotation of about 18.3$^\circ$ from the regional stress direction (5 km panel in Fig.
 \ref{fig:SNFR25_ref}B).
-$\phi_{\max}$ at 5 km and 10 km depths is close to 0$^\circ$ within the \change[OF]{crater}{impact structure}, being subparallel to the regional stress orientation ~\citep{Zoback_1992}.
+$\phi_{\max}$ at 5 km and 10 km depths is close to 0$^\circ$ within the impact structure, being subparallel to the regional stress orientation ~\citep{Zoback_1992}.
 
@@
 \subsubsection{SD70R25}
-Magnitudes of $\sigma_{D}$ in SD70R25 are smaller in the \change[OF]{crater}{impact structure} than in the surrounding crust, as in the reference model, but also significantly modified by abrupt changes in the vicinity of the rift faults (Fig.
+Magnitudes of $\sigma_{D}$ in SD70R25 are smaller in the impact structure than in the surrounding crust, as in the reference model, but also significantly modified by abrupt changes in the vicinity of the rift faults (Fig.
 \ref{fig:SD70R25}A).
-$\sigma_{D}$ at a distance greater than 50 km from the center of the \change[OF]{crater}{impact structure} is similar to that of the reference model at each depth.
+$\sigma_{D}$ at a distance greater than 50 km from the center of the impact structure is similar to that of the reference model at each depth.
 
@@
 \centering
-%\includegraphics[width=25pc]{Figures/SD70R25.png}
 \includegraphics[width=25pc]{Figures/SD70R25_2.png}
@@
 Earthquakes within 2 km of each depth slice are represented by black dots in \ref{fig:SD70R25}C.
-\add[OF]{The outline of the impact structure is represented as a black circle.} Each figure is 70 $\times$ 70 km.}
+The outline of the impact structure is represented as a black circle.
+Each figure is 70 $\times$ 70 km.}
 \label{fig:SD70R25}
@@
 
-$\phi_{\max}$ shows a four-lobe pattern of alternating polarities around the weaker \change[OF]{crater}{impact structure} but modifications made by the faults are also clearly visible.
-$\phi_{\max}$ in the surrounding crust approaches 0$^\circ$ as distance from the \change[OF]{crater}{impact structure}'s center or depth increases (Fig.
+$\phi_{\max}$ shows a four-lobe pattern of alternating polarities around the weaker impact structure but modifications made by the faults are also clearly visible.
+$\phi_{\max}$ in the surrounding crust approaches 0$^\circ$ as distance from the impact structure's center or depth increases (Fig.
 \ref{fig:SD70R25}B).
-$\phi_{\max}$ within the \change[OF]{crater}{impact structure} is about $-5^{\circ}$ at a depth of 5 km but is subparallel to the regional stress orientation at 10 km depth (Fig.
+$\phi_{\max}$ within the impact structure is about $-5^{\circ}$ at a depth of 5 km but is subparallel to the regional stress orientation at 10 km depth (Fig.
 \ref{fig:SD70R25}B).
 The main effect of the rift faults is a 5$^{\circ}$ to 15$^{\circ}$ $\phi_{\max}$ clockwise rotation that persists along the faults at 5 and 10 km depths.
-The sense of near-fault $\phi_{\max}$ rotations flips to anticlockwise at 10 km within the \change[OF]{crater}{impact structure} and at depths below the \change[OF]{crater}{impact structure} in the surrounding crust.
+The sense of near-fault $\phi_{\max}$ rotations flips to anticlockwise at 10 km within the impact structure and at depths below the impact structure in the surrounding crust.
 The anticlockwise rotation also persists along the faults and has a magnitude of about 5$^{\circ}$.
@@
 \ref{fig:SD70R25}C).
-\add[OF]{About 70\% of the hypocenters fall in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} We superimpose the relocated hypocenters of earthquakes of \citet{Powell_2017} that occurred within 2 km of each depth slice.
-The hypocenters are rotated clockwise by 35$^{\circ}$ about the center of the \change[OF]{crater}{impact structure} in order for them to be consistent with the rotated model geometry.
-Some earthquakes fall in the region of negative $\Delta\sigma_{D}^{\prime}$ near the SW and NE boundary of the \change[OF]{crater}{impact structure} at depths shallower than 15 km.
+About 70\% of the hypocenters fall in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.
+We superimpose the relocated hypocenters of earthquakes of \citet{Powell_2017} that occurred within 2 km of each depth slice.
+The hypocenters are rotated clockwise by 35$^{\circ}$ about the center of the impact structure in order for them to be consistent with the rotated model geometry.
+Some earthquakes fall in the region of negative $\Delta\sigma_{D}^{\prime}$ near the SW and NE boundary of the impact structure at depths shallower than 15 km.
 
@@
 \ref{fig:SD70R25}D show that the rift faults rotate SH$_{\max}$ of SNFR25 further clockwise at 5 and 10 km depths by up to 19$^{\circ}$.
-The effect of clockwise rotation due to the faults is diminished within the \change[OF]{crater}{impact structure} and flips the sense of rotation to anticlockwise at 10 km (Fig.
+The effect of clockwise rotation due to the faults is diminished within the impact structure and flips the sense of rotation to anticlockwise at 10 km (Fig.
 \ref{fig:SD70R25}D).
-At depths below the \change[OF]{crater}{impact structure}, the overall impact of the faults decrease everywhere.
+At depths below the impact structure, the overall impact of the faults decrease everywhere.
 
@@
 As marked on the 10-km depth slice of $\Delta\sigma_{D}^{\prime}$ (left panel in Fig.~\ref{fig:profiles_70_70_70_2km}), they are all perpendicular to the fault strike.
-Two cross sections, 1 and 2, go through the central and marginal areas of the \change[OF]{crater}{impact structure} but the cross section 3 does not intersect the \change[OF]{crater}{impact structure}.
+Two cross sections, 1 and 2, go through the central and marginal areas of the impact structure but the cross section 3 does not intersect the impact structure.
 Also plotted on these cross sections are the hypocenters of the region's earthquakes within 2 km from each cross section.
 Most of the earthquakes fall within regions of increased differential stress but some are associated with negative or negligible changes in differential stress.
-In the cross sections going through the \change[OF]{crater}{impact structure}, the broad region between the northernmost and the southernmost fault shows positive $\Delta\sigma_{D}^{\prime}$.
+In the cross sections going through the impact structure, the broad region between the northernmost and the southernmost fault shows positive $\Delta\sigma_{D}^{\prime}$.
 In contrast, the relocated hypocenters exhibit well-defined linear trends as observed by~\citet{Powell_2017}.
@@
 The three NW-SE cross sections are indicated on the 10-km depth slice showing earthquakes within 2 km of the depth slice.
-The outline of the \change[OF]{crater}{impact structure} is represented as black circle and curved lines on the depth slice and cross sections, respectively.
-The depth slice is 70 $\times$ 70 km centered on the impact \change[OF]{crater}{structure}.
+The outline of the impact structure is represented as black circle and curved lines on the depth slice and cross sections, respectively.
+The depth slice is 70 $\times$ 70 km centered on the impact structure.
 Note the cross sections have the same color and length scales as the depth slice in~\ref{fig:profiles_70_70_70_2km}A.}
@@
 \centering
-%\includegraphics[width=30pc]{Figures/SD65R25.png}
 \includegraphics[width=30pc]{Figures/SD65R25_2.png}
@@
 Earthquakes within 2 km of each depth slice are represented by black dots in \ref{fig:eff_of_dips}A.
-\add[OF]{The outline of the impact structure is represented as a black circle.} Each figure is 70 $\times$ 70 km.}
+The outline of the impact structure is represented as a black circle.
+Each figure is 70 $\times$ 70 km.}
 \label{fig:eff_of_dips}
@@
 \ref{fig:eff_of_dips}) although both models show the four-lobe pattern and magnitudes of $\phi_{\max}$ decreasing with depth.
-Within the \change[OF]{crater}{impact structure}, SD65R25 shows clockwise rotations of about 5$^\circ$ at 10 km depth and the counterclockwise rotation observed for model SD70R25 is seen only north of the northernmost fault because the other two faults barely cross the \change[OF]{crater}{impact structure} region at this depth due to their shallower dip (Fig.
+Within the impact structure, SD65R25 shows clockwise rotations of about 5$^\circ$ at 10 km depth and the counterclockwise rotation observed for model SD70R25 is seen only north of the northernmost fault because the other two faults barely cross the impact structure region at this depth due to their shallower dip (Fig.
 \ref{fig:eff_of_dips}).
@@
 \ref{fig:eff_of_dips}).
-Counterclockwise rotation of $\phi_{\max}$ relative to the regional SH$_{\max}$ extends to the northeast and southwest of the \change[OF]{crater}{impact structure} in the fault-bounded region.
-
-When compared to SH$_{\max}$ orientations in the reference model, SD65R25 shows greater clockwise rotations of $\phi_{\max}$ by up to 20$^\circ$ near the rift faults and the northeastern boundary of the \change[OF]{crater}{impact structure} at 10 km depth (Fig.
+Counterclockwise rotation of $\phi_{\max}$ relative to the regional SH$_{\max}$ extends to the northeast and southwest of the impact structure in the fault-bounded region.
+
+When compared to SH$_{\max}$ orientations in the reference model, SD65R25 shows greater clockwise rotations of $\phi_{\max}$ by up to 20$^\circ$ near the rift faults and the northeastern boundary of the impact structure at 10 km depth (Fig.
 \ref{fig:eff_of_dips}).
@@
 
-The region of increased differential stress in SD65R25 exhibits well-defined linear trends near the rift faults, and thus gives a better explanation for the narrow and well-defined seismicity near the \change[OF]{crater}{impact structure} (Fig.
+The region of increased differential stress in SD65R25 exhibits well-defined linear trends near the rift faults, and thus gives a better explanation for the narrow and well-defined seismicity near the impact structure (Fig.
 \ref{fig:profiles_65_40_40_2km}).
-\add[OF]{About 25\% of the hypocenters fall in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.}.
+About 25\% of the hypocenters fall in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.
 The SD65R25 model shows a region of negative $\Delta\sigma_{D}^{\prime}$ between the observed seismicity on the northernmost and southernmost faults.
-The earthquakes on the middle rift fault and most of the earthquakes on the southernmost fault outside the \change[OF]{crater}{impact structure} fall in regions with negative $\Delta\sigma_{D}^{\prime}$ (Fig.
+The earthquakes on the middle rift fault and most of the earthquakes on the southernmost fault outside the impact structure fall in regions with negative $\Delta\sigma_{D}^{\prime}$ (Fig.
 \ref{fig:profiles_65_40_40_2km}).
-
-%\note[EC]{Why do you say ``even though''?
-Does the percentage betray your or a general expectation?} \add[OF]{, even though the overall percentage of the hypocenters that fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% is about 25\%.}
 
@@
 
-\subsection{Effects of the weakness of the damaged \change[OF]{crater}{impact structure} zone}
-Two models with the rift faults dipping at 70$^{\circ}$ are constructed such that the ratio of elastic moduli of the \change[OF]{crater}{impact structure} to that of the surrounding crust are 0.5 (SD70R50) and 1.0 (SD70R100), respectively.
+\subsection{Effects of the weakness of the damaged impact structure zone}
+Two models with the rift faults dipping at 70$^{\circ}$ are constructed such that the ratio of elastic moduli of the impact structure to that of the surrounding crust are 0.5 (SD70R50) and 1.0 (SD70R100), respectively.
 
 \subsubsection{SD70R50}
-While the effects of the \change[OF]{crater}{impact structure} and rift faults are still clear and consistent, SD70R50 values of $\Delta \sigma_{D}^{\prime}$ are mostly negative with some exceptions at 10 km depth amounting to about a 10 \% increased stress (Fig.
+While the effects of the impact structure and rift faults are still clear and consistent, SD70R50 values of $\Delta \sigma_{D}^{\prime}$ are mostly negative with some exceptions at 10 km depth amounting to about a 10 \% increased stress (Fig.
 \ref{fig:eff_of_moduli_ratio}A).
-The region of positive $\Delta\sigma_{D}^{\prime}$ in the SD70R50 model overlaps with the hypocenters only in the southeast corner of the \change[OF]{crater}{impact structure} boundary and the southernmost rift fault (i.e., the Charlevoix fault) at 5 km depth \add[OF]{, amounting to about 45\% of the hypocenters in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} (Fig.
+The region of positive $\Delta\sigma_{D}^{\prime}$ in the SD70R50 model overlaps with the hypocenters only in the southeast corner of the impact structure boundary and the southernmost rift fault (i.e., the Charlevoix fault) at 5 km depth, amounting to about 45\% of the hypocenters in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% (Fig.
 \ref{fig:eff_of_moduli_ratio}A).
@@
 \centering
-%\includegraphics[width=30pc]{Figures/SD70R50_100.png}
 \includegraphics[width=30pc]{Figures/SD70R50_100_2.png}
-\caption{Same as Fig.~\ref{fig:eff_of_dips} but for the models with different \change[OF]{crater}{impact structure}-crust elastic moduli ratios: (A) SD70R50 and (B) SD70R100.}
+\caption{Same as Fig.~\ref{fig:eff_of_dips} but for the models with different impact structure-crust elastic moduli ratios: (A) SD70R50 and (B) SD70R100.}
 \label{fig:eff_of_moduli_ratio}
@@
 \subsubsection{SD70R100}
-$\Delta\sigma_{D}^{\prime}$ and $\phi_{\max}$ only exhibit the effects of the rift faults since the \change[OF]{crater}{impact structure} and the crust have the same elastic moduli in model SD70R100 (Fig.
+$\Delta\sigma_{D}^{\prime}$ and $\phi_{\max}$ only exhibit the effects of the rift faults since the impact structure and the crust have the same elastic moduli in model SD70R100 (Fig.
 \ref{fig:eff_of_moduli_ratio}B).
@@
 \ref{fig:eff_of_moduli_ratio}B).
-\add[OF]{About 23\% of the hypocenters fall in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} $\Delta\sigma_{D}^{\prime}$ correlates with observed seismicity below 15 km except for some earthquakes in the northern cluster.
+About 23\% of the hypocenters fall in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.
+$\Delta\sigma_{D}^{\prime}$ correlates with observed seismicity below 15 km except for some earthquakes in the northern cluster.
 However, the model predicts earthquakes throughout the entire length of the rift faults at and below 15 km depth.
@@
 S4).
-\add[OF]{The result of a model with an intermediate moduli ratio of 0.75 is somewhat between the SD70R50 and SD70R100 models (Fig.
-S5).}
+The result of a model with an intermediate moduli ratio of 0.75 is somewhat between the SD70R50 and SD70R100 models (Fig.
+S5).
 
@@
 \ref{fig:eff_of_mu}A) because the model behaviors must approach those of the no-fault model as fault strength increases.
-When $\mu$ values are 0.1 and 0.2, the area of positive $\Delta\sigma_{D}^{\prime}$ regions does not cover the entire observed seismicity\add[OF]{, with about 3 and 24\% of the hypocenters within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, respectively}.
+When $\mu$ values are 0.1 and 0.2, the area of positive $\Delta\sigma_{D}^{\prime}$ regions does not cover the entire observed seismicity, with about 3 and 24\% of the hypocenters within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%, respectively.
 The regions of positive $\Delta\sigma_{D}^{\prime}$ for $\mu$ values equal to 0.3 and 0.4 show better spatial correspondence with the seismicity of the CSZ.
 However, the model with $\mu = 0.4$ predicts positive Coulomb stress changes along the entire length of the rift faults, which is contrary to the limited spatial extent of the observed seismicity.
-\add[OF]{Also, about 66\% of the hypocenters in the model with $\mu$ = 0.3 fall within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% while only 35\% do when $\mu$ = 0.4.
-However, when the hypocenters falling in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0\% are considered, the percentages increase to 73 and 82\% for $\mu$ equal to 0.3 and 0.4.}
+Also, about 66\% of the hypocenters in the model with $\mu$ = 0.3 fall within the region of $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% while only 35\% do when $\mu$ = 0.4.
+However, when the hypocenters falling in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0\% are considered, the percentages increase to 73 and 82\% for $\mu$ equal to 0.3 and 0.4.
 $\Delta\sigma_{D}^{\prime}$ approaches zero when $\mu$ values are 0.5 and 0.6, for which the faults are locked.
-\add[OF]{The percentage of hypocenters in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% reduces to 1.4\% and 0\% when $\mu$ values are 0.5 and 0.6, respectively.}
+The percentage of hypocenters in the region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% reduces to 1.4\% and 0\% when $\mu$ values are 0.5 and 0.6, respectively.
 
@@
 \centering
-%\includegraphics[width=30pc]{Figures/SD70R25V.png}
 \includegraphics[width=30pc]{Figures/SD70R25V_2.png}
@@
 Earthquakes within 2 km of each depth slice are represented by black dots in \ref{fig:eff_of_mu}A.
-\add[OF]{The outline of the impact structure is represented as a black circle.} Each figure is 70 $\times$ 70 km.}
+The outline of the impact structure is represented as a black circle.
+Each figure is 70 $\times$ 70 km.}
 \label{fig:eff_of_mu}
@@
 
-$\phi_{\max}$ maps show a clockwise stress rotation in the entire seismic zone, including the \change[OF]{crater}{impact structure} region, when $\mu$ values are 0.1 and 0.2 (Fig.
+$\phi_{\max}$ maps show a clockwise stress rotation in the entire seismic zone, including the impact structure region, when $\mu$ values are 0.1 and 0.2 (Fig.
 \ref{fig:eff_of_mu}B).
-When $\mu$ is 0.3, $\phi_{\max}$ is subparallel to the regional stress orientation within the \change[OF]{crater}{impact structure} region and the four-lobe pattern appears.
+When $\mu$ is 0.3, $\phi_{\max}$ is subparallel to the regional stress orientation within the impact structure region and the four-lobe pattern appears.
 For $\mu \ge$ 0.4, the distribution of $\phi_{\max}$ approaches that of the reference model.
@@
 We use the 1D velocity model \citep{lamontagne1999} (Fig.~\ref{figthree}) and the 3D tomography results \citep{Powell_2017} (Fig.~\ref{figfour}) in LD70R25 and TD70 models, respectively.
-The $V_p$ and $V_s$ tomography model covers and extends beyond the \change[OF]{crater}{impact structure} region, so the \change[OF]{crater}{impact structure}-crust elastic moduli ratio is irrelevant because it is dictated by the velocities.
+The $V_p$ and $V_s$ tomography model covers and extends beyond the impact structure region, so the impact structure-crust elastic moduli ratio is irrelevant because it is dictated by the velocities.
 
@@
 \centering
-%\includegraphics[width=20pc]{Figures/LD70R25_TD70.png}
 \includegraphics[width=20pc]{Figures/LD70R25_TD70_2.png}
@@
 
-The $\phi_{\max}$ maps also show the four-lobe pattern around the weaker \change[OF]{crater}{impact structure} and modification of the $\phi_{\max}$ by the rift faults is observed (Fig.
+The $\phi_{\max}$ maps also show the four-lobe pattern around the weaker impact structure and modification of the $\phi_{\max}$ by the rift faults is observed (Fig.
 \ref{fig:eff_of_vel}A).
@@
 \subsubsection{TD70}
-TD70 shows very different results from those of the models with a layered velocity model and a weak \change[OF]{crater}{impact structure}.
-As the tomography model does not clearly show low velocities within the \change[OF]{crater}{impact structure} region, $\Delta\sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta\phi_{\max}$ are all very similar to those in SD70R100, in which the \change[OF]{crater}{impact structure} is not distinguished from the surrounding crust in terms of elastic stiffness.
+TD70 shows very different results from those of the models with a layered velocity model and a weak impact structure.
+As the tomography model does not clearly show low velocities within the impact structure region, $\Delta\sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta\phi_{\max}$ are all very similar to those in SD70R100, in which the impact structure is not distinguished from the surrounding crust in terms of elastic stiffness.
 
@@
 
-The $\phi_{\max}$ maps do not show the characteristic four-lobe pattern as seen in the models with the \change[OF]{crater}{impact structure} due to the lack of a significant decrease in the velocity model within the \change[OF]{crater}{impact structure} versus outside the \change[OF]{crater}{impact structure} (Fig.
+The $\phi_{\max}$ maps do not show the characteristic four-lobe pattern as seen in the models with the impact structure due to the lack of a significant decrease in the velocity model within the impact structure versus outside the impact structure (Fig.
 \ref{fig:eff_of_vel}B).
@@
 \subsection{Earthquake distribution}
-Our models suggest that having both the rift faults and the impact \change[OF]{crater}{structure} is not only sufficient but also necessary for explaining the distribution of earthquakes in the CSZ.
-The models without a weaker \change[OF]{crater}{impact structure} zone, SD70R100 and TD70, show regions of positive $\Delta \sigma_{D}^{\prime}$, a proxy for earthquake generation potential, along the entire length of the rift faults (e.g., Fig.
+Our models suggest that having both the rift faults and the impact structure is not only sufficient but also necessary for explaining the distribution of earthquakes in the CSZ.
+The models without a weaker impact structure zone, SD70R100 and TD70, show regions of positive $\Delta \sigma_{D}^{\prime}$, a proxy for earthquake generation potential, along the entire length of the rift faults (e.g., Fig.
 \ref{fig:eff_of_moduli_ratio}B).
-In contrast, when the \change[OF]{crater}{impact structure} is set to be \change[OF]{less elastically stiff}{elastically softer} than the surrounding crust \add[OF]{ by up to a factor of 4}, positive $\Delta \sigma_{D}^{\prime}$ regions spatially coincide with the observed seismicity in the CSZ, especially above 15 km depth (e.g., Fig.
+In contrast, when the impact structure is set to be elastically softer than the surrounding crust by up to a factor of 4, positive $\Delta \sigma_{D}^{\prime}$ regions spatially coincide with the observed seismicity in the CSZ, especially above 15 km depth (e.g., Fig.
 \ref{fig:SD70R25}C).
-Our models predict that earthquake activity should extend to about 20 km \add[OF]{distance} from the \change[OF]{crater}{impact structure} in a northeast direction (Fig.
+Our models predict that earthquake activity should extend to about 20 km distance from the impact structure in a northeast direction (Fig.
 \ref{fig:SD70R25}C).
 This distribution of positive $\Delta \sigma_{D}^{\prime}$ is not seen in the reference model without the rift faults.
-These two findings from our models are consistent with the conclusion drawn by~\citet{Thomas_Powell_2017} that the seismicity in CSZ requires both the damaged \change[OF]{crater}{impact structure} zone and the rift faults.
+These two findings from our models are consistent with the conclusion drawn by~\citet{Thomas_Powell_2017} that the seismicity in CSZ requires both the damaged impact structure zone and the rift faults.
 
 The SD70R25 and SD65R25 models can explain the seismicity of the CSZ at least partially (Figs.~\ref{fig:profiles_70_70_70_2km} and~\ref{fig:profiles_65_40_40_2km}).
-Correlation between the $\Delta\sigma_{D}^{\prime}$ distribution in SD65R25 and the observed seismicity shows a better and fine-scale correlation than in SD70R25, especially well near and within the \change[OF]{crater}{impact structure} region (Fig.
-\ref{fig:profiles_65_40_40_2km}) while those in SD70R25 fit the observed seismicity better in the northeast region outside the \change[OF]{crater}{impact structure} (Fig.
+Correlation between the $\Delta\sigma_{D}^{\prime}$ distribution in SD65R25 and the observed seismicity shows a better and fine-scale correlation than in SD70R25, especially well near and within the impact structure region (Fig.
+\ref{fig:profiles_65_40_40_2km}) while those in SD70R25 fit the observed seismicity better in the northeast region outside the impact structure (Fig.
 \ref{fig:profiles_70_70_70_2km}).
@@
 The SD65R25 model explains the observed seismic gap between the NW and SE clusters (i.e., between Gouffre Northwest and the Saint-Laurent faults, Fig.
-\ref{figone}) and can also explain the rimming of earthquakes around the \change[OF]{crater}{impact structure} as noted by~\citet{Powell_2017} especially at 10 km depth (Fig.~\ref{fig:profiles_65_40_40_2km}).
-
-Our present models, however, cannot explain the differences in earthquake activity between the \change[OF]{crater}{impact structure} and the surrounding crust in the CSZ.
-`b' values of the Gutenberg-Richter relationship for the regions within and outside the \change[OF]{crater}{impact structure} are 0.93 and 0.74, respectively~\citep{Yu_2016}, indicating a higher frequency of small magnitude earthquakes within the \change[OF]{crater}{impact structure}.
-Also, \change[OF]{the large-magnitude}{most M4+} earthquakes in the CSZ \change[OF]{occurred}{appear to occur} in the northeast region outside the \change[OF]{crater}{impact structure}~\citep[e.g.,][]{lamontagne1999,Powell_2017,Baird_2010}.
-\add[OF]{Reexamination of historical earthquakes in the Charlevoix area by}~\citet{Stevens1980} \add[OF]{shows that some M4+ earthquakes in the period 1924-1978 also occurred at the SE end of the impact structure.} Our models do not show significantly higher values of $\Delta\sigma_{D}^\prime$ in the seismogenic zone outside the \change[OF]{crater}{impact structure} relative to the regions within the impact \change[OF]{crater}{structure} (Fig.
+\ref{figone}) and can also explain the rimming of earthquakes around the impact structure as noted by~\citet{Powell_2017} especially at 10 km depth (Fig.~\ref{fig:profiles_65_40_40_2km}).
+
+Our present models, however, cannot explain the differences in earthquake activity between the impact structure and the surrounding crust in the CSZ.
+`b' values of the Gutenberg-Richter relationship for the regions within and outside the impact structure are 0.93 and 0.74, respectively~\citep{Yu_2016}, indicating a higher frequency of small magnitude earthquakes within the impact structure.
+Also, most M4+ earthquakes in the CSZ appear to occur in the northeast region outside the impact structure~\citep[e.g.,][]{lamontagne1999,Powell_2017,Baird_2010}.
+Reexamination of historical earthquakes in the Charlevoix area by~\citet{Stevens1980} shows that some M4+ earthquakes in the period 1924-1978 also occurred at the SE end of the impact structure.
+Our models do not show significantly higher values of $\Delta\sigma_{D}^\prime$ in the seismogenic zone outside the impact structure relative to the regions within the impact structure (Fig.
 \ref{fig:SD70R25}C).
-A possible explanation is that faults created in the highly fractured \change[OF]{crater}{impact structure} region~\citep{RONDOT_2000} might have lower friction coefficients than the faults outside the \change[OF]{crater}{impact structure}.
-Stress build-up on those weaker \change[OF]{crater}{impact structure} faults can be quicker and smaller in magnitude than on faults outside the \change[OF]{crater}{impact structure} under the same tectonic loading, resulting in more numerous, smaller magnitude earthquakes within versus outside the \change[OF]{crater}{impact structure}.
+A possible explanation is that faults created in the highly fractured impact structure region~\citep{RONDOT_2000} might have lower friction coefficients than the faults outside the impact structure.
+Stress build-up on those weaker impact structure faults can be quicker and smaller in magnitude than on faults outside the impact structure under the same tectonic loading, resulting in more numerous, smaller magnitude earthquakes within versus outside the impact structure.
 
@@
 
-Most of the earthquakes in the NW cluster are within the \change[OF]{crater}{impact structure} region and occur at about 10 km depth (Fig.
+Most of the earthquakes in the NW cluster are within the impact structure region and occur at about 10 km depth (Fig.
 \ref{figone}).
-Our model shows that the rift faults tend to rotate the stress orientation clockwise in the upper 15 km depth but the amount of rotation is reduced within the weak \change[OF]{crater}{impact structure} (e.g., Fig.
+Our model shows that the rift faults tend to rotate the stress orientation clockwise in the upper 15 km depth but the amount of rotation is reduced within the weak impact structure (e.g., Fig.
 \ref{fig:SD70R25}D).
-However, the model with a \change[OF]{crater}{impact structure}-crust moduli ratio of 1.0 shows significant clockwise rotations uniformly along the entire length of the rift faults (Fig.
+However, the model with a impact structure-crust moduli ratio of 1.0 shows significant clockwise rotations uniformly along the entire length of the rift faults (Fig.
 \ref{fig:eff_of_moduli_ratio}B).
-This observation suggests that the impact \change[OF]{crater}{structure} tends to align the $\phi_{\max}$ to the regional tectonic loading direction within the \change[OF]{crater}{impact structure}, particularly at 10 km depth (Fig.
+This observation suggests that the impact structure tends to align the $\phi_{\max}$ to the regional tectonic loading direction within the impact structure, particularly at 10 km depth (Fig.
 \ref{fig:SD70R25}D).
 
-In a model with a \change[OF]{crater}{impact structure} and the rift faults (SD70R25), the stress rotation in the CSZ is clockwise (maximum value of 20.3$^\circ$) and decreases to 0$^\circ$ at an average of 20 km away from the CSZ (Fig.
+In a model with a impact structure and the rift faults (SD70R25), the stress rotation in the CSZ is clockwise (maximum value of 20.3$^\circ$) and decreases to 0$^\circ$ at an average of 20 km away from the CSZ (Fig.
 \ref{fig:SD70R25}B).
 SD70R25 can explain about 60$\%$ of the 32$^\circ$ clockwise stress rotation observed in the CSZ relative to the borehole breakouts, and about 43$\%$ of the 47$^\circ$ rotation in the SE part of the CSZ relative to the NW part.
-The magnitudes of $\phi_{\max}$ in the SD65R25 model are higher than the SD70R25 model by 6$^\circ$, but show a small clockwise rotation within the \change[OF]{crater}{impact structure} at 10 km depth, and thus can explain about 80$\%$ of the 32$^\circ$ clockwise stress rotation observed in the CSZ relative to the borehole breakouts, and about 55$\%$ of the 47$^\circ$ rotation in the SE part of the CSZ relative to the NW part.
-The increase in $\phi_{\max}$ in the SD65R25 relative to the SD70R25 models suggests that the remaining observed stress rotations, not explained by \change[OF]{both models}{either model}, could be partly due to change in dip angle of the rift faults with depth.
+The magnitudes of $\phi_{\max}$ in the SD65R25 model are higher than the SD70R25 model by 6$^\circ$, but show a small clockwise rotation within the impact structure at 10 km depth, and thus can explain about 80$\%$ of the 32$^\circ$ clockwise stress rotation observed in the CSZ relative to the borehole breakouts, and about 55$\%$ of the 47$^\circ$ rotation in the SE part of the CSZ relative to the NW part.
+The increase in $\phi_{\max}$ in the SD65R25 relative to the SD70R25 models suggests that the remaining observed stress rotations, not explained by either model, could be partly due to change in dip angle of the rift faults with depth.
 
@@
 Lawrence seismic zone is located along the St.
-Lawrence River to the NE of the CSZ, and does not contain an impact \change[OF]{crater}{structure}, similar to the SD70R100 model.
+Lawrence River to the NE of the CSZ, and does not contain an impact structure, similar to the SD70R100 model.
 The rotation suggests that the presence of the rift faults and the relative angles of their strikes with respect to the regional orientation of SH$_{\max}$ alone can result in stress rotations ~\citep[e.g.,][]{Zoback_1992}.
-However, the combined effect of the impact \change[OF]{crater}{structure} with up to a quarter of the elastic moduli of the surrounding crust, and the rift faults are required in the CSZ to explain the observed clockwise rotations of the $\phi_{\max}$ in the SE cluster of earthquakes relative to the NW cluster, as well as in the entire CSZ relative to the direction of regional tectonic loading.
+However, the combined effect of the impact structure with up to a quarter of the elastic moduli of the surrounding crust, and the rift faults are required in the CSZ to explain the observed clockwise rotations of the $\phi_{\max}$ in the SE cluster of earthquakes relative to the NW cluster, as well as in the entire CSZ relative to the direction of regional tectonic loading.
 
@@
 1).
-We did not consider the South Shore fault given its aseismic nature \change[OF]{and its location at the extreme eastern edge of the crater}{, although it appears to mark a boundary to the active zone}~\citep{lamontagne1999}.
+We did not consider the South Shore fault given its aseismic nature, although it appears to mark a boundary to the active zone~\citep{lamontagne1999}.
 Our models show that a $\mu$ of 0.3 and cohesion values of 0 MPa create $\Delta\sigma_{D}^\prime$ maps that spatially correlate with the seismicity of CSZ and the observed stress rotations (Fig.
 \ref{fig:eff_of_mu}).
-\add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig.
+We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig.
 S6).
-Cohesion values less than 5 MPa could better explain the spatial distribution of observed seismicity in the CSZ than the greater values.} \add[OF]{$\mu$ equal to 0.4 also seems suitable to the rift faults as the $\Delta\sigma_{D}^\prime$ maps spatially correlate well with the seismicity of the CSZ.
+Cohesion values less than 5 MPa could better explain the spatial distribution of observed seismicity in the CSZ than the greater values.
+$\mu$ equal to 0.4 also seems suitable to the rift faults as the $\Delta\sigma_{D}^\prime$ maps spatially correlate well with the seismicity of the CSZ.
 A small number of earthquakes also occurred at the SW region outside the impact structure (Fig.
-$\ref{figone}$)}.
-%, however, previous studies in the CSZ agreed with a finite extent of the seismicity}~\citep[e.g.,][]{Stevens1980}.
-\note[EC]{I don't understand the point of the sentence about the finite extent of the seismicity.
-Is it necessary?}\change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig.
-\ref{figone}).
-\note[EC]{This sentence should be in the model setup unless you want to discuss implications of this difference.}
+$\ref{figone}$).
 
@@
 
-\remove[OF]{In contrast to the normal faults as suggested by} 
-%\citet{Hurd_Zoback_2012,Hurd_Zoback2012b,Fereidoni2014}, \citet{Baird_2010} 
-\remove[OF]{conclude that the rift faults in the CSZ are very weak with a friction angle of 5$^\circ$ that is equivalent to a $\mu$ of about 0.1.
-This very low value of $\mu$ was necessary for their stopping criterion for boundary loading, which was $\sigma_{D}$ equal to 200 MPa at 10 km depth.} In our study, we stop increasing boundary displacements when $\sigma_{D}$ reaches 706 MPa at 10 km depth as described earlier without making any assumptions for the intermediate principal stress ($\sigma_2$).
-\add[OF]{In contrast,} \citet{Baird_2010} \add[OF]{used a $\sigma_{D}$ equal to 200 MPa at 10 km depth as their stopping criterion for boundary loading.
-They suggested that the rift faults in the CSZ are very weak with %a friction angle of 5$^\circ$ that is equivalent to
-a $\mu$ of about 0.1.
+In our study, we stop increasing boundary displacements when $\sigma_{D}$ reaches 706 MPa at 10 km depth as described earlier without making any assumptions for the intermediate principal stress ($\sigma_2$).
+In contrast, \citet{Baird_2010} used a $\sigma_{D}$ equal to 200 MPa at 10 km depth as their stopping criterion for boundary loading.
+They suggested that the rift faults in the CSZ are very weak with a $\mu$ of about 0.1.
 The higher stopping criterion in our study is based on Byerlee's law under the assumption of no pore-fluid pressure on the rift faults, and it is necessary to make faults slip at seismogenic depth when $\mu$ is 0.3 as assumed in this study.
@@
 In other words, the lower stopping criterion, $\sigma_{D}$ equal to 200 MPa at 10 km depth, might be sufficient for rifts faults with $\mu$ = 0.3 or 0.4 to slip if pore fluid pressure is sufficiently high.
-Another possible consequences of pore-fluid pressure is that faults could be reactivated at smaller angles from the maximum compressive stress}~\citep[e.g.,][]{ChenChen18}.
-
-%This very low value of $\mu$ was necessary for faults to slip under the stopping criterion for boundary loading, which was $\sigma_{D}$ equal to 200 MPa at 10 km depth. \add[OF]{
-%, which will act to reduce the effective normal stress on the rift faults 
-%Pore-fluid pressure is related to the lithostatic stress ($\rho g z$) by a pore-fluid factor ($\lambda$)~\citep[e.g.,][]{HubbertRubey1959, ZobackTownend2001}.
-$\lambda$ values are different for different pore-pressure states: e.g., for a hydrostatic state where pore spaces are interconnected up to the water table, $\labmda$ is between 0.3 and 0.4; for a suprahydrostatic state, $0.4 < \lambda \le 1.0$; and for the lithostatic state, $\lambda = 1.0$~\citep[e.g.,][]{Sibson2000,SibsonRowland,PetriniPodladchikov}.
-It has been suggested that seismic faulting in intraplate seismic zones generally occurs under hydrostatic fluid pressure conditions~$\citep{TownendZoback2000,SibsonRowland}$, except in areas of strong fluid release where $\lambda$ can be up to 1.0~$\citep{ManningIngebritsen99}$.% by up to a factor of two the value of the pore-fluid pressure~\citep[e.g.,][]{ZobackTownend2001}
+Another possible consequences of pore-fluid pressure is that faults could be reactivated at smaller angles from the maximum compressive stress~\citep[e.g.,][]{ChenChen18}.
 
@@
 Our models show that a 1D velocity model of the CSZ \citep{lamontagne1999} (Fig.
-\ref{figthree}) with embedded \change[OF]{crater}{impact structure} and rift faults can explain the observed seismicity and more than 50$\%$ of the stress rotations (Fig.
+\ref{figthree}) with embedded impact structure and rift faults can explain the observed seismicity and more than 50$\%$ of the stress rotations (Fig.
 \ref{fig:eff_of_vel}A).
-Using the velocity model of the \change[OF]{Sanguenay}{Saguenay} region does not improve this result (Fig.
+Using the velocity model of the Saguenay region does not improve this result (Fig.
 \ref{fig:SD70R25}).
@@
 \ref{fig:eff_of_vel}B).
-\citet{lamontagne1999} \change[OF]{Further investigation is needed to determine why the supposedly better velocity models fail}{constructed a 1-D velocity model for the Canadian Shield region that does not include lateral variations of} velocity model to explain the seismicity and stress orientations.
+\citet{lamontagne1999} constructed a 1-D velocity model for the Canadian Shield region that does not include lateral variations of velocity model to explain the seismicity and stress orientations.
 
 \subsection{Limitations of our study}
-Our models could not explain some earthquakes in the SW part of the \change[OF]{crater}{impact structure} especially in the upper 10 km depth (Fig.
+Our models could not explain some earthquakes in the SW part of the impact structure especially in the upper 10 km depth (Fig.
 \ref{fig:SD70R25}C).
@@
 A possible hypothesis for the remaining stress rotation is a change in the dip of the rift faults with depth and the effect of postglacial rebound.
-\remove[OF]{The high stress rotation could also be due to unconstrained focal mechanisms used in the stress inversion.} Most of the focal mechanisms used for stress inversion \add[OF]{in the CSZ} are obtained from first motion P and SH waves~\citep{Mazzotti_2010,lamontagne1998}.
-\change[OF]{Better constrained}{The} focal mechanisms %\note[EC]{What do you mean by ``focal mechanisms are `good\rq{}''?
-It would be good/nice to have better constrained ones, you mean?}
-\add[OF]{are well defined, and we suggest that the focal mechanisms can be further constrained} using waveform modeling \remove[OF]{will be needed} to validate the magnitude of the stress rotation.
-
-We \change[OF]{simplified}{assumed that} the rift faults to be planar however, the fault \change[OF]{trace}{traces} on the geologic map of the CSZ \change[OF]{is not straight}{are not linear} (Fig.
+Most of the focal mechanisms used for stress inversion in the CSZ are obtained from first motion P and SH waves~\citep{Mazzotti_2010,lamontagne1998}.
+The focal mechanisms are well defined, and we suggest that the focal mechanisms can be further constrained using waveform modeling to validate the magnitude of the stress rotation.
+
+We assumed that the rift faults to be planar however, the fault traces on the geologic map of the CSZ are not linear (Fig.
 \ref{figone}).
-The scatter of the seismicity within the \change[OF]{crater}{impact structure} indicates that the faults do not remain planar.
+The scatter of the seismicity within the impact structure indicates that the faults do not remain planar.
 Future models depicting a more realistic fault geometry may also shed light on the factors controlling stress rotation.
-Our model also did not incorporate pore pressure which could have affected the calculated $\mu$ \add[OF]{and maximum $\sigma_{D}$}.
-The 3D velocity model is not \change[OF]{accurate}{very well defined} in the upper 5 km depth and does not cover the entire seismic zone (Fig. \ref{figfour}).
+Our model also did not incorporate pore pressure which could have affected the calculated $\mu$ and maximum $\sigma_{D}$.
+The 3D velocity model is not very well defined in the upper 5 km depth and does not cover the entire seismic zone (Fig.
+\ref{figfour}).
 
@@
 
-\item The combined effects of the impact \change[OF]{crater}{impact structure} and the rift faults are required in the CSZ to explain the observed distribution of seismicity and more than 50$\%$ of the observed clockwise rotations of the $\phi_{\max}$ in the CSZ \add[OF]{with respect to the regional maximum compressive stress direction}.
-
-\item \change[OF]{A crater}{An impact structure} elastically weaker than the surrounding crust by up to a factor of 4 is required to explain the seismicity in the upper 10 km of the CSZ and the observed clockwise rotation of the SH$_{\max}$ in the SE relative to the NW part of the \change[OF]{crater}{impact structure}.
-Below 10 km depth in the \change[OF]{crater}{impact structure}, reactivation of the rift faults explains the observed seismicity in the CSZ.
-
-\item Stress models that spatially correlate with the seismicity of CSZ and the observed stress rotations were obtained when rifts faults have a friction coefficient of 0.3 and zero cohesion \add[OF]{under an assumption of no pore-fluid pressure on the rift faults}.
+\item The combined effects of the impact impact structure and the rift faults are required in the CSZ to explain the observed distribution of seismicity and more than 50$\%$ of the observed clockwise rotations of the $\phi_{\max}$ in the CSZ with respect to the regional maximum compressive stress direction.
+
+\item An impact structure elastically weaker than the surrounding crust by up to a factor of 4 is required to explain the seismicity in the upper 10 km of the CSZ and the observed clockwise rotation of the SH$_{\max}$ in the SE relative to the NW part of the impact structure.
+Below 10 km depth in the impact structure, reactivation of the rift faults explains the observed seismicity in the CSZ.
+
+\item Stress models that spatially correlate with the seismicity of CSZ and the observed stress rotations were obtained when rifts faults have a friction coefficient of 0.3 and zero cohesion under an assumption of no pore-fluid pressure on the rift faults.
 
@@
 
-\item Stress models with dips of 65$^\circ$, 40$^\circ$ and 40$^\circ$ based on a recent hypocenter relocation study show a better correlation between the high differential stress regions and the observed seismicity near and within the \change[OF]{crater}{impact structure} region than those with a constant 70$^\circ$ dip.
-However, the constant-dip models fit the observed seismicity better in the northeast region outside the \change[OF]{crater}{impact structure}.
+\item Stress models with dips of 65$^\circ$, 40$^\circ$ and 40$^\circ$ based on a recent hypocenter relocation study show a better correlation between the high differential stress regions and the observed seismicity near and within the impact structure region than those with a constant 70$^\circ$ dip.
+However, the constant-dip models fit the observed seismicity better in the northeast region outside the impact structure.
 The partial success of each model might indicate more complex geometry of the faults: e.g., an along-strike variation of the dip angles of the rift faults.
@@
 We acknowledge the high performance computing (HPC) resource center at the University of Memphis, TN for providing the computing time for this research.
-\add[OF]{Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakescanada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).}
+Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakescanada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).
 

### 2019-07-01 main_full_manuscript.tex
Minor changes

@@
 We acknowledge the high performance computing (HPC) resource center at the University of Memphis, TN for providing the computing time for this research.
-Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakescanada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).
+Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakes canada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).
 

### 2019-07-01 Supporting_Information.tex
Edits for submission

@@
 %
-\begin{figure}[h!]
+\begin{figure}[ht]
 \setfigurenum{S1}
-\includegraphics[width=25pc]{Figures/res_test_CSZ.png}
+\includegraphics[width=25pc]{res_test_CSZ.png}
 \caption{Errors in displacement components and differential stress ($\sigma_{D}$) for models with element sizes ranging from 2 to 8 km relative to a model with 1 km element size.}
@@
 \setfigurenum{S2}
-\includegraphics[width=25pc]{Figures/Calc_diff_stress.png}
+\includegraphics[width=25pc]{Calc_diff_stress.png}
 \caption{Determining the differential stress for stopping criterion.}
@@
 \setfigurenum{S3}
-\includegraphics[width=25pc]{Figures/effect_of_density.png}
+\includegraphics[width=25pc]{effect_of_density.png}
 \caption{Effect of impact structure-crust density ratio on the percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$) and the change in $\phi_{\max}$ ($\Delta \phi_{\max}^{\prime}$) at 10 km depth.
@@
 \setfigurenum{S4}
-\includegraphics[width=25pc]{Figures/SD70R100_S1.png}
+\includegraphics[width=25pc]{SD70R100_S4.png}
 \caption{Percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) in SD70R100 relative to SNFR25 at various depths.
@@
 \setfigurenum{S5}
-\includegraphics[width=25pc]{Figures/effect_of_moduli_ratio.png}
+\includegraphics[width=25pc]{effect_of_moduli_ratio.png}
 \caption{Same as \ref{S3} but for the models with different impact structure-crust moduli ratio.}
@@
 \setfigurenum{S6}
-\includegraphics[width=25pc]{Figures/SD70R25C_S6.png}
+\includegraphics[width=25pc]{SD70R25C_S6.png}
 \caption{Same as \ref{S3} but for the models with different cohesion values.}

### 2019-07-01 main_full_manuscript.tex
Edits for submission

--- 2019-07-01 main_full_manuscript.tex
@@
 The impact structure superimposed major, steeply dipping basement faults trending approximately N35$^\circ$E.
-Approximately 250 earthquakes are recorded each year in the CSZ and are concentrated within and beneath the impact structure.
+Approximately 250 earthquakes are recorded each year and are concentrated within and beneath the impact structure.
 Most M4+ earthquakes associated with the rift faults occurred outside the impact structure.
-Apart from the unique distribution of earthquakes in the CSZ, stress inversion of focal mechanisms shows stress rotations within the CSZ, and in the CSZ relative to the stress orientation determined from borehole breakouts.
+Apart from the unique distribution of earthquakes, stress inversion of focal mechanisms shows stress rotations within the CSZ, and in the CSZ relative to the stress orientation determined from borehole breakouts.
 The primary goal of this research is to investigate the combined effects of the pre-existing structures and regional stresses on earthquake activity and stress rotations in the CSZ.
@@
 We find that the observed stress rotation is due to the combined effect of the rift faults and the impact structure.
-1D velocity models of the CSZ with an embedded impact structure and a combination of 65$^\circ$-40$^\circ$-40$^\circ$ and constant 70$^\circ$ fault dip models for the three main rift faults with a very low friction coefficient of 0.3 and cohesion of 0 MPa can explain the observed seismicity and more than 50$\%$ of the stress rotations.
+1D velocity models of the CSZ with an embedded impact structure and a combination of 65$^\circ$-40$^\circ$-40$^\circ$ and constant 70$^\circ$ fault-dip models with a very low friction coefficient of 0.3 and cohesion of 0 MPa can explain the observed seismicity and more than 50$\%$ of the stress rotations.
 \end{abstract}
@@
 \centering
-\includegraphics[width=18.5pc]{Figures/Map_of_CSZ_2.png} 
+\includegraphics[width=18.5pc]{Map_of_CSZ_2.png} 
 \caption{Topography, bathymetry, and seismicity of the Charlevoix Seismic Zone (CSZ) as well as the locations of the impact structure (outer cyan circle) and the more damaged inner impact structure (inner cyan circle).
@@
 \centering
-\includegraphics[width=25pc]{Figures/model_geometry.png}
+\includegraphics[width=25pc]{model_geometry.png}
 \caption{(A) Model domain with the impact structure (gray) and crust (red).
@@
 \centering
-\includegraphics[width=30pc]{Figures/layered_vel_models.png}
+\includegraphics[width=30pc]{layered_vel_models.png}
 \caption{Velocity models used in this study.
@@
 \centering
-\includegraphics[width=30pc]{Figures/TOMO_vel_models.png}
+\includegraphics[width=30pc]{TOMO_vel_models.png}
 \caption{Variation of $V_p$ and $V_s$ at the depths from 12 to 14 km from the 3D seismic tomographic model by \citet{Powell_2017}.}
@@
 \centering
-\includegraphics[width=30pc]{Figures/SNFR25.png}
+\includegraphics[width=30pc]{SNFR25.png}
 \caption{(A) Differential stress ($\sigma_D$) and (B) SH$_{\max}$ orientation ($\phi_{\max}$) in the reference model (SNFR25) at different depths.
@@
 \centering
-\includegraphics[width=25pc]{Figures/SD70R25_2.png}
+\includegraphics[width=25pc]{SD70R25_2.png}
 \caption{(A) Differential stress ($\sigma_D$), (B) SH$_{\max}$ orientation ($\phi_{\max}$), (C) Percentage change in differential stress  ($\Delta\sigma_{D}^{\prime}$) and (D) the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) in SD70R25 model relative to SNFR25 at various depths.
@@
 \centering
-\includegraphics[width=25pc]{Figures/SD70R25_profiles.png}
+\includegraphics[width=25pc]{SD70R25_profiles.png}
 \caption{NW-SE cross sections through the percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$) solution in the SD70R25 model.
@@
 \centering
-\includegraphics[width=30pc]{Figures/SD65R25_2.png}
+\includegraphics[width=30pc]{SD65R25_2.png}
 \caption{Percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max})$ and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) at 10 and 15 km depths from the SD65R25 model.
@@
 \centering
-\includegraphics[width=25pc]{Figures/SD65R25_profiles.png}
+\includegraphics[width=25pc]{SD65R25_profiles.png}
 \caption{Same as Fig. \ref{fig:profiles_70_70_70_2km} but for SD65R25 model.}
@@
 \centering
-\includegraphics[width=30pc]{Figures/SD70R50_100_2.png}
+\includegraphics[width=30pc]{SD70R50_100_2.png}
 \caption{Same as Fig.~\ref{fig:eff_of_dips} but for the models with different impact structure-crust elastic moduli ratios: (A) SD70R50 and (B) SD70R100.}
@@
 \centering
-\includegraphics[width=30pc]{Figures/SD70R25V_2.png}
+\includegraphics[width=30pc]{SD70R25V_2.png}
 \caption{Effect of friction coefficient on the $\Delta\sigma_{D}^{\prime}$ and $\phi_{\max}$ in the SD70R25V model at 10 km depth.
@@
 \centering
-\includegraphics[width=20pc]{Figures/LD70R25_TD70_2.png}
+\includegraphics[width=20pc]{LD70R25_TD70_2.png}
 \caption{Same as Fig.~\ref{fig:eff_of_dips} but only at a depth of 10 km for (A) LD70R25 and (B) TD70.}
@@
 We acknowledge the high performance computing (HPC) resource center at the University of Memphis, TN for providing the computing time for this research.
-Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakescanada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).
+Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakes canada.nrcan.gc.ca/stndon/NEDB-BNDS/bulletin-en.php, Natural Resources Canada (1/30/2019).
 

### 2019-07-01 main_full_manuscript_with_trackchanges.tex
Removed all comments and created a manuscript without trackchanges
Edits for submission

--- 2019-06-30 main_full_manuscript.tex
@@
 The \change[OF]{crater}{impact structure} superimposed major, steeply dipping basement faults trending \add[OF]{approximately} N35$^\circ$E.
-\change[OF]{Many}{Approximately 250} earthquakes are recorded each year in the CSZ and are concentrated within and beneath the impact \change[OF]{crater}{structure}.
+\change[OF]{Many}{Approximately 250} earthquakes are recorded each year \remove[OF]{in the CSZ} and are concentrated within and beneath the impact \change[OF]{crater}{structure}.
 \change[OF]{Some large-magnitude}{Most M4+} earthquakes associated with the rift faults occurred outside the \change[OF]{crater}{impact structure}.
-Apart from the unique distribution of earthquakes in the CSZ, stress inversion of focal mechanisms shows stress rotations within the CSZ, and in the CSZ relative to the stress orientation determined from borehole breakouts.
+Apart from the unique distribution of earthquakes \remove[OF]{in the CSZ}, stress inversion of focal mechanisms shows stress rotations within the CSZ, and in the CSZ relative to the stress orientation determined from borehole breakouts.
 The primary goal of this research is to investigate the combined effects of the pre-existing structures and regional stresses on earthquake activity and stress rotations in the CSZ.
@@
 We find that the observed stress rotation is due to the combined effect of the rift faults and the \change[OF]{crater impact}{impact structure}.
-1D velocity models of the CSZ with an embedded \change[OF]{crater}{impact structure} and a combination of 65$^\circ$-40$^\circ$-40$^\circ$ and constant 70$^\circ$ fault dip models \add[OF]{for the three main rift faults} with a \add[OF]{very low} friction coefficient of 0.3 and cohesion of 0 MPa can explain the observed seismicity and more than 50$\%$ of the stress rotations.
+1D velocity models of the CSZ with an embedded \change[OF]{crater}{impact structure} and a combination of 65$^\circ$-40$^\circ$-40$^\circ$ and constant 70$^\circ$ \change[OF]{fault dip}{fault-dip} models with a \add[OF]{very low} friction coefficient of 0.3 and cohesion of 0 MPa can explain the observed seismicity and more than 50$\%$ of the stress rotations.
 \end{abstract}
@@
 \centering
-\includegraphics[width=18.5pc]{Figures/Map_of_CSZ_2.png} 
+\includegraphics[width=18.5pc]{Map_of_CSZ_2.png} 
 \caption{Topography\add[OF]{, bathymetry,} and seismicity of the Charlevoix Seismic Zone (CSZ) as well as the locations of the impact \change[OF]{crater}{structure} (outer cyan circle) and the more damaged inner \change[OF]{crater}{impact structure} (inner cyan circle).
@@
 \centering
-\includegraphics[width=25pc]{Figures/model_geometry.png}
+\includegraphics[width=25pc]{model_geometry.png}
 \caption{(A) Model domain with the \change[OF]{crater}{impact structure} (gray) and crust (red).
@@
 %\includegraphics[width=25pc]{Figures/SD70R25.png}
-\includegraphics[width=25pc]{Figures/SD70R25_2.png}
+\includegraphics[width=25pc]{SD70R25_2.png}
 \caption{(A) Differential stress ($\sigma_D$), (B) SH$_{\max}$ orientation ($\phi_{\max}$), (C) Percentage change in differential stress  ($\Delta\sigma_{D}^{\prime}$) and (D) the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) in SD70R25 model relative to SNFR25 at various depths.
@@
 %\includegraphics[width=30pc]{Figures/SD65R25.png}
-\includegraphics[width=30pc]{Figures/SD65R25_2.png}
+\includegraphics[width=30pc]{SD65R25_2.png}
 \caption{Percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max})$ and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) at 10 and 15 km depths from the SD65R25 model.
@@
 %\includegraphics[width=30pc]{Figures/SD70R50_100.png}
-\includegraphics[width=30pc]{Figures/SD70R50_100_2.png}
+\includegraphics[width=30pc]{SD70R50_100_2.png}
 \caption{Same as Fig.~\ref{fig:eff_of_dips} but for the models with different \change[OF]{crater}{impact structure}-crust elastic moduli ratios: (A) SD70R50 and (B) SD70R100.}
@@
 %\includegraphics[width=30pc]{Figures/SD70R25V.png}
-\includegraphics[width=30pc]{Figures/SD70R25V_2.png}
+\includegraphics[width=30pc]{SD70R25V_2.png}
 \caption{Effect of friction coefficient on the $\Delta\sigma_{D}^{\prime}$ and $\phi_{\max}$ in the SD70R25V model at 10 km depth.
@@
 %\includegraphics[width=20pc]{Figures/LD70R25_TD70.png}
-\includegraphics[width=20pc]{Figures/LD70R25_TD70_2.png}
+\includegraphics[width=20pc]{LD70R25_TD70_2.png}
 \caption{Same as Fig.~\ref{fig:eff_of_dips} but only at a depth of 10 km for (A) LD70R25 and (B) TD70.}
@@
 We acknowledge the high performance computing (HPC) resource center at the University of Memphis, TN for providing the computing time for this research.
-\add[OF]{Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakescanada.nrcan.gc.ca/stndon/NEDB-BNDS/bulleng.php, Natural Resources Canada (1/30/2019).}
+\add[OF]{Earthquake dataset are available from Earthquakes Canada, GSC, Earthquake Search (On-line Bulletin), http://earthquakescanada.nrcan.gc.ca/stndon/NEDB-BNDS/bulletin-en.php, Natural Resources Canada (1/30/2019).}
 
